\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{enumitem}
\geometry{margin=1in}

\title{Goertzel 4CP v23.5: Residual Boundary Peeling after the IDBRAD Obstruction}
\author{Oruzi / Codex}
\date{May 8, 2026}

\begin{document}
\maketitle
\sloppy

\begin{abstract}
This memo records a standalone v23.5 repair attempt for the Goertzel four-color
route.  The exact v23 Step 2 purification statement remains valid in Lean:
single-component purification holds, and summing those local identities
recovers the boundary-only generator used downstream.  What fails is the
present ambient interior-dual boundary-root adjacent-distance peeling package:
on honest closed-walk geometry with genuine interior support, Lean proves that
the current IDBRAD surface cannot exist.  The proposed repair is therefore not
to weaken or patch away that obstruction, but to move the induction to a
residual/current-boundary peeling lane whose certificate is tied to the live
boundary created by previous cancellations.  This document is a route
specification and proof attempt, not a proof of the Four Color Theorem.  Lean
now also proves that the current residual/current-boundary positive wrapper is
equivalent, on a fixed embedding, to the existing collar-layer and
height-ordered positive surfaces.  So the present v23.5 work supplies a
conservative reformulation and sharper obstruction tests, not a validated
stronger same-embedding workaround.
\end{abstract}

\section{Proved Lean facts}

The current Lean status is already sharp enough to separate what survives from
what is blocked.  The main proved facts needed for a v23.5 memo are:

\begin{itemize}[leftmargin=2em]
\item \path{v23_single_component_purification} proves the exact v23 Step 2
local identity
\(
X_f^{ab}(C) \oplus X_f^{ab}(C^D) = c \cdot 1_{D \cap \partial f}
\)
for one boundary-hitting \((a,b)\)-Kempe component \(D\).
\item \path{sum_v23_single_component_purifications_eq_boundaryOnlyGenerator}
shows that summing the exact Step 2 purifications over the boundary-hitting
components recovers the boundary-only generator already used later in the
algebraic route.
\item \path{PlaneEmbeddingWithBoundary.FaceBoundaryClosedWalk.three_le_faceBoundary_card}
shows that every honest nonempty simple facial closed walk has at least three
boundary edges.
\item \path{InteriorDualBoundaryRootAdjDistancePeelData.false_of_mem_interiorEdgeSupport_of_faceBoundaryClosedWalkGeometry}
shows that any ambient IDBRAD package covering an interior edge would force an
impossible terminal peeled face.
\item \path{not_nonempty_interiorDualBoundaryRootAdjDistancePeelData_of_interiorEdgeSupport_nonempty_of_faceBoundaryClosedWalkGeometry}
therefore rules out any nonempty ambient IDBRAD package on honest closed-walk
geometry with genuine interior support.
\item
\path{nonempty_planarBoundaryResidualBoundaryLayerFacePeelWitnessData_iff_nonempty_planarBoundaryCollarLayerFacePeelWitnessData},
\path{theorem49ResidualBoundaryPositiveProjectedGeometryOn_iff_collarLayerPositiveProjectedGeometryOn},
and
\path{theorem49ResidualBoundaryPositiveProjectedGeometryOn_iff_heightOrderedPositiveProjectedGeometryOn}
show that the current residual/current-boundary positive wrapper has exactly
the same fixed-embedding strength as the pre-existing collar-layer and
height-ordered witness surfaces.
\item
\path{nonempty_sharedInteriorPair_v23ResidualBoundaryInitialState_sipFace0Boundary}
builds the exact v23 residual initial state on a genuine face boundary of the
shared-interior-pair honest source benchmark, while
\path{sharedInteriorPair_closedWalkSource_tait_hasUnblockedInteriorEndpoint_and_v23ResidualBoundaryInitialState_without_residualBoundaryGeometry}
and
\path{not_forall_residualBoundaryPositiveProjectedGeometryOn_of_closedWalkAnnulusBoundarySource_and_v23ResidualBoundaryInitialState_and_taitEdgeColoring_and_hasUnblockedInteriorEndpoint_sharedInteriorPair}
show that even this exact Step~2 seed, together with honest source data, a
Tait coloring, and the purified endpoint witness, still does not force any
residual/current-boundary positive geometry on the same embedding.
\end{itemize}

The first two theorems live in
\path{Mettapedia/GraphTheory/FourColor/GoertzelLemma44.lean}; the closed-walk
cardinality lower bound lives in
\path{Mettapedia/GraphTheory/WalkPlanarEmbeddingWithBoundary.lean}; and the
IDBRAD obstruction theorems live in
\path{Mettapedia/GraphTheory/FourColor/Theorem49PlanarBoundaryPeeling.lean};
the residual-equivalence theorems live in
\path{Mettapedia/GraphTheory/FourColor/Theorem49ResidualBoundaryPeeling.lean}.

This fixes the status line exactly.  Step 2 purification is not the live bug.
The live bug is the ambient terminal-peeling interface currently encoded by
IDBRAD.  Any v23.5 route that tries to smuggle that same interface back in
under weaker rhetoric should be rejected immediately by the existing regression
theorems.

\section{The v23.5 proof attempt}

The strategic shift is simple to state and difficult to prove: stop asking the
original ambient annulus boundary to own the whole induction.  The present
obstruction says that if every terminal peeled remainder must already sit on
that ambient boundary, then genuine interior support forces an impossible
one-edge face.  That is valuable information.  It tells us the induction
parameter is wrong.

The v23.5 proposal is to let the algebra follow the \emph{live} boundary of the
surviving residual equation rather than the fixed ambient boundary of the full
embedding.  After each certified cancellation, one forms a new residual object
\(\mathcal{R}_k\) together with its current boundary \(B_k\).  The next peeling
move is certified only relative to \(B_k\), not relative to the initial annulus
boundary chosen before any cancellation happened.

In route form, the intended proof attempt is:
\begin{enumerate}[leftmargin=2em]
\item Start from the honest closed-walk source and the exact v23 Step 2
purification identity already proved in Lean.
\item Package the surviving algebra as a residual equation object
\(\mathcal{R}_0\) with a current boundary \(B_0\) and explicit invariants saying
which terms are still live.
\item Prove that any nonzero residual \(\mathcal{R}_k\) exposes a
current-boundary certificate: some face, component, or boundary-supported
algebraic event that can be canceled without leaving the residual framework.
\item Produce the next residual \(\mathcal{R}_{k+1}\), with a strictly smaller
measure, and repeat.
\item Reach contradiction only by exhausting the residual, not by demanding in
advance that the whole ambient embedding already carries an IDBRAD-style
terminal ownership package.
\end{enumerate}

The creative claim of v23.5 is therefore not that the present IDBRAD
obstruction is illusory.  It is that the obstruction identifies the wrong
globalization step.  The proof route should chase the moving frontier created by
surviving source terms, not the frozen frontier of the original ambient annulus.
If that stronger live-boundary certificate exists, then the exact Step 2
purification theorem becomes the correct algebraic entry point instead of a
local identity waiting for an impossible ambient peel theorem.

The central missing theorem is now clear: every nonzero residual satisfying the
live-boundary invariants must admit a boundary-aligned algebraic cancellation
certificate on the current boundary.  Without that theorem, residual
current-boundary peeling is only a plausible narrative.  With it, one has a
credible replacement for the blocked ambient lane.

The new shared-interior-pair calibration makes this sharper.  The issue is not
that Lean lacks the exact v23 Step~2 seed object: that seed already exists on a
real source face boundary.  What is missing is the genuinely geometric bridge
from that algebraic seed to any same-embedding residual/current-boundary witness
surface.

Lean now shows this already at the actual boundary-order source shell, not only
after lowering to an honest closed-walk package.  On the shared-interior-pair
benchmark, explicit annulus boundary reachability, successor-cycle selected
boundary arcs, the concrete Tait coloring, `HasUnblockedInteriorEndpoint`, and
the exact v23 residual seed still do not force residual positive geometry.  So
the live missing theorem is genuinely route-facing source-to-residual geometry.

Lean now also shows that this exact v23 seed does not recover any of the older
same-embedding geometry ladders either.  On the same shared-interior-pair
benchmark, the exact seed plus honest source data, the concrete Tait coloring,
and `HasUnblockedInteriorEndpoint` still do not force residual witness data,
residual selector data, height-ordered witness data, collar-layer witness
data, the attached boundary-rooted certificate, well-founded witness data, or
weak annulus-collar geometry.  The same failed-universal statement already
holds on the actual successor-cycle boundary-order shell.  So the remaining
v23.5 burden is not a repackaging back into one of the existing geometry
interfaces; it is a genuinely new source-to-residual bridge.

The current ambient IDBRAD obstruction should remain in place as a regression
guard.  A future proof that accidentally reconstructs ambient IDBRAD on honest
closed-walk geometry has not repaired the route; it has walked back into a
formally refuted interface.

\section{Formal obligations}

To turn the v23.5 story into Lean work, the roadmap is:
\begin{enumerate}[leftmargin=2em]
\item \textbf{Residual equation object.}  Define a structure carrying the live
generator, current support, current boundary, and the invariants preserved by
one cancellation step.
\item \textbf{Live-boundary terminal theorem.}  Prove that a nonzero residual
cannot become terminal without exposing a boundary event on the current
boundary.  This replaces the ambient terminal-face claim used by IDBRAD.
\item \textbf{Algebraic cancellation certificate.}  This is the central new
obligation: from a live residual, extract a certified boundary-supported
cancellation move that preserves honesty of the residual package.
\item \textbf{Residual annihilator theorem.}  Show that repeated certified
cancellations strictly decrease a well-founded measure and force the residual to
vanish.
\item \textbf{Source construction theorem.}  Build the initial residual object
from the honest closed-walk source, the exact Step 2 purification theorem, and
the boundary-only generator already present downstream.
\item \textbf{Regression tests.}  Preserve the current ambient IDBRAD
obstruction, and add negative tests showing that the new lane never silently
reintroduces boundary-free ambient peeling, source-free witness placement, or a
fake terminal singleton-face endpoint.
\end{enumerate}

In particular, the algebraic cancellation certificate is the theorem that makes
or breaks the entire v23.5 proposal.  The rest of the roadmap organizes around
it.

\section{Status}

No proof of the Four Color Theorem is claimed here.  What is presently supported
is narrower and firmer: the exact v23 Step 2 purification statement is proved,
and the current ambient IDBRAD route is blocked by proved obstruction theorems.
The residual/current-boundary lane now has a formal wrapper layer, but Lean
also proves that the present positive wrapper is conservative: it is equivalent
to the existing collar-layer and height-ordered packages on a fixed embedding.
So v23.5 is still a proposed repair specification, not a completed derivation
or a validated stronger same-embedding construction theorem.

Accordingly, this memo should be read as a repaired route document.  It states
what survives, what fails, and what new Lean obligations would have to be
discharged before any proof claim could responsibly be made.

\section{Update (2026-06-10): the residual lane refuted as a uniform oracle}

The conservativity observation above is now packaged as a formal refutation.
\path{Mettapedia/GraphTheory/FourColor/Goal.lean} defines
\path{ResidualBoundaryGeometryOracle} --- the statement that every embedding
carrying the bundled endpoint-bearing exact one-collar/v23 shell
(\path{ClosedWalkExactShell}, see \path{Shells.lean}) admits the residual
positive wrapper --- and proves \path{not_residualBoundaryGeometryOracle}:
the wrapper's fixed-embedding equivalence with the collar-layer surface
transports the shared-interior-pair benchmark refutation directly.  The same
file proves the analogous refutations for the previous-boundary witness
geometry, well-founded peel-witness, and generic IDBRAD oracles, so all four
uniform routes from the manuscript's hypothesis shells to its Theorem~4.9
synthesis are now formally closed.

Consequently the status of this memo's proposal is sharpened rather than
changed: items (1), (2), (4), and (5) of the formal-obligations roadmap cannot
succeed through any interface equivalent to the existing geometry ladders.
The algebraic cancellation certificate (item 3) remains the sole live
obligation, and it now carries a precise meta-constraint: whatever interface
expresses it must fail on the wheel-with-inner-triangle and
shared-interior-pair benchmarks, because those embeddings inhabit the full
shells while the synthesis inputs are refuted there.  A complementary cheap
experiment is recorded in \path{ROADMAP.md}: decide
\path{Theorem49BoundaryRootSynthesis} directly on the shell-bearing wheel
embedding, where it is currently neither proved nor refuted.

\end{document}
