\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{listings}
\geometry{margin=1in}

\lstdefinestyle{lean}{
  basicstyle=\ttfamily\small,
  breaklines=true,
  columns=fullflexible,
  keepspaces=true,
  showstringspaces=false,
  frame=single,
  framesep=4pt,
  xleftmargin=2pt,
  aboveskip=8pt,
  belowskip=8pt,
}
\lstset{style=lean}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}
\theoremstyle{definition}
\newtheorem{definition}{Definition}

\newcommand{\Kpoly}{K^{\mathrm{poly}}}
\newcommand{\MY}{M(Y)}
\newcommand{\FF}{\mathbb{F}_2}
\newcommand{\Gap}{\mathrm{Gap}}
\newcommand{\StarSW}{(\star_{\mathrm{SW}})}

\title{A Quantale-Weakness Route to $\mathrm{P}\neq\mathrm{NP}$\\
via CD Evidence Normalization and\\
Gauge-Buffered Locked Ensembles:\\
\large A Machine-Checked Formalization Companion}
\author{The MeTTapedia formalization effort}
\date{July 2026}

\begin{document}
\maketitle
\sloppy

\begin{abstract}
This is a living formalization companion to Ben Goertzel's current-best
$\mathrm{P}$ versus $\mathrm{NP}$ manuscript, \emph{A Quantale-Weakness Route to
$\mathrm{P}\neq\mathrm{NP}$ via CD Evidence Normalization and Gauge-Buffered
Locked Ensembles} (v13, April 2026). That manuscript is a re-architecture of the
earlier Switching-by-Weakness route (v12): it discards the ``short computation is
local'' midpoint and replaces it with an \emph{evidence-accounting} one. The
proof is a single clash in polytime-capped conditional description length
$\Kpoly(\MY\mid Y)$ on an efficiently samplable family of SAT instances $Y$ whose
every witness carries the same global readout message $\MY$: under
$\mathrm{P}=\mathrm{NP}$ a self-reduction gives $\Kpoly(\MY\mid Y)=O(1)$, while an
unconditional lower bound argues $\Kpoly(\MY\mid Y)\ge\eta t$. The lower bound
treats computation as an evidence-producing process: predictive advantage becomes
constructible-dual (CD) evidence skew, then pairwise distinctions between
message-opposite worlds; a normalization theorem forces every target-relevant
non-neutral trace leaf to be a safe-buffer or a hidden-gauge observation; an
\emph{atomic evidence budget} then caps the total advantage at $o(t)$ across the
selected coordinates, which with boundary-law mixing yields product small-success
$2^{-\Omega(t)}$ and, by compression-from-success, the linear incompressibility.

We record what the MeTTapedia Lean development has machine-checked of this route,
and we are scrupulous about a distinction that a naive axiom audit would blur:
the development contains \emph{no} \texttt{sorry}, \texttt{axiom},
\texttt{native\_decide}, or placeholder in its proof terms, and every headline
reduces to Lean's standard base
$\{\texttt{propext},\allowbreak\ \texttt{Classical.choice},\allowbreak\
\texttt{Quot.sound}\}$; but the \emph{open} content of the route is carried
\emph{in the types}, as interface-hypothesis fields of structures and as named
\texttt{Prop} obligations passed as hypotheses. Consequently a clean
\texttt{\#print axioms} on the central clash theorem certifies \emph{the
implication, not the conclusion}. We label every result as unconditional,
conditional on Ben's named interface hypotheses, or open, and we foreground the
places where the formalization \emph{refutes} a stated step (including one of the
manuscript's own scaled constructions, proved inadmissible) rather than
discharging it. The latest source reconciliation gives a sharper verdict than
an open terminal node: the complete nonempty faithful-M4 construction target is
machine-checked \emph{uninhabited}. D.8 message rigidity, D.31 neutrality of the
complete public-template syntax, D.48's opposite-phase coupling, Definition~7.4
/ Hypothesis~7.5 support-wide pair-neutrality, and full public observability are
jointly inconsistent. This obstruction uses none of the four analytic frontier
packages and cannot be repaired merely by changing the lock family.
\textbf{OURS:} the most direct remaining repair --- classify the target-bearing
public syntax as charged while retaining D.48, support-wide neutrality of the
uncharged catalog, full observability, and D.8 rigidity --- is now closed as
well.  Every exact phase coupling carries charged-public disagreement mass one
at each target coordinate, hence exactly $|S|$ over a target set $S$; no
$o(|S|)$ localization is possible under those premises. We make no claim about
$\mathrm{P}$ versus $\mathrm{NP}$, which remains open. Appendices record the
superseded v12 route --- whose calibration step this companion's predecessor was
devoted to obstructing --- and a graveyard of disproven sub-routes, with their
history.
\end{abstract}

\tableofcontents

\section{Orientation: what this document is}
\label{sec:orientation}

A companion of this kind exists to grow alongside a formalization, not to freeze a
single verdict. It has three jobs. First, to distill the \emph{current-best}
version of Ben Goertzel's proof --- the v13 evidence-accounting route --- as a
faithful mathematical spine (\S\ref{sec:route}). Second, to record what the Lean
development has actually checked of that spine, with an honest ledger separating
what holds unconditionally from what holds only modulo the manuscript's interface
hypotheses (\S\S\ref{sec:honesty}--\ref{sec:instantiation}). Third, to keep the
history of obstructions and reroutings --- the counterexamples the formalization
found and how the route moved around them --- both inline where they bear on the
argument (\S\ref{sec:obstructions}) and, for wholly superseded paths, in
appendices (Appendices~\ref{app:v12}--\ref{app:graveyard}).

The reader should keep one structural fact in view throughout. The manuscript's
proof is abstract-then-concrete: an evidence calculus and a budget theorem are
proved \emph{from} a stated interface that a concrete ensemble must satisfy, and
the concrete gauge-buffered locked ensemble is the object that must satisfy all of
those interface hypotheses at once. The formalization mirrors exactly this shape.
Its strongest verified content is therefore of two kinds: genuinely unconditional
theorems about the calculus (normalization, bookkeeping, and a battery of
counterexamples that kill specific over-strong readings), and conditional
\emph{implications} that assemble the interface into the clash. The genuine open
mathematics --- the concentration and hardness inputs the ensemble must supply ---
is named precisely and left open.

\section{The current-best route (v13)}
\label{sec:route}

We follow the manuscript's own notation and numbering. What is preserved from v12
is only the outer skeleton --- the polytime-capped weakness object $\Kpoly$, the
Compression-from-Success bridge, and the self-reduction upper bound under
$\mathrm{P}=\mathrm{NP}$; everything between them is new.

\subsection{The $\Kpoly$ upper--lower clash}
\label{sec:clash}

The cost object (v13 \S2.1--2.2, Def.~2.2) is polytime-capped conditional
description length $\Kpoly(x\mid y)$: the length of the shortest program that
outputs $x$ from $y$ within a fixed polynomial time bound. The construction builds
an efficiently samplable family of public SAT instances $Y$ with a polynomial-time
witness relation $R(Y,W)$; every satisfying witness carries a \emph{readout
message} $M(W)\in\{0,1\}^{r_t}$, $r_t=\Omega(t)$, $t=\Theta(m)$, and the ensemble
enforces the \emph{single-message promise} (v13 \S1.1, Prop.~4.10):
\[
  R(Y,W)=1 \ \wedge\ R(Y,W')=1 \ \Longrightarrow\ M(W)=M(W'),
\]
so $\MY$ is well-defined on the support even though the witness is \emph{not}
unique. The proof is the clash of two bounds on $\Kpoly(\MY\mid Y)$:
\begin{itemize}
  \item \textbf{Upper bound, conditional on $\mathrm{P}=\mathrm{NP}$}
        (v13 \S11 / Prop.~2.17, Thm.~11.10): if $\mathrm{P}=\mathrm{NP}$, the
        bit-fixing SAT self-reduction finds \emph{some} satisfying $W$ in
        polynomial time, and the fixed readout returns $M(W)=\MY$; this is one
        fixed constant-length program, so $\Kpoly(\MY\mid Y)=O(1)$ pointwise on
        the support. Uniqueness of witness is not needed --- the single-message
        promise makes any witness sufficient (Rmk.~11.17).
  \item \textbf{Lower bound, unconditional over the ensemble}
        (v13 \S10 / Thm.~10.9): for every fixed polynomial clock exponent $D$,
        after choosing ensemble parameters for that $D$, there are constants
        $\eta,\kappa>0$ with
        $\Pr[\,\Kpoly_{(D)}(\MY\mid Y)\ge\eta t\,]\ge 1-2^{-\kappa t}$.
  \item \textbf{The clash} (v13 Thm.~11.14 / Cor.~11.15): assume
        $\mathrm{P}=\mathrm{NP}$; it supplies a fixed solver exponent $D^\ast$.
        Instantiate the ensemble at $D^\ast$. For large $t$,
        $\eta^\ast t > c_{\mathrm{up}}$, yet the same instance must satisfy both
        $\Kpoly\ge\eta^\ast t$ and $\Kpoly\le c_{\mathrm{up}}$: contradiction,
        hence $\mathrm{P}\neq\mathrm{NP}$.
\end{itemize}
The clocked constants (e.g.\ a safe radius $R_{\mathrm{safe}}=c(D^\ast)\log m$) are
allowed to depend on the alleged solver's exponent $D^\ast$; the manuscript
defends this (Rmks.~11.16--11.19) on the ground that under $\mathrm{P}=\mathrm{NP}$
the exponent $D^\ast$ is one fixed finite constant, instantiated before
$m,t\to\infty$.

\subsection{The gauge-buffered locked ensemble}
\label{sec:ensemble}

The ensemble (v13 \S4) replaces v12's masked-and-isolated USAT / Valiant--Vazirani
construction. A regioned public geometry $G_m$ (Def.~4.1) partitions sites into
neutral, buffer, locked, gauge, and readout regions. The public instance
$Y=(Y_{\mathrm{neu}},Y_{\mathrm{buf}},Y_{\mathrm{lock}})$ (Def.~4.2) exposes
neutral template syntax, the public law of a strictly-positive high-temperature
\emph{buffer}, and the public template of the locked global-message layer --- and
crucially contains \emph{no} raw witness values, no hidden gauge values, and
\emph{no} public atom of the form $M_a=b$ (no planted message tag). Hidden sites
(Def.~4.3) carry a raw representative $x$, a hidden \emph{gauge} vector $g$, and
the gauge-invariant quotient $z$, tied by $z_v=x_v\oplus g_v$. The verifier
(Def.~4.8) conjoins locked-layer acceptance, the gauge equations, buffer
acceptance, readout consistency, and the Tseitin/CNF gadgets; it has a uniform
poly-size CNF realization $F_Y$ (Thm.~4.13). The gauge group $(\FF)^V$ acts by
$s\cdot(x,g,z,\xi,M)=(x\oplus s,\,g\oplus s,\,z,\,\xi,\,M)$, fixing $Y$, $R$, and
$M$ (Lemma~4.15); the \emph{hidden-gauge product law} (Hyp.~4.17) keeps unexposed
gauge coordinates independent fair bits, giving the guessing bound
$\Pr[\hat g_J=g_J\mid Y,h]\le 2^{-|J|}$ (Cor.~4.19). A \emph{legal safe probe}
reads few buffer sites far from the locked/gauge/readout regions (Def.~4.25);
under buffer contraction / Dobrushin uniqueness (Hyp.~4.27) the soft-buffer
max-qSSM bound (Thm.~4.29) makes polynomially many probes leak only $o(1)$
(Cor.~4.30). Thm.~4.31 exports the interface: samplable $Y/F_Y$; poly-time $R$;
message $M\in\{0,1\}^{r_t}$; single-message promise; gauge action; hidden-gauge
product law; atom completeness (Hyp.~4.22); and max-qSSM.

\subsection{The evidence-accounting midpoint}
\label{sec:midpoint}

The weight of the proof sits on a new midpoint (v13 \S1.2):
\[
  \text{advantage}\ \Longrightarrow\ \text{CD evidence skew}\ \Longrightarrow\
  \text{atomic pair-distinctions}\ \Longrightarrow\ \text{safe leakage}+\text{gauge rank}.
\]
Its components, in order: \textbf{(\S3)} for a target bit $B_j$ with opposite
fibers, a transcript's positive/negative masses encode predictive advantage as
\emph{evidence skew}, and the phase gap
$\Gap_j(A_j)=\tfrac12\bigl|\Pr[A_j=1\mid B_j=1]-\Pr[A_j=1\mid B_j=0]\bigr|$ equals
the CD skew (Lemma~3.20). \textbf{(\S5)} the CD evidence normal form (CD-ENF,
Thm.~5.17) leaves only three non-neutral leaf classes --- neutral, safe-buffer,
hidden-gauge --- and gauge faithfulness (Thm.~5.20, Cor.~5.21) forbids using the
quotient identity $z_v=x_v\oplus g_v$ as a canonical-gauge shortcut: any
target-relevant use normalizes to raw gauge support and is \emph{charged}. This is
the technical heart that replaces v12's calibration/involution step.
\textbf{(\S6)} CD trace capture (Thm.~6.15) telescopes an observer's evidence
trace, bounding the output phase gap by half the total atomic derivative along the
trace: internal computation creates no new pair-distinctions; advantage enters
only when a primitive atom separates two previously undistinguished opposite
worlds. \textbf{(\S7.7)} the \emph{Atomic Evidence Budget} (Thm.~7.23) combines
these with atom-level bounds --- neutral leaves contribute $0$, safe leaves are
bounded by $Q_{\mathrm{tot}}\,\varepsilon_{\mathrm{step}}(m)$ (max-qSSM), gauge
leaves by a gauge-rank entropy $\mathrm{rank}_G$ --- to give
$\sum_{j\in S}\Gap_j(A_j)=o(|S|)$ (Cor.~7.26). \textbf{(\S8)} boundary-law mixing
(Thm.~8.10) makes the pivot-visible surface near-random. \textbf{(\S9)} combining
the budget with mixing yields product small-success
$\Pr[A_S=B_S]\le 2^{-\Omega(t)}$ over the $\Omega(t)$ switched coordinates
(Thms.~9.18/9.19) --- the average-case unpredictability of the message
coordinates that the whole route reduces to. \textbf{(\S2.2 / App.~A.17)}
Compression-from-Success turns that exponential small-success into the linear
$\Kpoly\ge\Omega(t)$ lower bound of \S10.

A self-imposed correctness check (Rmk.~13.11), ``no hidden use of locality,''
forbids any module from re-importing the very step --- v12's
Switching-by-Weakness / calibration via the involution $T_i$ --- that the v13
pivot was designed to eliminate. This is a candid signal of where the earlier
route was fragile; Appendix~\ref{app:v12} records what the formalization found
there.

\subsection{What the manuscript claims, and what it leaves open}
The manuscript claims $\mathrm{P}\neq\mathrm{NP}$ unconditionally by contradiction
(Thm.~1.1). $\mathrm{P}=\mathrm{NP}$ is assumed only for contradiction, supplying
the fixed exponent $D^\ast$. Everything else is discharged \emph{from} the
ensemble-interface hypotheses of Thm.~4.31, which a concrete construction must
satisfy simultaneously; the manuscript is explicit (Rmk.~13.6, milestone M4) that
exhibiting one concrete gauge-buffered locked ensemble satisfying all of them at
once --- single-message promise, SAT realization, atom completeness, gauge
faithfulness, hidden-gauge product law, max-qSSM, bounded gauge incidence,
\emph{and} boundary-law mixing --- is the remaining weight of the proof. Two
contraction hypotheses (boundary posterior contraction, Hyp.~8.5; buffer
contraction, Hyp.~4.27) are offered explicitly as ``prove-or-import.'' The
public-input/neutrality tension is acknowledged as the pivot's pressure point
(Rmk.~4.5): the observer may read the entire public $Y$, and on the single-message
support the target bit is a mathematical function of $Y$, so the claim that
full public-input access normalizes to \emph{neutral} context --- with any
target-relevant use \emph{charged} --- is a genuine structural assumption of the
ensemble, not a cosmetic restriction.

\section{How honesty is encoded in the formalization}
\label{sec:honesty}

Before listing results we fix the reading protocol, because it is the crux of an
honest audit of this route.

\paragraph{No placeholders in proof terms.} A scan of the entire PNP development
finds \emph{no} \texttt{axiom}, \texttt{sorry}, \texttt{admit},
\texttt{native\_decide}, \texttt{opaque}, or \texttt{:= True} placeholder in code.
Every headline theorem we cite was checked with \texttt{\#print axioms} and
reduces to a subset of Lean's standard base
$\{\texttt{propext},\ \texttt{Classical.choice},\ \texttt{Quot.sound}\}$ --- some
to just $\{\texttt{propext}\}$ or $\{\texttt{propext},\ \texttt{Quot.sound}\}$.

\paragraph{The open content lives in the types.} The route's open steps are
carried not as Lean axioms but as \emph{hypotheses}: as assumption fields of a
\texttt{structure}, and as named \texttt{def \dots : Prop} obligations passed in as
arguments. Consequently, a clean axiom print on a \emph{conditional} theorem
certifies that the \emph{implication} is validly proved, and says nothing about
whether the hypotheses hold. Throughout this document we therefore tag each result
with one of four statuses:
\begin{description}
  \item[\textnormal{(a) unconditional}] proved outright (standard axioms, no
        interface hypotheses);
  \item[\textnormal{(b) conditional}] a proved implication from named interface
        hypotheses, or a theorem over a \texttt{structure} carrying assumption
        fields --- ``machine-checked modulo Ben's interface hypotheses'';
  \item[\textnormal{(c) asserted \texttt{Prop}}] a named \texttt{Prop} obligation
        used only as a hypothesis --- no Lean axiom, but analytically open;
  \item[\textnormal{(d) open frontier}] named in doc-comments, not yet a Lean
        statement.
\end{description}
The route's own itinerary is recorded as data in \texttt{Roadmap.lean}, whose
terminal node \texttt{pnp.global-separation} is \texttt{openBackground} at
progress $0\%$: \emph{no final separation theorem is asserted}. Several earlier
nodes are marked \texttt{blockedByCounterexample} --- the formalization
\emph{refutes} the stated step rather than overclaiming it; those refutations are
themselves unconditional theorems (\S\ref{sec:instantiation},
Appendix~\ref{app:graveyard}).

\section{The evidence spine, formalized (Phases A--D)}
\label{sec:spine}

The four phases below are all present in the settled core of the formalization. We give the
load-bearing statement of each and its status.

\subsection{Phase B: the CD evidence normal form (unconditional)}
The cleanest genuine win of the spine. \texttt{V13CDENF} defines a raw evidence
syntax whose leaves are exactly neutral / safe-buffer / hidden-gauge, with
\emph{no} observer-output constructor, and proves that the recursive normalizer
preserves semantics (v13 \S5--6, App.~C.7).
\begin{lstlisting}
theorem CDENF_semantics
    (S : EvidenceSemantics Omega Neutral Safe Gauge)
    (E : RawEvidence Neutral Safe Gauge) :
    S.SatNormal (CDENF E) = S.SatRaw E
\end{lstlisting}
\textbf{Status (a), unconditional}, axioms $\{\texttt{propext},\
\texttt{Quot.sound}\}$ (it does not even need \texttt{Classical.choice}). That the
raw syntax has no opaque observer-output atom is a structural design choice that
makes the three-leaf classification exhaustive by construction; observer outputs
must be expanded through an interface carrying its own semantics theorem
(\texttt{observerToCDENF\_sat}, status (b)).

\subsection{Phase A: the finite evidence spine (conditional)}
\texttt{V13EvidenceSpine} works over a finite rational law (no measure theory),
defines the target \texttt{Gap} of an observer, and bounds it by half a
derivative sum.
\begin{lstlisting}
theorem phaseA_gap_le_half_derivative_sum
    (C : EvidenceSpineBound mu B T g Pair Stage Branch) :
    Gap mu B T g <= (1/2 : Rat) * C.telescoping.derivativeSum
\end{lstlisting}
\textbf{Status (b), conditional}: the \texttt{EvidenceSpineBound} structure carries
the capture inequality (\texttt{capturesGap}) and the telescoping bound
(\texttt{sep\_le\_derivativeSum}) as \emph{assumption fields}; the theorem
assembles them. The two-point toy witnesses are unconditional but trivial. This is
the \S3/\S6 telescoping architecture in place, not a concrete-ensemble estimate.

\subsection{Phase C: the gauge-buffered locked interface (conditional)}
\texttt{V13GaugeBufferedLockedInterface} states the ensemble interface as a
nine-field structure over the Phase-A/B objects --- single-message promise,
hidden-gauge product, no public target tags, atom completeness, gauge
faithfulness, safe-qSSM, bounded gauge incidence, boundary mixing, admissible
histories --- and proves three ledger-coherence consequences (e.g.\ that an
admissible history is not target-measurable, and that boundary mixing blocks pivot
sufficiency). \textbf{Status (b)}: all three are derived \emph{from} the nine
assumption fields. A two-point toy jointly inhabits all nine fields (status (a),
but trivial): it certifies the interface is \emph{consistent / non-vacuous}, not
that any scaled ensemble satisfies it. The manuscript's quantitative estimates
(max-qSSM, gauge-rank) appear here only as abstract budget fields.

\subsection{Phase D: the upper--lower clash, as a conditional object}
\label{sec:phaseD}
\texttt{V13ConditionalClash} assembles Phases~A--D into the clash \emph{as an
implication}. It reuses the checked lower-bound plumbing and isolates the two
genuinely open analytic inputs as their own structures: a
\texttt{CompressionStarSWHardness} field (the average-case witness-bit hardness
transfer, $\StarSW$) and a \texttt{SelfReductionUpperHypothesis} field (the
$\mathrm{P}=\mathrm{NP}$ constant-length decoder).
\begin{lstlisting}
theorem v13_upperLowerClash
    (L : GaugeBufferedLockedInterface ...)
    (P : ParameterRecord L) :
    UpperLowerClash L P
\end{lstlisting}
\textbf{Status (b), conditional --- and this is the crux of the whole audit.} The
theorem is a proved implication from the nine-field ledger $L$ plus a
\texttt{ParameterRecord} that \emph{bundles the two explicitly self-flagged open
inputs}. Its own audit tags exactly those two of seven fields \texttt{.openInput}.
Because the lower chain forces $\eta\le\Kpoly$ while the upper hypothesis asserts
$\Kpoly<\eta$, a \texttt{ParameterRecord} is jointly contradictory --- so the
theorem encodes the \emph{clash architecture}, not an unconditional falsehood or a
separation. Its clean axiom print certifies the implication is valid; it does
\emph{not} certify $\mathrm{P}\neq\mathrm{NP}$.

\paragraph{A naming caution.} The module \texttt{PNPv13AtomicEvidenceBudget}
formalizes the \emph{charged-occurrence bookkeeping} that the \S7.9 interface
export demands --- the no-double-counting / no-omission discipline that any such
coordinate sum must obey --- together with concrete obstruction countermodels. It
does \emph{not} prove the manuscript's quantitative Theorem~7.23 ($o(t)$ budget);
the safe-leakage and gauge-rank estimates live only as abstract interface fields.
The bookkeeping algebra itself is unconditional:
\begin{lstlisting}
theorem coordinateSummedCost_le_atomBudget_of_noDoubleCounting
    (hno : S.NoDoubleCounting) : S.coordinateSummedCost <= S.atomBudget
theorem noDoubleCounting_iff_allPositiveCostAtomsCharged_of_coordinateSummedCost_eq_atomBudget
    (heq : S.coordinateSummedCost = S.atomBudget) :
    S.NoDoubleCounting <-> S.AllPositiveCostAtomsCharged
\end{lstlisting}
and a companion module exhibits a finite surface where a double-counted atom and
an omitted atom \emph{cancel}, so aggregate budget equality holds while both
structural failures persist --- a machine-checked warning that the aggregate
budget alone certifies neither side condition.

\subsection{The interface as a finite consistency suite}
\label{sec:interface}
The manuscript itself flags the pressure point (Rmk.~4.5): on the single-message
support the target bit $B_j=\ell_j(\MY)$ is a mathematical function of the full
public instance $Y$, so $B_j=f_j(Y)$. The full public input therefore
\emph{cannot} be classified neutral; only a target-blind public skeleton
$Y_{\mathrm{neu}}$ can, and every target-relevant use of the remaining
$Y_{\mathrm{chg}}$ must normalize to charged safe-buffer or hidden-gauge evidence.
This is the decisive soundness condition of the whole route --- and it is the one
a formalization can pin down finitely, before any concentration estimate. The
development enforces it as a suite of finite consistency lemmas over the interface,
each an unconditional theorem:
\begin{itemize}
  \item message-opposite coupled pairs must agree on a target-blind skeleton, not
        on the full $Y$: same-full-$Y$ opposite pairs are empty (single-message),
        so any statement pairing opposite messages at fixed $Y$ is vacuous;
  \item a pair-neutral atom family cannot generate the target
        ($B_j=g(N(\omega))$ with $N$ pair-neutral forbids a nontrivial
        message-opposite coupling) --- the neutral skeleton must be target-blind;
  \item the full public input carries derivative mass: if $B_j=f_j(Y)$ then every
        message-opposite coupling puts unit mass on public-bit disagreements, so
        $Y$ cannot be folded into the neutral class;
  \item the full $\sigma$-field $\sigma(Y)$ is not admissible conditioning for the
        current coordinate: a $C$-measurable balanced bit cannot have
        $\Pr[B_j=1\mid C]=\tfrac12$ on positive-probability atoms, so an
        admissible history may contain only a target-blind projection of $Y$;
  \item a boundary summary that is \emph{sufficient} for $B_j$ forces mixing error
        $\ge\tfrac12$, so the pivot summary must be genuinely non-sufficient;
  \item no opaque run-atom: the raw evidence syntax has \emph{no}
        observer-output constructor, so an arbitrary polynomial-time computation
        cannot be inserted as one uncharged primitive --- it must expand through
        the interface and be normalized by CD-ENF (\S\ref{sec:spine}).
\end{itemize}
These are the finite obligations a concrete ensemble must satisfy, and they are the
checkable core of the interface: they say precisely where the scaled Phase-E family
failed (\S\ref{sec:inadmissible}), and they are what a candidate ensemble must
pass rather than assume. What they do \emph{not} supply are the quantitative
estimates --- max-qSSM, gauge-rank entropy, boundary-law mixing --- which remain
interface hypotheses (\S\ref{sec:scope}).

\subsection{OURS: the charged-public repair has a linear budget}
\label{sec:charged-public}

The preceding inconsistency uses D.31's classification of the complete public
catalog as neutral.  The direct repair is to split that same catalog into
pair-neutral primitives and primitives with charged expansions.  This does
remove the literal contradiction, but it exposes a quantitative obstruction.
For the exact D.48 coupling $\Gamma_j$ at target coordinate $j$, let
\[
  D_j=\{(\omega_0,\omega_1):
    \text{some charged public primitive has different values at }
    \omega_0,\omega_1\}.
\]
This is the ordinary union of charged-primitive disagreement events; its
definition contains no target predicate.  Exact phase marginals give
$B_j(\omega_0)\ne B_j(\omega_1)$ with $\Gamma_j$-probability one.  On any
positive-mass pair outside $D_j$, every charged primitive agrees by definition
and every neutral primitive agrees by the retained Definition~7.4 condition.
Full-catalog observability then makes the public instances equal, and D.8
public-fiber rigidity makes the target bits equal, a contradiction.  Therefore
\[
  \Gamma_j(D_j)=1,
  \qquad
  \sum_{j\in S}\Gamma_j(D_j)=|S|.
\]
Lean proves the pointwise identity, its finite-set sum, and the strict corollary
that no coefficient $c<1$ upper-bounds the total on a nonempty $S$:
\begin{lstlisting}
theorem v13D48_chargedPublicDisagreementMass_eq_one :
    chargedPublicDisagreementMass D48 theta m t j = 1
theorem v13D48_chargedPublicDisagreementTotal_eq_card :
    chargedPublicDisagreementTotal D48 theta m t S = S.card
theorem v13D48_chargedPublicDisagreementTotal_not_subunit :
    c < 1 -> S.Nonempty ->
    not (chargedPublicDisagreementTotal D48 theta m t S <= c * S.card)
\end{lstlisting}

This is an internal consistency and budget theorem for the displayed coupling
architecture.  It supplies no circuit lower bound, oracle separation, or
arithmetized lower bound, and therefore makes no claim to cross the
relativization, natural-proofs, or algebrization barriers.  Its force is the
narrower one proved above: every construction retaining the listed premises
pays the same linear charged-public term.

A resumable exact transport census supplied the finite verdict before the
general proof.  It exhausts all nonconstant Boolean targets and charged masks
through three public bits: 2,092 candidate target/mask pairs, of which 530 admit
the exact conditional phase marginals together with neutral-fiber agreement.
None has optimum below one; the minimum is sharp, while the largest optimum in
the census is $12/7$.  Integral primal flows and the coefficient-one dual
certificate are checked independently in Lean in dimensions one, two, and
three.  The strongest localization canary reuses one charged atom for every
target: the number of distinct charged atoms stays one, but the
coordinate-summed mass is still exactly $|S|$.  Paying that atom only once would
discard the coordinate multiplicity already isolated by the atomic-budget
no-double-counting theorem.

Thus changing D.31 alone cannot repair the advertised $o(|S|)$ Atomic Evidence
Budget.  A surviving route must alter another structural premise, absorb a
linear public term and replace the lower-bound architecture, or obtain its
sublinear estimate from a genuinely different quantity.

\section{The concrete instantiation: Phase E, the observer ladder, and a
refuted family}
\label{sec:instantiation}

The manuscript's remaining weight is the concrete ensemble. The formalization's
Phase-E work is where it is most valuably \emph{negative}, and the honesty
protocol of \S\ref{sec:honesty} earns its keep.

\subsection{A concrete smoke test that works}
\texttt{V13PhaseEConcrete} builds a genuine four-world locked unit-CNF instance
with an isolation row, proves it has a unique witness, and exhibits a real nonzero
target gap $\Gap=\tfrac12$ (a finite \texttt{norm\_num} fact over the four
worlds). All nine interface obligations are discharged one by one on this instance
--- \textbf{status (a)}, but explicitly a smoke test: the caveats note that scaled
max-qSSM and scaled boundary-law mixing remain separate obligations.

\subsection{A scaled family, proved inadmissible}
\label{sec:inadmissible}
\texttt{V13PhaseEScaled} attempts a parameterized hard family --- and proves its
own construction broken. The public input sets the locked target tag equal to the
target itself, so a single public coordinate determines the target:
\begin{lstlisting}
theorem phaseEScaled_familyInadmissible_publicTargetTag (m k : Nat) :
    exists coordinate : PhaseEScaledPublic m k -> Bool,
      forall omega,
        coordinate (phaseEScaledPublicInput omega) = phaseEScaledTarget omega
\end{lstlisting}
\textbf{Status (a), unconditional} (axioms $\{\texttt{propext}\}$). This violates
the manuscript's own ``no public target tags'' requirement (Hyp.~4.21), so the
family's obligation map re-tags all nine fields \emph{inadmissible}. The lesson,
carried forward as a design rule: a candidate ensemble must be pinned by theorem to
carry no uncharged target-bearing public atom, or it silently prints the answer.

\subsection{The observer ladder}
\texttt{V13ObserverLadder} climbs the scaled family and records, at each rung, a
machine-checked fact --- most of them negative. A $q=1$ observer that reads the
public target-lock wins with probability $1$
(\texttt{phaseEScaled\_targetLockObserver\_success\_eq\_one}); target-blind juntas
and parities sit at exactly $\tfrac12$; the full random-switching lift is
\emph{pinned, not proved}, as \texttt{PhaseEScaledSwitchingStatementNeeded}
(status (c)); and hardness is proved \emph{equivalent} to the open $\StarSW$
half-bound:
\begin{lstlisting}
theorem phaseEScaled_payloadDomination_iff_starSW ... :
    CoarseDominationAll payloadSummary target decoderSuccess slack
      <-> StarSW decoderSuccess slack
\end{lstlisting}
This equivalence is the honest localization: on this family, ``a local rule
dominates every decoder'' is not weaker than the average-case hardness one is
trying to prove --- it is the same statement.

\subsection{The linear replacement route, and a lesson from formalization}
\label{sec:truefirst}
After the scaled family was proved inadmissible, a concrete linear-algebra testbed
was opened (the Roadmap ties it under \texttt{v13RealRungOne*} /
\texttt{v13ObserverLadder}): public instance $(A,\,Ax)$ over $\FF^m$ with $A$ a
certified invertible linear map, and a family of row-query observers on it. Two
success bounds hold \textbf{unconditionally} on this route (axioms
$\{\texttt{propext},\ \texttt{Classical.choice},\ \texttt{Quot.sound}\}$), using a
crude one-time union-bound constant:
\begin{lstlisting}
-- sequential q-row observers:
--   uniformSequentialQRowSuccess observer i0 <= 1/2 + 4*(2^q - 1)/2^m
-- no-target bit-junta observers:
--   NoTargetBitJuntaSuccess i0 observer <= 1/2 + 4*2^j/2^m
\end{lstlisting}
A fixed-map parity observer's success obeys an exact trichotomy --- $1$, $0$, or
exactly $\tfrac12$ (status (a)). The \emph{sharp} $1/2+2^q/2^m$ bound for general
causal row queries is open for $q\ge 2$ (a fan of asserted \texttt{Prop} counting
obligations, status (c)/(d)); the $q\le 1$ cases are discharged, and a
machine-checked \emph{negative} shows the sharp bound is \emph{false} for a
target-row-reading observer at $m=2$, which is exactly why the construction restricts to
the no-target event.

This route is also where the formalization taught us something about
\emph{stating} events. The natural step-indexed ``first coset hit at step $t$''
event, used as a counting target, turned out to be \emph{false as stated}: it
carried no ``no earlier hit'' clause, so an observer that re-reads a row over a
prefix that already generates the target makes \emph{every} world in the prefix
class hit. The refutation is an explicit constructed observer, not an abstract
objection:
\begin{lstlisting}
def rowShearGeneratedRereadObserver (i0 : Fin m) (hm : 1 < m) :
    SequentialRowObserver m 3 where
  chooseRow transcript :=
    match transcript.length with
    | 0 => i0
    | 1 => finSpare i0 hm
    | _ + 2 => i0
  decideFromTranscript := fun _ => 0
-- ...ConditionedCountingBound_not_of_generated_reread_prefix_gap :
--   not (ConditionedCountingBound i0 observer)     -- status (a), a refutation
\end{lstlisting}
The repair restores the missing minimality: the corrected \emph{true-first} event
adds ``no coset hit at any earlier step,'' and with that clause the conditioned,
packing, and counting bounds all close \emph{unconditionally}. The crown counting
lemma is a conditioned replay of a two-row shear embedding applied at the hit row;
because the shear fixes the already-read rows, the conditioning is free and the
constants land exactly. The refuted step-indexed surfaces are kept in the
development, documented against their refuting theorems, because a refutation of a
plausible statement is itself a finding. With the corrected event, these bounds
assemble into an unconditional closure of ``rung one'' on both samplers --- a
unified success $\le\tfrac12+\varepsilon$ headline with an explicit rung ledger ---
and the route's separation endpoint follows from an $\StarSW$ hardness input by an
implication whose axiom print is \emph{empty}: pure plumbing, asserting no
separation. (This is the concrete-instantiation frontier; the evidence spine of
\S\ref{sec:spine} is the more settled core.)

\subsection{The linear gauge-CNF regression carrier and the faithful M4 specification}
\label{sec:realM4}
The current \texttt{V15RealLinearCNFEnsemble} and
\texttt{V15SmallSingleMessageCNFEnsemble} are frozen regression carriers, not the
manuscript's M4 ensemble.  The general linear carrier unit-locks the decoded witness
coordinates and has one free Boolean gauge coordinate.  It is useful for testing
generic SAT/readout, gauge-action, and bit-fixing machinery, but it has no regioned
neutral/buffer/locked/gauge/readout geometry and cannot supply the growing gauge
entropy or buffer law used by the analytic argument.

Its principal manuscript-facing result is negative.  When the full concrete
Appendix-I formula syntax is public, that syntax determines the target and the
readout.  Accordingly,
\texttt{v13RealLinearNoTargetRowsGaugeCNFAppendixICNFFormula\_noPublicTargetTags\_obstruction}
and
\texttt{v13RealLinearNoTargetRowsGaugeCNFAppendixICNFFormula\_noPublicReadoutTags\_obstruction}
prove that the no-public-tag disciplines \emph{fail} on this carrier.  A theorem for
a deliberately smaller neutral skeleton does not repair the full-syntax failure.
Likewise, the carrier's Appendix-D-shaped read predicate asserts
\texttt{message = targetBit}; its resulting \texttt{PublicMessageInvariant} is
premise-baking and is not evidence that D.8 was constructed from bounded-arity
lock/readout constraints.

The manuscript-facing work uses one common size- and clock-indexed ensemble.
\texttt{V13FaithfulQuantitativeFrontiers} states the
conditional hidden-gauge product law, a nontrivial indexed finite gauge action,
full-public-syntax coverage, max-qSSM, finite-set bounded incidence together with
the simultaneous Atomic Evidence Budget, conditional boundary mixing, the
fixed-clock Theorem-10.9 probability bound, and the Section-11 upper side on the
same object at $D^\ast$.  \texttt{PNPv13FaithfulM4Spec} states the five-region
Appendix-D/I type layer, the $x/g/z$ quotient equations and uniform gauge lift,
lock/readout and buffer predicates, legal probes, sampler support, compatible
couplings, and uniform CNF compilation. The concrete regioned scaffold proves
sampler mechanics, quotient equations, D.30 full-syntax coverage, a positive-rank
free gauge action, quotient-conditioned uniform lift, and the exact adaptive
hidden-gauge product law for every legal prefix and unsupported finite coordinate
set.

The scaffold's free XOR connector refutes D.8 by two supported completions with
different messages. A broader search and a machine-checked affine theorem close
the free-linear lock family; full-rank public parity systems make the message
algebraically recoverable, while small synthesized CNFs merely bake the desired
message into public syntax. These findings motivated a final reconciliation of
the exact Appendix-D and Section-7 roles rather than another carrier search.

The exact faithful target now also records three requirements used by the
neutral-zero step: Appendix~D.31 neutrality of every primitive obtained solely
from public template syntax, extensional observability of the advertised full
public catalog, and Definition~7.4 / Hypothesis~7.5 pair-neutrality on every pair
in the support of the D.48 opposite-phase coupling. A nonempty switched-target
guard prevents vacuous satisfaction. Lean proves
\begin{lstlisting}
theorem v13M4OpenConstructionObligations_uninhabited :
    not (Nonempty (V13M4OpenConstructionObligations E G C Primitive CNFVar))
\end{lstlisting}
The proof chooses a positive-mass D.48 coupling pair. Exact marginals place both
endpoints in sampler support. D.31 and Definition~7.4 make every complete public
valuation equal; full-catalog observability makes the public instances equal;
D.8 then makes the designated message coordinate equal. The opposite-phase
marginals make that same coordinate unequal, a contradiction.

This no-go is independent of lock arity, linearity, geometry, buffer behavior,
gauge action, and all four analytic packages.  Charging public syntax contrary
to D.31 is the direct consistency repair, but the OURS result in
\S\ref{sec:charged-public} proves that its D.48 charged-disagreement term is
exactly linear, not $o(|S|)$.  A viable revision must therefore weaken D.8,
change the D.48 phase coupling, replace the Section-7 support-wide neutrality
rule, abandon full public observability, or replace the lower-bound architecture
so that it does not require a sublinear charged-public term. The observability
option conflicts with the stated observer model. The four analytic packages ---
max-qSSM; bounded incidence plus the Atomic Evidence Budget; conditional
boundary mixing; and fixed-clock global message incompressibility --- remain
open mathematics, but they cannot inhabit the jointly inconsistent mechanical
interface without such a route revision.

\section{Obstructions and reroutings}
\label{sec:obstructions}

The move from v12 to v13 was not cosmetic; it routed around a specific, now
machine-checked obstruction. We record the live reroutings here; the superseded
v12 route in full is Appendix~\ref{app:v12}.

\paragraph{The calibration defect, and the kernel-flip repair.} v12's calibration
(Lemma~4.8 / App.~A.17) needed, at a fixed local input, exchangeability of the
witness bit under a promise-preserving involution $T_i$. \texttt{tiInputMap} sends
the third coordinate $b\mapsto b\oplus a_i$, so it fixes the full input
\emph{iff} the column $a_i$ is zero
(\texttt{tiInputMap\_eq\_self\_iff\_zeroColumn}), a vanishing $m^{-\Theta(1)}$
fraction of columns (\texttt{not\_calibrationFullInputPreservation\_on\_nonzeroColumns},
status (a)). The repair that strengthens the step is a \emph{kernel-flip}
involution: flip the witness by a kernel vector $w\in\ker(A)$ with $w_i=1$; this
toggles the target bit while fixing $b$ (since $Aw=0$) and the rest of the local
statistic, giving \emph{exact} neutrality, expressed as a cardinality-preserving
pairing of the two witness-bit fibers:
\begin{lstlisting}
theorem kernelFlip_exactNeutrality_card
    (hw : IsKernelVector A w) (hwi : w i = 1) :
    Fintype.card (KernelBitFiber A b i 0)
      = Fintype.card (KernelBitFiber A b i 1)
\end{lstlisting}
Exact neutrality removes the broken calibration lemma outright and makes the
associated sparsification stack unnecessary.

\paragraph{The No-Threading impossibility.} Any hope of \emph{enriching} a single
local statistic to be simultaneously neutral and sufficient is blocked, and for a
logical rather than analytic reason: the target bit is a deterministic function of
the instance, so a sufficient statistic pins it to $\{0,1\}$, which neutrality
forbids from equalling $\tfrac12$.
\begin{lstlisting}
theorem noThreadingLemma (phi : Phi) :
    not (Neutral u x /\ Sufficient u x)
\end{lstlisting}
\textbf{Status (a).} Because the obstruction is logical, no concentration or
log-Sobolev inequality can ever supply the missing domination; this is the
structural reason the hardness input $\StarSW$ cannot be made a free lemma, and
part of why v13 abandons the locality midpoint entirely.

\paragraph{The steelman conditional.} The repaired abstract implication consumes
two premise packages: kernel-flip neutrality plus the open $\StarSW$ hardness
input, and a \texttt{PNPConditionalFramework} supplying pivot independence,
compression from success, and the self-reduction clash.
\begin{lstlisting}
theorem pnp_steelman_starSW_frameworkBundle_conditional
    (hKernel : KernelFlipNeutrality F)
    (hSW : StarSWAverageCaseWitnessBitHardness F) :
    F.pNeNPClaim
\end{lstlisting}
\texttt{pnpSteelmanFrameworkPremiseBundleAudit} lists the three non-$\StarSW$
framework premises.  \textbf{Status (b), conditional}: the composition theorem is
axiom-free, but it proves none of those premises and asserts no unconditional
separation.  A future concrete theorem must establish every premise on the same
faithful M4 ensemble.  ($\StarSW$ itself is not weaker than the target: it is
contradicted in the $\mathrm{P}=\mathrm{NP}$ regime and is equivalent, on the
ensemble, to the separation --- which is why No-Threading forbids deriving it for
free.)

\section{Status, scope, and the open frontier}
\label{sec:scope}

\paragraph{Machine-checked unconditionally.} The syntactic CD-ENF
semantics-preservation theorem (not the open real-execution primitive expansion)
(\S\ref{sec:spine}); the atomic-evidence \emph{bookkeeping} algebra and its
cancellation/exactness countermodels; non-vacuity of the nine-field interface; the
Phase-E \emph{negatives} (the scaled family is inadmissible; the observer ladder
stops at a $q=1$ target-lock counterexample; hardness $\Leftrightarrow\StarSW$);
the Roadmap-node refutations of stated readout and calibration steps; and, on the
linear route, the two crude-constant success bounds, the parity trichotomy, the
public-surface certificate, the $q\le1$ causal cases, and the true-first counting
close.

\paragraph{Machine-checked only modulo explicit premise bundles.} The legacy
Phase-A theorem is a conditional certificate eliminator; the faithful Phase-A
record still requires normalized exact phase marginals, actual-trace capture, and
the refinement comparison.  The Phase-C coherence lemmas use the legacy thin
interface.  The \textbf{Phase-D upper--lower clash} is an implication from the full
\texttt{ParameterRecord}, which supplies the phase budget, lower framework, kernel
neutrality, $\StarSW$ transfer, and the incompatible Section-11 upper premise.
These are reduction skeletons, not a separation.

The no-target sequential result is \emph{not} conditional on the former pinned
counting proposition.  \texttt{V13RealLinear\_rungLedger} records unconditional
half-plus-epsilon bounds for both the adjusted no-target sequential sampler and the
bit-junta sampler, together with unconditional Crux-2; only the
$\StarSW$--framework endgame remains conditional.  Separately, the faithful
quantitative frontiers remain open statement records. The complete faithful
Appendix-D/I target is no longer merely uninhabited by known constructions: its
nonempty form is refuted by
\texttt{v13M4OpenConstructionObligations\_uninhabited}.

\paragraph{Route revision required.} Before the analytic frontiers can be a
same-object completion program, at least one of D.8, D.48, Definition~7.4 /
Hypothesis~7.5, or full public observability must be revised and the affected
lower-bound argument reproved.  Revising D.31 alone to charge the remaining
public syntax restores consistency but, by \S\ref{sec:charged-public}, forces a
coefficient-one linear disagreement budget and does not restore Theorem~7.23's
$o(|S|)$ conclusion. Independently open work includes the sharp $2^q/2^m$
causal counting bounds for $q\ge2$, the random-switching lift
\texttt{PhaseEScaledSwitchingStatementNeeded}, the $\StarSW$ average-case
hardness input, and the boundary/buffer contraction hypotheses.

\paragraph{$\mathrm{P}$ versus $\mathrm{NP}$ remains open.} We make no claim in
either direction. The value of the formalization is the verified plumbing and the
exact localization of the open inputs, together with a body of machine-checked
counterexamples that keep specific over-strong readings of the route honest. The
latest result proves that no nonempty object can simultaneously satisfy the exact
joint faithful target as currently stated; the manuscript architecture must change
before a concrete ensemble can close it.

\section*{Provenance}
\addcontentsline{toc}{section}{Provenance}
The manuscript distilled in \S\ref{sec:route} is Ben Goertzel, \emph{A
Quantale-Weakness Route to $\mathrm{P}\neq\mathrm{NP}$ via CD Evidence
Normalization and Gauge-Buffered Locked Ensembles} (v13, 20 April 2026), which
supersedes the earlier \emph{$\mathrm{P}\neq\mathrm{NP}$: A Non-Relativizing Proof
via Quantale Weakness and Geometric Complexity} (v12, 9 October 2025) discussed in
Appendix~\ref{app:v12}. The formalization is work of the MeTTapedia formalization
effort. The v13 evidence spine (Phases~A--D), Phase-E instantiation, and observer
ladder are the modules \texttt{V13EvidenceSpine}, \texttt{V13CDENF},
\texttt{V13GaugeBufferedLockedInterface}, \texttt{PNPv13AtomicEvidenceBudget},
\texttt{V13ConditionalClash}, \texttt{V13PhaseEConcrete},
\texttt{V13PhaseEScaled}, and \texttt{V13ObserverLadder}, with the itinerary in
\texttt{Roadmap.lean}; the v12 obstruction is \texttt{PostSwitchInputObstruction};
the steelman conditional and its inputs are \texttt{PNPSteelmanConditional},
\texttt{KernelFlipInvolution}, and \texttt{NoThreadingLemma}; the linear
replacement route is the \texttt{V13RealRungOne*} / \texttt{V13RealRungTwoBitJunta}
family; the frozen legacy staging spine and linear CNF regression/obstruction
carrier are \texttt{V15RealEnsembleSpine} and
\texttt{V15RealLinearCNFEnsemble}.  The faithful manuscript-facing statement layers
are \texttt{V13FaithfulQuantitativeFrontiers} and
\texttt{PNPv13FaithfulM4Spec}; the adaptive counting and final faithful-interface
verdict are in \texttt{V13FaithfulM4AdaptiveGaugeProduct},
\texttt{V13FaithfulM4CouplingObstruction}, and the non-vacuous
\texttt{V13M4OpenConstructionObligations} target.  The OURS charged-public
verdict and its finite primal/dual checker are
\texttt{PNPv13ChargedPublicBudgetObstruction} and
\texttt{PNPv13ChargedPublicBudgetFiniteCertificates}. Lean listings
are ASCII transliterations of the source declarations
(the sources are normative); every headline was checked with \texttt{\#print
axioms}. Per-declaration source links are omitted pending publication of the
development tree.

\appendix

\section{The superseded v12 route: a machine-checked obstruction in the
calibration step}
\label{app:v12}

The v12 manuscript separated $\mathrm{P}$ from $\mathrm{NP}$ by a
Switching-by-Weakness normal form (Thm.~4.2) that reduces every short global
decoder, after a short wrapper, to an $O(\log m)$-local per-block rule on the
post-switch input $u_i=(z,a_i,b)$ --- $z$ a sign-invariant feature, $(a_i,b)$
Valiant--Vazirani labels with $a_i=Ae_i$ --- on a masked-random Unique-SAT
ensemble; neutrality (Thm.~5.1) and template sparsification (Thm.~5.10) pin each
local rule near $\tfrac12$; independence across $\Theta(m)$ blocks gives per-program
success $2^{-\Omega(t)}$ and hence $\Kpoly\ge\eta t$, clashing with a constant
self-reduction upper bound under $\mathrm{P}=\mathrm{NP}$. The load-bearing step
was the \emph{calibration}/success-domination link (Lemma~4.8; App.~A.5,
Lemma~A.17), which derived exchangeability of the witness bit at a fixed $u$ from a
promise-preserving involution $T_i$.

The formalization (\texttt{PostSwitchInputObstruction}) found that $T_i$ acts by
$b\mapsto b\oplus a_i$: it preserves the reduced projection $(z,a_i)$ always
(\texttt{invariantProjection\_tiInputMap}) but the full input $(z,a_i,b)$
\emph{iff} $a_i=0$ (\texttt{tiInputMap\_eq\_self\_iff\_zeroColumn}), so the
fixed-$u$ exchangeability holds only on a vanishing $2^{-k}=m^{-\Theta(1)}$
fraction of columns. A finite two-point success-domination counterexample
(\texttt{finite\_successDomination\_counterexample}, axioms
$\{\texttt{propext},\ \texttt{Quot.sound}\}$) shows a $u$-measurable comparator
cannot dominate a global decoder merely by sharing the local input. The natural
repair --- coarsening to the $T_i$-invariant projection $(z,a_i)$ --- was proved
\emph{circular}: on that neutral interface, success domination is equivalent to the
average-case hardness it must prove (it renames the target). These are the
findings the v13 re-architecture routes around by discarding the locality midpoint;
the kernel-flip repair and the No-Threading impossibility of \S\ref{sec:obstructions}
are the constructive residue that carries into the v13 steelman conditional.

\section{A graveyard of disproven sub-routes}
\label{app:graveyard}

Each entry is a route or reading that was tried and closed; several are themselves
machine-checked theorems (that a stated property \emph{fails}).

\begin{description}
  \item[Fixed-input calibration via $T_i$ (v12).] Dead as stated: the involution
        moves $b$ off the fixed fiber on every nonzero column
        (Appendix~\ref{app:v12}). Superseded by the kernel-flip involution, which
        gives exact neutrality.
  \item[Coarse / reduced-projection repair.] Circular: on a neutral interface,
        ``every decoder is dominated by the best local rule'' is equivalent to
        $\StarSW$ (a two-point witness makes coarse-domination demonstrably fail).
        A closed door, not a weakening.
  \item[Analytic-concentration closure.] Retired by No-Threading: the obstruction
        to a neutral-and-sufficient statistic is logical, so no hypercontractivity
        or log-Sobolev device can close it.
  \item[Per-map capacity counting.] Arithmetically dead: a single adversarial map
        can host a constant fraction of hitting worlds, so the required smallness
        lives in the map \emph{ensemble}, not in any one map; the closure runs
        through a per-prefix partition and a \emph{conditioned} one-row density
        instead.
  \item[Surrogate-ERM ``distillation'' of domination.] Relativizes, hence (by
        Baker--Gill--Solovay) cannot establish a class-separating switching step;
        symmetrization projects onto an $\approx m$-bit invariant algebra, far
        richer than the $O(\log m)$-bit local statistic where neutrality lives.
  \item[H{\aa}stad-style $p$-random bit restriction.] Wrong tool for this family:
        the public bits are parities of hidden bits at a fixed witness, so random
        bit-fixing leaves live parities and the switching-lemma hypothesis fails;
        rerouted to gauge-compensation.
  \item[The naive $2^q/2^m$ row-observer constant.] Refuted at $m=2$ by a
        target-row observer; repaired to the honest
        $\tfrac12+4(2^q-1)/2^m$ crude-constant bound.
  \item[The scaled Phase-E hard family.] Proved \emph{inadmissible} --- a single
        public coordinate determines the target (\S\ref{sec:inadmissible}); the
        family prints the answer. Retained as a design rule: pin no-public-target-tag
        by theorem, or the ensemble is void.
  \item[Token-ledger false starts.] An early formalization tracked the argument as
        status \emph{tokens} with no representation of the actual SAT / Kolmogorov
        / measure objects; disavowed as proof content and replaced by the finite
        evidence calculus grounded in the manuscript's objects. Lesson carried
        forward: never let a family be chosen that carries the answer as a public
        tag, and demand admissibility by theorem.
\end{description}

\end{document}
