\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{listings}
\geometry{margin=1in}

\lstdefinestyle{lean}{
  basicstyle=\ttfamily\small,
  breaklines=true,
  columns=fullflexible,
  keepspaces=true,
  showstringspaces=false,
  frame=single,
  framesep=4pt,
  xleftmargin=2pt,
  aboveskip=8pt,
  belowskip=8pt,
  literate=
    {ℝ}{{$\mathbb{R}$}}1
    {ℕ}{{$\mathbb{N}$}}1
    {ℤ}{{$\mathbb{Z}$}}1
    {λ}{{$\lambda$}}1
    {ε}{{$\varepsilon$}}1
    {Δ}{{$\Delta$}}1
    {κ}{{$\kappa$}}1
    {≤}{{$\leq$}}1
    {≥}{{$\geq$}}1
    {≠}{{$\neq$}}1
    {∧}{{$\wedge$}}1
    {∨}{{$\vee$}}1
    {¬}{{$\neg$}}1
    {→}{{$\rightarrow$}}1
    {↦}{{$\mapsto$}}1
    {∃}{{$\exists$}}1
    {∀}{{$\forall$}}1
    {∈}{{$\in$}}1
    {·}{{$\cdot$}}1
    {²}{{$^2$}}1
    {₀}{{$_0$}}1
    {₁}{{$_1$}}1
    {₂}{{$_2$}}1
    {₃}{{$_3$}}1
    {⟨}{{$\langle$}}1
    {⟩}{{$\rangle$}}1,
}
\lstset{style=lean}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{remark}{Remark}
\theoremstyle{definition}
\newtheorem{definition}{Definition}

\newcommand{\SUN}{\mathrm{SU}(N)}
\newcommand{\Lirr}{\lambda_{\mathrm{irr}}}
\newcommand{\dmax}{d_{\max}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\Pleq}{P_{\leq \dmax}}

\title{A Machine-Checked Audit of the Extended-Extraction\\
RG Contraction in the Wilson-Lattice / OS Route\\
to a 4D Yang--Mills Mass Gap}
\author{The MeTTapedia formalization effort}
\date{July 2026}

\begin{document}
\maketitle
\sloppy

\begin{abstract}
Ben Goertzel's manuscript \emph{Yang--Mills Mass Gap in 4D: RG Bootstrap,
Polymer Expansion, OS Reconstruction} (v14) proposes to construct a continuum
$\SUN$ Yang--Mills theory from Wilson lattice gauge theory via a multiscale
renormalization-group (RG) bootstrap, a Koteck\'y--Preiss (KP) polymer expansion,
exponential clustering, and Osterwalder--Schrader (OS) reconstruction. Its
technical keystone is an \emph{extended-extraction} contraction
$\Lambda=C_1\Lirr<1$, with advertised constant near $2224$ and
$\Lirr=2^{-13}$ at block factor $2$ and extraction depth $16$.

The scalar bootstrap arithmetic is exact, but the advertised Wilson recursion
constant is \emph{not derived in v14 as written}. The main-text factor product
is $33152$ at $b=2$; Appendix~O's different proposed factorization is
$11088/5$ when its extraction factor is $2$. A sign-only repair of the printed
extraction series is insufficient once the displayed multivariate
multiplicities are retained.

We construct a concrete finite Wilson-polynomial realization on actual
group-valued link fields. In its explicit coefficient-majorant norm,
canonical-dimension truncation is gauge invariant and has operator constant
$1$. This does not transfer from v14's range-only specification of
$P_{\mathrm{ext}}$: a skew projection onto the same low-coordinate range has
arbitrarily large coefficient norm. We prove the correct transfer theorem from
explicit basis and dual-jet matrices with their column-sum conditioning bounds,
but v14 does not provide those data for the dimension-$16$ action sector. A
direct source reconciliation shows that they cannot be reconstructed uniquely
from the present text: Appendix~F.4 uses equations of motion to identify the
operator space, while Appendix~O.9 explicitly retains EOM operators in an
off-shell basis; neither section supplies lattice Wilson representatives or a
quotient basis, and Appendix~I's explicit dual jets stop at the distinct
dimension-$4$ observable sector.
Likewise, regrouping connected families by union support has norm $1$; the
factor $14$ is exactly a \emph{local rooted branching count}
$2(2\cdot4-1)$, not a bound on the total contacts of two extended polymers.
The fluctuation big-$O$ and weighted cumulant-generation estimates also require
quantitative proofs on the actual Wilson RG map.

A third machine-checked round works on the exact $\mathrm{SU}(2)$, $b=2$
Wilson block with normalized Haar measure and decides the extraction stage
from three sides. (i)~Representative-wise hard truncation is not well-defined
on the actual trace-word quotient: for the centered trace words
$a=2-\Tr(U)$ and $b=2-\Tr(U^2)$, Cayley--Hamilton forces $a^3b-4a^4+a^5=0$
with monomial canonical dimensions $16$, $16$, $20$; truncation at $16$
deletes only $a^5$, and the truncated expression evaluates to $-32$ on the
holonomy $\mathrm{diag}(i,-i)$ while the exact expression vanishes
identically. (ii)~Two corrected constructions nevertheless carry exact
norm-below-two extractors --- the full associated-graded jet chart
($131071/65536<2$) and the one-plaquette trace quotient ($31/16<2$); with
Appendix~O's other factors kept unchanged, the resulting conditional constant
$90832203/40960\approx2217.6$ closes the two-source bootstrap at depth $16$
and fails at depth $15$. (iii)~Neither survivor transfers to v14's canonical
$(F,D)$ operator space: a dimension-$18$ scalar descendant has radial degree
only $6$ (resp.\ $3$), so both extractors retain it, and the dimension-$6$
descendant $\partial^2\Tr(F^2)$ is zero in the manuscript's
integration-by-parts quotient yet has a nonzero gauge-invariant realization
on an explicit three-plaquette block. The transfer socket required before any
Wilson-RG intertwiner is therefore uninhabited as written, under both the
on-shell and off-shell relation policies.

A fourth machine-checked round tests the replacement census against the exact
symmetry of the finite-spacing lattice. On an explicit $\mathrm{SU}(2)$ Cartan
link chart, the sum of squared normalized Wilson potentials over the six
coordinate plaquettes is gauge invariant and has canonical dimension $8$.
Its exact fourth jet is $6\sum_{\mu<\nu}F_{\mu\nu}^{4}$. A rational orthogonal
rotation changes the corresponding quartic from $1$ to $337/625$. Thus the
observable is hypercubic-invariant but not $O(4)$-invariant. Every span of
Appendix~O.9.3's Lorentz-scalar contractions remains $O(4)$-invariant, so it
cannot be complete for actual lattice Wilson observables. This obstruction
closes the off-shell, on-shell EOM, Bianchi/IBP, trace, Cayley--Hamilton, and
postponed-IBP variants of the same Lorentz-only target. It does not rule out a
finite coordinate system: it forces either a genuinely hypercubic census at
finite lattice spacing or a separately proved continuum/Symanzik projection
with a quantitatively controlled Lorentz-breaking remainder.

A fifth machine-checked round begins the hypercubic branch. On the unpadded
derivative-free Cartan quartic carrier, all $126$ monomials are classified by
signed $H(4)$ orbit certificates. Exactly four admissible orbit basis
functions remain; evaluation at their representatives gives four duals and
the identity conditioning matrix, and every hypercubic-covariant rational
quartic coefficient function is reconstructed from them. The exact Wilson
fourth jet has coordinate vector $(6,0,0,0)$ in this basis. The subspace of
curvature observables invariant under every $O(4)$ transformation is proper,
and the pure-fourth Wilson polynomial is a nonzero class in the corresponding
Lorentz-breaking quotient. The attempted dimension-$16$
extension then reaches a different terminal obstruction: its
fixed-width raw carrier retains inactive padding as part of equality. Two
distinct encodings with zero active fields and derivatives have identical
active syntax. Any basis faithful to active syntax must give them equal rows,
whereas the proposed exact census requires a right inverse and hence distinct
identity-matrix rows. Lean proves that no invertible exact census on this
padded carrier can have every basis column padding-invariant. The next
finite-spacing construction must use an unpadded dependent syntax or an
explicit padding quotient before relation rows and dimension-$16$ duals are
meaningful.

\textsc{Ours:} the unpadded dimension-$16$ replacement is now constructed
and connected by an explicit equivalence to the exact-dimension subtype of
the active $(F,D)$ syntax. Its raw carrier has
$23{,}027{,}949{,}358{,}636{,}282{,}675{,}200$ elements. Character averaging
over all $384$ signed coordinate permutations gives rank-$16$ invariant
tensor multiplicities $22{,}379{,}179$ (scalar) and $22{,}368{,}256$
(pseudoscalar); after the exact
$5{,}361{,}612{,}271{,}200$ trace/derivative layouts are included, the raw
invariant coefficient spaces have dimensions
$119{,}988{,}480{,}745{,}781{,}344{,}800$ and
$119{,}929{,}915{,}854{,}943{,}027{,}200$. These are exact raw-carrier
dimensions before antisymmetry, Bianchi, EOM, integration by parts, trace,
or Cayley--Hamilton rows, not a physical operator basis. On the separately
complete derivative-free Cartan octic sector, $1287$ monomials reduce to
$17$ signed-orbit coordinates with exact duals and identity conditioning.
The actual Wilson eighth jet occupies only the pure-octic coordinate, with
Symanzik coefficient $-a^{12}/20160$. For bounded constant Cartan curvature,
the normalized Wilson density differs from its $O(4)$-invariant quadratic
term by at most $(5/8)a^4M^4$ and converges to that term as $a\to0$. The
two-block boundary-cochain lift retains extraction constant $1$; carrying the
three still-conditional analytic factors gives budget $5544/5$, whose
two-source arithmetic closes first at depth $15$. This is a quantitative
tree-level constant-Cartan restoration theorem, not an interacting
Symanzik theorem or a constructive continuum limit.

Thus there is presently no derived constant $C_{\mathrm{true}}$ for the Wilson
recursion. The support recurrence, two-marked glue identity, stopping-scale
polymer estimates, Wilson reflection positivity, and continuum/OS construction
remain route-specific open inputs. The finite $\mathbb{Z}_2$, $\mathbb{Z}_3$,
and $Q_8$ gaps checked in Lean are real but Clay-irrelevant
(single-link, strong-coupling, finite). The Yang--Mills mass gap remains open;
we make no claim about it.
\end{abstract}

\section{The problem and Ben Goertzel's route}

\subsection{The Millennium problem and the lattice strategy}

Fix the gauge group $G = \SUN$ with $N \geq 2$ and let $\mathbb{R}^4$ be
Euclidean space. The Yang--Mills mass-gap problem asks for the construction of a
nontrivial continuum quantum Yang--Mills theory on $\mathbb{R}^4$ with gauge
group $G$, satisfying the Wightman / Osterwalder--Schrader axioms, whose
reconstructed Hamiltonian has a unique vacuum and a strictly positive spectral
gap on the orthocomplement of the vacuum.

Goertzel's v14 manuscript follows Wilson's lattice regularization. One
discretizes $\mathbb{R}^4$ as a hypercubic lattice $a\mathbb{Z}^4$ with spacing
$a>0$, with link variables $U_{x,\mu}\in G$ on oriented nearest-neighbor links.
The plaquette variable is the parallel transporter around an elementary square,
\[
  U_{x,\mu\nu} \;=\; U_{x,\mu}\,U_{x+a e_\mu,\nu}\,U_{x+a e_\nu,\mu}^{-1}\,U_{x,\nu}^{-1},
  \qquad 1 \leq \mu < \nu \leq 4,
\]
and the Wilson action penalizes deviation of plaquettes from the identity,
\[
  S_{\Lambda,a}(U) \;=\; \beta \sum_{p\subset\Lambda} V(U_p),
  \qquad \beta = \frac{2N}{g^2},
  \qquad V(U) := 1 - \tfrac{1}{N}\mathrm{Re}\,\Tr(U) \in [0,2].
\]
Weak coupling is $\beta \gg 1$. The strategy is: (Step 1) start from the
well-defined finite-dimensional lattice integral; (Step 2) run a multiscale RG
bootstrap controlling the effective theory across all scales; (Step 3)
establish exponential clustering at a fixed physical scale $\ell_*$ via a KP
polymer expansion; (Step 4) transfer clustering from the coarse scale back to
the fine scale with a glue / back-propagation lemma; (Step 5) reconstruct the
continuum Hilbert space, vacuum, and Hamiltonian by OS, with the clustering rate
becoming the spectral gap; (Step 6) verify nontriviality through a nonzero
third cumulant of the action density.

\subsection{The continuum-limit obstruction and extended extraction}

In any RG scheme one must show that the ``irrelevant'' sector (operators of
canonical dimension $>4$) contracts at each step:
\[
  \| K^{\mathrm{irr}}_{j+1}\| \;\leq\; \Lambda\, \|K^{\mathrm{irr}}_{j}\| + (\text{source terms}),
  \qquad \Lambda < 1.
\]
The manuscript identifies a sharp obstruction in the \emph{naive} scheme, where
one extracts only the relevant and marginal operators of dimension $\leq 4$.
Under rescaling, a dimension-$d$ operator scales by $b^{4-d}$, so the leading
irrelevant operators (dimension $6$) contract by $b^{-2} = 0.25$ for $b=2$. But
the RG step also recombines polymers, contributing a combinatorial constant
$C_1$. The manuscript advertises the working bound $C_1 \leq 2224$ for $b=2$;
if that value were established, the naive gain would be
\[
  \Lambda_{\mathrm{naive}} \;=\; 2224\, b^{-2} \;=\; 2224 \times 0.25 \;=\; 556 \;>\; 1,
\]
an \emph{expanding} map: initial smallness would grow like $556^{J}$ over
$J\sim|\log a_0|$ steps and diverge as $a_0\to 0$.

The proposed resolution is \emph{extended extraction}. Instead of extracting
only dimension $\leq 4$ operators, one extracts all gauge-invariant local
operators up to canonical dimension $\dmax = 16$ (for $b=2$). The irrelevant
sector then begins at dimension $\dmax+1 = 17$ and contracts by
\[
  \Lirr \;=\; b^{\,4-(\dmax+1)} \;=\; b^{\,3-\dmax} \;=\; 2^{-13} \;\approx\; 1.2\times 10^{-4}.
\]
With the same advertised value, the proposed contraction factor becomes
\[
  \boxed{\;\Lambda \;=\; C_1\,\Lirr \;\leq\; 2224 \cdot 2^{-13} \;\approx\; 0.27 \;<\; 1.\;}
\]
The manuscript presents this as genuine contraction ``with substantial slack.''
The audit below verifies this arithmetic only \emph{conditional on the supplied
constant}; it refutes the available derivations of that constant as written.
The price is tracking a finite-dimensional vector of higher couplings
$\vec g_j = (g_j^{(4)},g_j^{(6)},\dots,g_j^{(\dmax)})$ rather than the single
gauge coupling; the manuscript argues these are perturbatively small and do not
affect the universal one-loop beta-function coefficient
$b_0 = 11/(3\cdot 16\pi^2)$, which is determined entirely by local ultraviolet
information.

\subsection{The recombination constant and the extraction-projection norm}

Appendix~O proposes the factorization
\[
  C_1 \;\leq\; C_{\mathrm{fluct}} \cdot C_{\mathrm{cumulant}} \cdot C_{\mathrm{recomb}} \cdot C_{\mathrm{extract}}
  \;\leq\; 1.65 \times 3b^4 \times 14 \times 2,
\]
which at $b=2$ equals $11088/5=2217.6$, rather than exactly $2224$.
Appendix~F.5 displays a different factor product which equals $33152$ at
$b=2$; the two ledgers are inconsistent. The last Appendix-O factor
$C_{\mathrm{extract}} = \|\Pleq\|_{\mathrm{op}}$ is the operator norm of the
extraction projection onto the finite-dimensional space of operators of
dimension $\leq \dmax$. The manuscript bounds it (its Computation~O.7(d)) by
\[
  \|\Pleq\|_{\mathrm{op}} \;\leq\; \sum_{d=0}^{\dmax} \binom{\#\mathrm{indices}}{d}\,(r_1/r_0)^{-d}
  \;\leq\; 1 + O\!\big((r_0/r_1)^{\dmax}\big),
\]
and asserts $\|\Pleq\|_{\mathrm{op}} \leq 2$ for $r_1/r_0 = 1/2$ and $\dmax=16$.
The literal negative exponent grows, but changing only its sign does not turn
the displayed multivariate sum into a one-dimensional geometric series. More
fundamentally, v14 specifies $P_{\mathrm{ext}}$ by its range and does not give
the dimension-$16$ invariant basis, dual jets, or conditioning estimates needed
to determine its operator norm. We return to the proved realization and the
transfer obstruction in \S\ref{sec:honest}.

\section{What we formalized}

The formalization lives in the Lean namespace
\texttt{Mettapedia.QuantumTheory.YangMills}. We summarize the four checked
components: the contraction predicate, the knife-edge arithmetic, the finite
strong-coupling gaps with their finite OS reconstruction, and the
continuum-open gating. All theorem and definition names below are reproduced
verbatim from the corresponding modules.

\subsection{The extended-extraction contraction predicate}

The module \texttt{Mettapedia.QuantumTheory.YangMills.RGBootstrap} models the
route's contraction obligation as a predicate over a recombination constant
$C$, block factor $b$, and extraction depth $\dmax$. The irrelevant scaling
factor is $b^{3-\dmax}$ (an integer power, since the useful cases have
$\dmax>3$), and a contraction is a nonnegative constant whose product with the
irrelevant scale is below $1$.

\begin{lstlisting}
/-- Irrelevant scaling factor `b^(3-dmax)` used by the extended-extraction
discussion.  The exponent is an integer because the useful cases have
`dmax > 3`. -/
def irrelevantScale (b dmax : ℕ) : ℝ :=
  (b : ℝ) ^ (3 - (dmax : ℤ))

/-- The route-level contraction audit for a combinatorial constant and an
irrelevant scaling factor. -/
def HasRGContraction (C scale : ℝ) : Prop :=
  0 ≤ C ∧ 0 ≤ scale ∧ C * scale < 1

/-- The extended-extraction audit specialized to `λ = b^(3-dmax)`. -/
def HasExtendedExtractionContraction (C : ℝ) (b dmax : ℕ) : Prop :=
  HasRGContraction C (irrelevantScale b dmax)
\end{lstlisting}

A threshold lemma in the same module records the exact content of the predicate:
for $b>0$ and $\dmax\geq 3$, the contraction \texttt{HasExtendedExtractionContraction
C b dmax} holds if and only if $0 \leq C < b^{\dmax-3}$. Thus the entire
arithmetic content of the route is the comparison of $C$ with the threshold
$b^{\dmax-3}$.

\subsection{The knife-edge arithmetic}

The module machine-checks that the advertised constant contracts at $\dmax=16$
and that the exact one-step gain is $2224\cdot 2^{-13} = 139/512 < 1/3$:

\begin{lstlisting}
/-- The advertised numerical slack: `2224 * 2^-13 < 1`. -/
theorem rgContraction_2224_two_sixteen :
    HasExtendedExtractionContraction 2224 2 16 := by
  refine ⟨by norm_num, by rw [irrelevantScale_two_sixteen]; norm_num, ?_⟩
  rw [irrelevantScale_two_sixteen]
  norm_num

/-- Exact advertised one-step gain for the extended-extraction constants. -/
theorem rgGain_2224_two_sixteen_eq :
    (2224 : ℝ) * irrelevantScale 2 16 = (139 : ℝ) / 512 := by
  rw [irrelevantScale_two_sixteen]
  norm_num
\end{lstlisting}

Crucially, the same constant does \emph{not} contract at the nearest even
extraction depth below the advertised one. At $\dmax=14$ the threshold is
$2^{11}=2048<2224$, so the contraction is arithmetically false; the module
proves that any contraction at $\dmax=14$ would force $C<2048$, and hence that
$2224$ fails:

\begin{lstlisting}
/-- Any contraction proof at `dmax = 14` must improve the linear recombination
constant below `2048`.  The manuscript's advertised bound `2224` is therefore
insufficient for this lower extraction depth. -/
theorem rgContraction_two_fourteen_forces_constant_lt_2048
    {C : ℝ} (h : HasExtendedExtractionContraction C 2 14) :
    C < 2048 := by
  have hprod : C * irrelevantScale 2 14 < 1 := h.2.2
  rw [irrelevantScale_two_fourteen] at hprod
  nlinarith

/-- Same-constant blocker at the nearest even extraction depth below `16`. -/
theorem not_rgContraction_2224_two_fourteen :
    ¬ HasExtendedExtractionContraction 2224 2 14 := by
  intro h
  have hC : (2224 : ℝ) < 2048 :=
    rgContraction_two_fourteen_forces_constant_lt_2048 h
  norm_num at hC
\end{lstlisting}

This is the knife edge: the choice $\dmax=16$ is exactly what makes the
advertised constant contract, and the manuscript's own table shows
$\dmax\in\{10,12,14\}$ all fail against $C_1\leq 2224$ while $\dmax=16$ succeeds.
The module \texttt{Mettapedia.QuantumTheory.YangMills.RGCrux} packages this into
a route-level statement: a mass-gap route that keeps the advertised constant
$2224$ but uses an even extraction depth strictly below $16$ cannot exist, since
the required contraction is arithmetically false before any OS / clustering
layer is reached.

\begin{lstlisting}
/-- Same-constant lower-extraction certificate in the manuscript's even
canonical-dimension shape: the cutoff is strictly below `16`, is even, and uses
the same advertised recombination bound `2224`. -/
def SameConstantEvenBelowSixteenRGCertificate (dmax : ℕ) : Prop :=
  dmax < 16 ∧ Even dmax ∧ HasExtendedExtractionContraction 2224 2 dmax

/-- No same-constant RG certificate exists for an even manuscript-shape cutoff
strictly below `16`. -/
theorem not_sameConstantEvenBelowSixteenRGCertificate
    {dmax : ℕ} :
    ¬ SameConstantEvenBelowSixteenRGCertificate dmax := by
  intro hcert
  have hdmax : dmax ≤ 14 :=
    even_lt_sixteen_le_fourteen hcert.1 hcert.2.1
  exact (not_rgContraction_2224_two_of_dmax_le_fourteen hdmax) hcert.2.2
\end{lstlisting}

A strengthened companion theorem,
\texttt{not\_atLeast2048EvenBelowSixteenRGCertificate}, shows that any even
lower-extraction repair below $\dmax=16$ would need a genuinely sharper constant
($C<2048$), not merely the advertised one. We stress that this is an honest
delimiter of the arithmetic surface, not a refutation of the route: at the raw
natural number $\dmax=15$ the same constant \emph{does} contract
($2^{12}=4096>2224$), and the module records this explicitly so that the
obstruction is read precisely as an even canonical-dimension statement matching
the manuscript's dimensions $4,6,\dots,\dmax$.

\subsection{Finite strong-coupling spectral gaps and finite OS reconstruction}

The module \texttt{Mettapedia.QuantumTheory.YangMills.FiniteOSReconstruction}
formalizes the finite algebraic core of OS reconstruction: a reflection-positive
finite kernel induces a positive pairing on observables, and a transfer operator
that is self-adjoint for that pairing descends to the pairing quotient and
remains self-adjoint there. On this base, the modules
\texttt{Z2StrongCouplingGap} and \texttt{Z3StrongCouplingGap} build explicit
finite single-link abelian lattice gauge models. For $\mathbb{Z}_2$, the
one-link heat-kernel transfer at heat time $1$ has eigenvalues $1$ and
$\exp(-1)$, so the dimensionless gap is $-\log(\exp(-1)/1)=1$:

\begin{lstlisting}
theorem z2StrongCouplingGap_eq_one :
    z2StrongCouplingGap = 1 := by
  simp [z2StrongCouplingGap, z2StrongCouplingLambdaTwo,
    z2StrongCouplingLambdaOne, z2StrongCouplingRatio, Real.log_exp]

/-- End-to-end finite lattice theorem: the explicit `Z₂` strong-coupling model is
nontrivial, reflection positive, has an OS transfer operator, and has
dimensionless transfer gap at least `1`. -/
theorem z2StrongCoupling_latticeYangMills_massGap_landmark :
    ∃ _ : Z2StrongCouplingGapCanary,
      (∃ x y : Z2OneLinkConfig, x ≠ y) ∧
        OSReflectionPositive z2StrongCouplingKernel ∧
        z2StrongCouplingGap = 1 ∧
        (1 : ℝ) ≤ z2StrongCouplingGap ∧
        0 < z2StrongCouplingGap := by
  exact
    ⟨z2StrongCouplingPositiveCanary,
      z2OneLinkConfig_nontrivial,
      z2StrongCouplingKernel_reflectionPositive,
      z2StrongCouplingGap_eq_one,
      z2StrongCouplingGap_lower_bound_one,
      z2StrongCouplingGap_positive⟩
\end{lstlisting}

The $\mathbb{Z}_3$ module proves the analogous landmark with two mean-zero
transfer eigenvectors and the same unit gap. These theorems are unconditional
and non-vacuous: they exhibit genuine reflection positivity, a genuine finite OS
transfer reconstruction, and a strictly positive spectral gap. They are also
kept rigorously separate from any continuum claim. Each module carries an
explicit scaling diagnostic showing that a finite gap need not survive a naive
continuum schedule. For the heat-time schedule $t(a)=a^2$, the \emph{physical}
gap (dimensionless gap divided by lattice spacing) closes as $a\to0$:

\begin{lstlisting}
/-- A concrete gap-closing schedule for the finite model under the heat-time
scaling `t(a)=a²`: the physical gap can be made smaller than any positive
threshold by taking the lattice spacing small enough. -/
theorem z2QuadraticHeatTime_physicalGap_closes :
    ∀ ε : ℝ, 0 < ε →
      ∃ a : ℝ,
        0 < a ∧ a < ε ∧
          z2HeatTimePhysicalGap a (a ^ 2) < ε := by
  intro ε hε
  refine ⟨ε / 2, by linarith, by linarith, ?_⟩
  have hne : ε / 2 ≠ 0 := by linarith
  rw [z2QuadraticHeatTime_physicalGap_eq hne]
  linarith
\end{lstlisting}

\subsection{The continuum endpoint is gated open}

The module \texttt{Mettapedia.QuantumTheory.YangMills.ProofState} records a
status ledger over the route's nodes. The finite RG / extraction surfaces are
marked \texttt{checked} or \texttt{refuted} as appropriate, but the continuum
mass-gap endpoint carries an explicit \texttt{openGoal} status, gated behind a
constructive-QFT promotion barrier (continuum measure, Euclidean covariance,
reflection positivity, OS reconstruction, and Hamiltonian mass-gap transfer ---
none of which is represented for the RG / extraction route, which supplies only
a finite ledger):

\begin{lstlisting}
/-- The final mass-gap endpoint remains an open goal in this lane. -/
def yangMillsMassGapEndpointNode : YangMillsProofNode where
  id := "yang-mills.mass-gap-endpoint"
  status := .openGoal
  truthValue := ⟨0, 95⟩
  evidence := "currentYangMillsMassGapEndpoint_blockedByConstructiveGate blocks promotion from the audited RG/extraction surfaces to a continuum mass-gap endpoint ..."
  nextObligation := "Connect the RG and extraction surfaces to a genuine continuum mass-gap statement only after the constructive-QFT gate, OS/Hamiltonian transfer dependency packet, challenge-world interface packet, and mass-gap promotion gate clear."

theorem yangMillsMassGapEndpointNode_open :
    yangMillsMassGapEndpointNode.status = .openGoal := by
  rfl
\end{lstlisting}

A companion theorem \texttt{currentYangMillsMassGapEndpoint\_blockedByConstructiveGate}
records that the endpoint is open, the constructive checks are all unrepresented,
and the only supplied interface is the finite RG / extraction ledger. In short,
the formalization does not overclaim: nothing in it asserts a continuum mass gap.

\section{Honest status and scope}\label{sec:honest}

This lane is, by construction, conservative; we now state precisely what is and
is not established.

\paragraph{The contraction constant is an input, not a conclusion.}
Every arithmetic theorem above takes the recombination constant as a
\emph{given real number}. The predicate \texttt{HasExtendedExtractionContraction
C b dmax} is a statement about $C$, $b$, $\dmax$ alone; the checked facts
\texttt{rgContraction\_2224\_two\_sixteen} and
\texttt{not\_rgContraction\_2224\_two\_fourteen} verify the comparison
$C \lessgtr b^{\dmax-3}$ for the specific value $C=2224$. Nothing in the
formalization derives that $2224$ (or any $O(1)\cdot b^4$ bound) is the correct
value of the manuscript's recombination constant. The Lean ledger is therefore
faithful to the route's bookkeeping but agnostic about the route's hardest
analytic claim.

\paragraph{The extraction projection: realization succeeds, range-only transfer
fails.}
The sign-only repair is insufficient: even with positive exponent, the displayed
binomial/multivariate multiplicities make the corrected finite sum exceed $2$
once at least two coordinates are present. We therefore constructed the natural
finite polynomial realization rather than treating the omission as a verdict.
For a finite Wilson block of actual group-valued links, plaquette holonomies,
and a conjugation-invariant Wilson potential, finite polynomials in the
plaquette coordinates are gauge invariant. In the explicitly defined weighted
coefficient-majorant norm, canonical-dimension truncation has operator constant
$1$ (module \texttt{WilsonBlockMajorant}).

This is our realization of the manuscript's extraction idea, not an attribution
to v14. It cannot be transferred to v14's $P_{\mathrm{ext}}$ from the specified
range alone: \texttt{projectionRangeSpecification\_does\_not\_imply\_bound\_two}
constructs an idempotent skew projection onto the same low-coordinate range
that violates the bound $2$. The positive transfer theorem
\texttt{coefficientL1\_basisJetProjection\_le} shows exactly what would suffice:
explicit basis and dual-jet matrices whose coefficient-column bounds multiply.
The construction attempt is certified in
\texttt{Dimension16WilsonExtractionCertificate}: F.4's on-shell relation
policy and O.9's off-shell policy disagree already on the displayed
dimension-$6$ divergence-square operator; the exact block quotient, lattice
representatives, finite basis, dimension-$16$ dual jets, biorthogonality, and
conditioning matrices are not supplied. Appendix~I's explicit jets concern
the separate observable projection $P^{\mathrm{obs}}_{\leq4}$. Hence the
extraction component is not a standing erratum repair, and $C_1$ is not derived.

\paragraph{Hard truncation does not descend to the actual trace-word quotient.}
The third round replaces schematic carriers by the exact object: the
$\mathrm{SU}(2)$, $b=2$ Wilson block with normalized Haar measure --- $81$
vertices, $216$ positive links of which $8$ are internal, $216$ plaquettes,
an internal spanning tree with $7$ co-tree links, exact boundary-plus-co-tree
coordinates, the gauge action, the normalized Wilson potential, and the
fixed-boundary product-Haar reference integral with its logarithmic effective
block action (modules \texttt{SU2WilsonBlockPilot},
\texttt{SU2MajorantRepairDecision}). On this object the question ``is
canonical-dimension truncation even well-defined on the gauge-invariant
quotient?'' has a negative, intrinsic answer. For any $U\in\mathrm{SU}(2)$
the Cayley--Hamilton identity gives $\Tr(U^2)=\Tr(U)^2-2$; writing
$a=2-\Tr(U)$ and $b=2-\Tr(U^2)$ (each of canonical dimension $4$), the exact
relation $b=4a-a^2$ yields
\[
  a^3b-4a^4+a^5 \;=\; 0,
\]
whose three monomials have construction-derived canonical dimensions $16$,
$16$, $20$. Truncation through dimension $16$ deletes only $a^5$; on the
explicit holonomy $\mathrm{diag}(i,-i)$ the truncated expression evaluates to
$-32$, while the exact left-hand side vanishes on every field. Hence the
semantic kernel is not stable under representative-wise hard truncation, no
function on the evaluated trace-word quotient agrees with that truncation,
and the corresponding descended extraction certificate is uninhabited
(module \texttt{SU2CayleyHamiltonTruncationObstruction}). The witness uses
only the Cayley--Hamilton relation --- no equations-of-motion quotient and no
boundary-extension convention --- so it applies to both of v14's relation
policies, and it refutes any uniform-in-$N$ architecture that requires
representative-wise hard truncation of redundant Wilson trace words.

\paragraph{Corrected constructions do carry norm-below-two extractors.}
Truncation is, of course, definable on a \emph{chosen basis}, and the third
round constructs the two natural repairs exactly. The full associated-graded
jet chart on the gauge-fixed block ($7$ co-tree links, $3$ Lie coordinates
each, hence $21$ coordinates) carries the symmetric-monomial basis of jets
through total degree $16$, with identity jet matrix and biorthogonal
coefficient duals; radial Taylor extraction at radius ratio $1/2$ has the
exact operator constant
$\sum_{d=0}^{16}2^{-d}=131071/65536<2$
(modules \texttt{SU2AssociatedGradedExtraction},
\texttt{SU2AssociatedGradedExtractionDecision}). Independently, the evaluated
one-plaquette trace algebra is exactly a one-variable polynomial algebra: the
normal-form theorem $b=4a-a^2$ (proved semantically complete via an infinite
Cayley-rotation family) gives the basis $1,a,a^2,a^3,a^4$ through dimension
$16$, with extraction constant $\sum_{d=0}^{4}2^{-d}=31/16<2$ (module
\texttt{SU2IndependentTraceBasis}). Keeping Appendix~O's other factors
unchanged, the associated-graded constant yields the conditional ledger value
\[
  C_{\mathrm{proposed}}
  \;=\; \tfrac{90832203}{40960} \;\approx\; 2217.583 \;<\; 2224,
\]
whose two-source gain at depth $16$ is
$90832203/335544320\approx0.2707<1/3$, while depth $15$ does not close. This
is conditional bookkeeping: the fluctuation, cumulant, and recombination
factors remain unproved on the actual map. Two exact theorems keep these
constructions honestly separated from v14's object: the full graded chart has
dimension $12{,}875{,}774{,}670$ and admits no linear equivalence onto any
coordinate space of dimension at most $1851$, so the manuscript's schematic
count requires a genuine invariant quotient that v14 does not construct; and
the radial norm used here is a precise repair, not provably the manuscript's
intended multivariate norm.

\paragraph{Neither survivor transfers to the canonical $(F,D)$ space.}
The transfer question is then decided negatively by two independent
machine-checked obstructions (module \texttt{V14FDQuotientTransferNoGo},
headline \texttt{v14\_fullFD\_quotientTransfer\_noGo}). \emph{Derivative
blindness:} v14 counts canonical dimension as $2\cdot\#F+\#D$ (its O.9.1),
but radial degree on either chart is blind to derivative factors. The scalar
descendant $(\partial^2)^3[(\Tr F^2)^3]$ has canonical dimension $18$ yet
radial degree $6$ on the associated-graded chart and $3$ on the trace chart,
so both norm-below-two extractors \emph{fix} it --- and an explicit two-cell
zero-boundary sixth-difference witness evaluates to $-6$, so the retained
operator is nonzero. Both survivors therefore fail to implement the
dimension-$\leq16$ projection of F.4.2, independently of the choice of
quotient basis (\texttt{not\_associatedRadialImplementsCanonicalCutoff},
\texttt{not\_independentRadialImplementsCanonicalCutoff}).
\emph{Integration-by-parts/block incompatibility:} v14's local norm (F.3)
lives on ordinary functions on a finite block retaining boundary data, while
both relation branches identify integrated total derivatives with zero. The
dimension-$6$ descendant $\partial^2\Tr(F^2)$ is gauge invariant and
evaluates to $1$ on an explicit three-plaquette block field (a purely
quadratic associated-grade witness gives the same value, so higher Taylor
terms are not the cause). An ordinary block-functional realization would have
to send one quotient class to both the zero function and a nonzero boundary
descendant; the faithful transfer sockets --- exact-Wilson, pure
associated-graded, and every RG-compatible extension --- are therefore
uninhabited under both relation policies. Consequently no corrected recursion
constant propagates from the constructions above into the bootstrap. The
obstruction is structural rather than informational: supplying the omitted
dimension-$16$ coordinates or conditioning matrices cannot make either
extractor into the canonical $(F,D)$ projection. A viable replacement needs a
derivative-aware filtration whose truncation provably agrees with
$2\cdot\#F+\#D$, together with a boundary-aware complex that retains
total-derivative descendants on each block as boundary cochains and imposes
integration by parts only at global recombination; constructing exactly that
replacement is the current object of this formalization.

\paragraph{The actual-lattice census cannot be Lorentz-only.}
The derivative-aware boundary-cochain repair makes the filtration and local
boundary bookkeeping explicit, but a further obstruction appears before its
coordinate basis or dual jets can be supplied. Appendix~O.9.3 enumerates only
Lorentz-invariant complete contractions. The exact finite-spacing Wilson
lattice has only hypercubic symmetry, and the module
\texttt{SU2LatticeFDCensusNoGo} supplies a gauge-invariant canonical-dimension
$8$ observable whose fourth Cartan jet is
\[
  6\bigl(F_{01}^{4}+F_{02}^{4}+F_{03}^{4}
      +F_{12}^{4}+F_{13}^{4}+F_{23}^{4}\bigr).
\]
An explicit rational orthogonal rotation changes its normalized quartic value
from $1$ to $337/625$. Hence no finite span of the $O(4)$-invariant O.9.3 jets
contains it. The necessary spanning core, the O.9.2 off-shell certificate, and
the F.4.3 on-shell certificate are all formally uninhabited. The witness is
derivative-free, so changing EOM, Bianchi, integration-by-parts, trace,
Cayley--Hamilton, or boundary-cochain reduction policies cannot repair this
same-target symmetry mismatch. The result is already an $N=2$ counterexample
to an architecture asserted uniformly for $\mathrm{SU}(N)$. It is not a no-go
for a hypercubic-complete basis or for a controlled continuum projection.

\paragraph{The first hypercubic census succeeds at quartic order and refutes
its padded extension.}
The unpadded carrier of degree-four monomials in the six oriented two-form
components has cardinality $126$. Exact signed-orbit certificates divide it
into four admissible $H(4)$ orbit types --- a pure fourth power, adjacent
squares, opposite squares, and a rectangle product --- plus monomials killed
by negative stabilizers. Four signed orbit indicators obey the full
hypercubic covariance law, their representative evaluations form the
$4\times4$ identity, and they reconstruct every invariant rational
coefficient function. This is a complete result for the derivative-free
Cartan quartic restriction, not for the noncommutative $(F,D)$ quotient.
The actual gauge-invariant Wilson observable has exact fourth derivative equal
to the polynomial realization of coordinate vector $(6,0,0,0)$. Moreover, the
curvature observables invariant under every orthogonal spacetime matrix form a
proper linear subspace, and this pure-fourth polynomial defines a nonzero
class in the quotient by that subspace. Thus the Lorentz-breaking artifact is a
coordinate-level theorem, not merely an external rotation counterexample.

The fixed-width full carrier cannot supply that extension faithfully.
Inactive field and derivative slots are mathematically padding but remain
part of raw equality. The module
\texttt{V14HypercubicFDCensusPaddingNoGo} constructs two distinct encodings
of the empty active syntax and proves
\texttt{faithful\_dimension16\_exactCensus\_uninhabited}: if every basis
column ignores inactive padding, the two basis rows coincide; the required
right inverse instead makes them two different rows of the identity matrix.
This obstruction precedes Bianchi, EOM, integration-by-parts, trace, and
Cayley--Hamilton reduction. It does not show that an $H(4)$ basis cannot
exist. It shows that the next construction must first replace the raw carrier
by an unpadded/dependent syntax or quotient padding explicitly.

\paragraph{Our unpadded raw character census is exact through dimension
$16$.}
\textsc{Ours.} The replacement uses dependent active field and derivative
slots, so no inactive coordinate enters equality. An explicit equivalence
identifies its canonical-dimension-$16$ subtype with a separated presentation
consisting of an active trace/derivative layout and a rank-$16$ spacetime-axis
assignment; it commutes with the literal hypercubic action and preserves the
product of all active tensor signs. The induced linear equivalence identifies
the scalar and pseudoscalar covariance submodules on the original syntax with
the counted invariant fibers. The exact layout multiplicity is
$5{,}361{,}612{,}271{,}200$, and the complete raw carrier has
$23{,}027{,}949{,}358{,}636{,}282{,}675{,}200$ elements.

The standard signed four-vector representation of the literal $384$-element
hypercubic group is constructed over $\mathbb{Q}$. Reynolds-character
averaging, with all $24\times16$ group elements replayed by kernel-checked
certificate blocks, gives the scalar multiplicities
\[
 (1,0,1,0,4,0,31,0,379,0,5611,0,87979,0,
   1400491,0,22379179)
\]
and pseudoscalar multiplicities
\[
 (0,0,0,0,1,0,20,0,336,0,5440,0,87296,0,
   1397760,0,22368256)
\]
at tensor ranks $0$ through $16$. Since the layout coordinate is inert under
$H(4)$, the rank-$16$ values imply exact raw invariant-space dimensions
$119{,}988{,}480{,}745{,}781{,}344{,}800$ and
$119{,}929{,}915{,}854{,}943{,}027{,}200$. No relation is manufactured by
the count: field antisymmetry, Bianchi, EOM, integration by parts, trace, and
Cayley--Hamilton remain explicit quotient rows. Thus this theorem completes
the genuine raw-carrier census, but not the noncommutative physical operator
basis or its dual chart.

\paragraph{Our first syntactic quotient removes derivative labels exactly.}
\textsc{Ours.} The active derivative slots in the raw carrier are labeled,
whereas an operator depends only on the ordered derivative word.  Interpreting
\texttt{derivativeOrder} explicitly as the map from ordered positions to
active labels separates every raw derivative presentation into a label
permutation and the owner--axis datum at each ordered position.  Equality of
the latter data is proved equivalent to a unique relabeling of the active
derivative slots.  Consequently the actual quotient of the original exact
dimension-$16$ subtype is linearly represented by ordered derivative words;
no canonical representative is assumed.

This alpha quotient commutes with the literal $H(4)$ action and preserves the
product of all active tensor signs.  Before any physical identity is imposed,
the layout multiplicity falls from $5{,}361{,}612{,}271{,}200$ to
$5{,}030{,}751$, and the corresponding carrier has exactly
$21{,}606{,}911{,}019{,}319{,}296$ elements
(\texttt{HypercubicDimension16AlphaReduction}).  Field-label alpha
equivalence and the standard field antisymmetry, Bianchi, EOM, integration by
parts, covariant-derivative commutator, trace, and $\mathrm{SU}(2)$
Cayley--Hamilton identities remain to be imposed.  The commutator identity is
listed separately because $[D_\mu,D_\nu]X=[F_{\mu\nu},X]$ is necessary to
identify noncommuting derivative words and is not supplied by Bianchi or
integration by parts.

\paragraph{Our quantitative restoration theorem is tree-level and
constant-Cartan.}
\textsc{Ours.} The derivative-free Cartan octic restriction contains $1287$
monomials and exactly $17$ signed $H(4)$ orbit coordinates. Representative
evaluation supplies exact duals and the identity conditioning matrix, hence
analysis and synthesis both have coefficient-sup factor one. For the actual
$\mathrm{SU}(2)$ Cartan link field, the normalized Wilson eighth jet is
\[
  -2a^{12}\sum_{\mu<\nu}F_{\mu\nu}^{8},
\]
so division by $8!$ leaves only the pure-octic coordinate, equal to
$-a^{12}/20160$. If $|F_{\mu\nu}|\leq M$ and
$|a^2F_{\mu\nu}|\leq1$, the actual six-plaquette density obeys
\[
 \left|\mathcal W_a(F)-\sum_{\mu<\nu}F_{\mu\nu}^{2}\right|
 \leq \frac58 a^4M^4,
\]
and therefore converges to the $O(4)$-invariant quadratic density along every
eventually positive lattice-spacing net tending to zero. The corresponding
two-block rotation error is at most $(5/2)a^4M^4$.

The $17$ coordinates lift to the postponed-integration-by-parts boundary
complex; shared-boundary coboundaries cancel under global recombination, and
the degree-zero quotient retains rank $17$. The newly derived extraction
factor is exactly one. Keeping the fluctuation, cumulant, and recombination
bounds as explicit hypotheses gives the conditional recursion budget
$5544/5$; the two-source bootstrap then closes at depth $15$ and fails at
every depth at most $14$. None of these statements constructs an interacting
continuum measure, proves uniform Symanzik estimates for quantum
correlators, verifies Osterwalder--Schrader reconstruction, or proves a mass
gap.

\paragraph{The finite gaps are real but Clay-irrelevant.}
The $\mathbb{Z}_2$ and $\mathbb{Z}_3$ spectral gaps are honest theorems, but
they are abelian, single-link, strong-coupling, and finite. They exemplify the
finite OS-reconstruction mechanism; they are not lattice approximations to a
continuum $\SUN$ theory, and the accompanying scaling diagnostics show that the
physical gap can close under a naive continuum schedule. They establish the
machinery, not the target.

\paragraph{The continuum mass gap is correctly open.}
The continuum endpoint is gated \texttt{openGoal} with no claimed support, and
the constructive-QFT prerequisites are all marked unrepresented. The
formalization makes no claim, in either direction, about the existence of a
continuum Yang--Mills mass gap.

\section{What remains, exactly}\label{sec:remains}

\subsection*{Machine-checked since the first version of this report}

A second formalization round closed several items that the first version listed
as open, and sharpened others into theorems:

\begin{itemize}
  \item \textbf{The two-source bootstrap threshold.} Linear contraction
    ($\Lambda<1$) is \emph{not} sufficient for the manuscript's bootstrap; the
    scalar induction closes iff $a = C\,b^{\,3-\dmax} \leq 1/3$
    (\texttt{scalar\_bootstrap\_two\_sources}). At $C=2224$, $b=2$: depth $14$
    fails even linear contraction, depth $15$ contracts linearly but the
    bootstrap \emph{fails}
    (\texttt{not\_twoSourceBootstrapSlack\_2224\_two\_fifteen}), depth $16$
    closes. The true reason for $\dmax=16$ is the $1/3$ threshold, not parity of
    the depth --- and the threshold is \emph{dynamical}: an explicit nonlinear
    toy orbit realizes the recursion with equality and exits the
    $\varepsilon^{*}$-ball in one step at depth 15
    (\texttt{toyRG\_ball\_escape\_two\_fifteen},
    \texttt{benToyRGBootstrapRealization}).
  \item \textbf{The extraction realization and transfer obstruction.} The
    manuscript's literal displayed sum is $\geq 3$ for every
    $n\geq 1$ and never $\leq 2$
    (\texttt{three\_le\_literalExtractionOperatorSum},
    \texttt{not\_literalExtractionOperatorSum\_le\_two}). On an explicit
    finite Wilson-block polynomial algebra, coefficient-majorant truncation is
    norm one and gauge invariant (\texttt{WilsonBlockMajorant}). A matrix
    column-sum theorem transfers through explicit basis and dual jets; v14 does
    not provide these for $P_{\mathrm{ext}}\leq16$, and a skew-projection
    counterexample proves that no bound follows from the range alone
    (\texttt{ExtendedExtractionTransfer}). The source-certificate audit further
    proves that F.4 and O.9 select different EOM relation policies and records
    the absent lattice representatives, quotient basis, dimension-$16$ jets,
    biorthogonality, and conditioning rows
    (\texttt{Dimension16WilsonExtractionCertificate}).
  \item \textbf{The support-growth dichotomy.} The two collar-growth statements
    the manuscript makes are inequivalent, and both branches are now tight
    theorems: a coarsen-then-thicken recurrence $r_{j+1}\leq r_j/b + A$ yields
    the uniform bound $r_0/b^{J} + Ab/(b-1)$, while a thicken-only recurrence
    $r_{j+1}\leq r_j + A$ yields exactly $r_0 + AJ$
    (\texttt{support\_growth\_dichotomy}).
  \item \textbf{Gap $\Leftrightarrow$ clustering, finite class.} Reflection
    positivity, self-adjointness, and a $q$-contraction on the vacuum
    complement give exponential decay of truncated two-point functions at rate
    $-\log q$ (\texttt{abs\_truncatedTwoPoint\_le\_exp}); conversely, RP plus
    per-vector moment decay $\langle v, T^{n}v\rangle \leq C_v q^{n}$ on a
    dense subset gives the gap
    (\texttt{eigenvalue\_abs\_le\_of\_moment\_decay}) --- note the
    \emph{per-vector} constants: only the rate must be uniform, which weakens
    what the manuscript's Assumptions K.7/M.5 need to supply. A regression
    records that an additive $t$-independent tail defeats the conclusion
    (\texttt{moment\_decay\_additive\_defeat}), so large-field remainders must
    decay, not merely be small.
  \item \textbf{A non-abelian instance.} The quaternion group
    $Q_8\subset SU(2)$ single-link model: machine-checked non-commutativity
    ($ij=k\neq -k=ji$), reflection positivity, spectral gap carried by the
    four-dimensional spin isotypic component, and clustering; together with the
    $\mathbb{Z}_2$ instance this discharges the lattice-side inputs
    (\texttt{massGap}, \texttt{reflectionPositive}, \texttt{clustering}) of the
    finite continuum-gate conditional
    (\texttt{z2\_continuumMassGap\_of\_reconstructionMachine}).
\end{itemize}

\subsection*{Machine-checked in the third round}

A third round moved from schematic carriers to the exact $\mathrm{SU}(2)$,
$b=2$ Wilson block (\S\ref{sec:honest}) and decided the extraction stage on
it:

\begin{itemize}
  \item \textbf{Hard truncation refuted intrinsically.} The Cayley--Hamilton
    relation $a^3b-4a^4+a^5=0$, with monomial dimensions $(16,16,20)$ and the
    explicit $-32$ evaluation, proves representative-wise canonical truncation
    is not well-defined on the evaluated trace-word quotient
    (\texttt{SU2CayleyHamiltonTruncationObstruction}).
  \item \textbf{Exact norm-below-two extractors constructed.} The
    $21$-coordinate associated-graded jet chart has extraction constant
    $131071/65536$ and the one-plaquette trace quotient has $31/16$, both
    certified with explicit bases, identity jet matrices, and biorthogonal
    duals; the conditional ledger value $90832203/40960\approx2217.6$ closes
    the two-source bootstrap at depth $16$ and fails at depth $15$
    (\texttt{SU2AssociatedGradedExtraction},
    \texttt{SU2IndependentTraceBasis}).
  \item \textbf{A certified dimension separation.} The full graded chart has
    dimension $12{,}875{,}774{,}670$ and admits no linear equivalence onto any
    space of dimension $\leq1851$, so v14's schematic operator count requires
    an invariant quotient the manuscript does not construct
    (\texttt{SU2AssociatedGradedExtractionDecision}).
  \item \textbf{The $(F,D)$ transfer socket is uninhabited as written.} The
    dimension-$18$/radial-degree-$6$ descendant and the
    integration-by-parts/block witness $\partial^2\Tr(F^2)$ jointly refute the
    faithful transfer sockets for both relation policies and all
    RG-compatible extensions
    (\texttt{v14\_fullFD\_quotientTransfer\_noGo}).
\end{itemize}

\subsection*{Machine-checked in the fourth round}

A fourth round constructed the derivative-aware boundary-cochain scaffold and
then decided whether its dimension-$16$ coordinate socket could be filled by
the manuscript's Lorentz-only operator census:

\begin{itemize}
  \item \textbf{The repaired filtration and boundary bookkeeping are
    mechanical.} The canonical-dimension filtration, boundary-aware cochain
    coordinates, coefficient projection, and conditional scalar bootstrap are
    machine-checked. Their analytic Wilson-RG factors remain explicit inputs.
  \item \textbf{The actual-lattice O.9 census is refuted at dimension $8$.}
    The exact $\mathrm{SU}(2)$ Wilson observable, Cartan chart, fourth-jet
    calculation, and rational rotation witness prove that the hypercubic
    quartic jet is not Lorentz invariant
    (\texttt{SU2LatticeFDCensusNoGo}).
  \item \textbf{Both relation branches and six same-target variants are
    closed.} Neither the off-shell O.9.2 policy nor the on-shell F.4.3 policy
    admits a complete Lorentz-only certificate. EOM, Bianchi/IBP,
    cyclic/multitrace, $\mathrm{SU}(2)$ Cayley--Hamilton, and postponed-IBP
    variants share the same uninhabited spanning core.
  \item \textbf{The live fork is explicit.} One must either enumerate an
    $H(4)$-complete finite-spacing basis and rederive its duals and constants,
    or prove a Symanzik/continuum projection with quantitative decay of the
    Lorentz-breaking artifact coordinates. No numerical factor transfers
    automatically from the refuted census.
\end{itemize}

\subsection*{Machine-checked in the fifth round}

The first branch of the live fork was pursued directly:

\begin{itemize}
  \item \textbf{The exact hypercubic group and finite raw syntax are
    mechanical.} Signed coordinate permutations form a concrete group of
    order $384$. The raw surface records field and derivative indices, trace
    cycles, derivative ownership/order, canonical dimension through $16$,
    scalar/pseudoscalar characters, and separate relation-family labels. A
    label still supplies no relation row by itself
    (\texttt{V14HypercubicFDCensus}).
  \item \textbf{The unpadded dimension-$8$ quartic census is complete.}
    The $126$ Cartan quartic monomials have checked signed-orbit certificates.
    Four surviving orbit functions form a basis, representative evaluation
    supplies exact duals, and the conditioning matrix is the identity
    (\texttt{V14HypercubicQuarticCensusCertificate},
    \texttt{V14HypercubicQuarticBasis}).
  \item \textbf{The actual Wilson and artifact coordinates are certified.}
    The Wilson fourth jet is exactly coordinate vector $(6,0,0,0)$. The
    $O(4)$-invariant function subspace is proper, and the pure-fourth
    polynomial is nonzero in its quotient
    (\texttt{V14HypercubicQuarticWilsonBridge}).
  \item \textbf{The padded dimension-$16$ extension is refuted.} Two distinct
    fixed-width encodings of the empty active syntax differ only in inactive
    padding. Any active-syntax-faithful basis gives them equal rows, which is
    incompatible with the right-inverse identity required by
    \texttt{ExactCensusCertificate}
    (\texttt{V14HypercubicFDCensusPaddingNoGo}).
  \item \textbf{The corrected carrier is specified without padding.} The
    obstruction identifies finite unpadded/dependent $(F,D)$ syntax, or a
    checked padding quotient, as the required carrier on which the $H(4)$
    action and relation rows must descend. No dimension-$8$ constant transfers
    automatically. The unpadded construction and its raw character census are
    supplied in the results below; the relation quotient remains separate.
\end{itemize}

\subsection*{Machine-checked on the unpadded dimension-$16$ carrier}

All constructions in this subsection are ours and are independent of any
claim that the manuscript already contains the needed census.

\begin{itemize}
  \item \textbf{The counted carrier is the actual active syntax.} Exact
    dimension-$16$ shapes are classified by $f\in\{0,\ldots,8\}$ with
    $d=16-2f$. A checked equivalence identifies the corresponding subtype of
    the unpadded raw $(F,D)$ syntax with the separated layout--rank-$16$
    tensor presentation, preserves the literal action and tensor sign, and
    induces a linear equivalence on the covariance submodules. Its exact
    cardinality is
    $23{,}027{,}949{,}358{,}636{,}282{,}675{,}200$
    (\texttt{HypercubicUnpaddedFDSyntax},
    \texttt{HypercubicRawFDDimension16Census}).
  \item \textbf{Derivative-label alpha equivalence is quotiented exactly.}
    The raw derivative order is separated into a disposable active-label
    permutation and the owner--axis word indexed by ordered positions.
    Equality of ordered words is equivalent to a unique relabeling; the
    quotient of the original exact carrier is explicitly equivalent to the
    reduced carrier, equivariant under $H(4)$, and tensor-sign preserving.
    Its exact layout and carrier counts are $5{,}030{,}751$ and
    $21{,}606{,}911{,}019{,}319{,}296$
    (\texttt{HypercubicDimension16AlphaReduction}).
  \item \textbf{The complete raw $H(4)$ character multiplicities are
    certified.} The standard signed-axis representation, all $384$ trace and
    determinant values, Reynolds projector, and rank-$0$--$16$ character
    averages are checked. At rank $16$ the scalar and pseudoscalar tensor
    multiplicities are $22{,}379{,}179$ and $22{,}368{,}256$; multiplication
    by the exact active-layout count gives the raw invariant-space dimensions
    displayed above (\texttt{HypercubicRawFDCharacterCensus},
    \texttt{HypercubicRawFDCharacterCertificate}).
  \item \textbf{The Cartan octic chart has exact conditioning.} The $1287$
    derivative-free monomials split into $17$ surviving signed orbits and
    negative-stabilizer orbits. The orbit indicators, representative duals,
    reconstruction theorem, and $17\times17$ identity matrix are certified
    (\texttt{HypercubicDimension16CartanCensus},
    \texttt{HypercubicDimension16CartanCertificate},
    \texttt{HypercubicDimension16CartanBasis}).
  \item \textbf{The Wilson coefficient and classical restoration rate are
    derived on that chart.} Only the pure-octic coordinate is populated, with
    coefficient $-a^{12}/20160$. The actual Cartan link observable converges
    to its quadratic $O(4)$-invariant density with the explicit uniform bound
    $(5/8)a^4M^4$
    (\texttt{HypercubicWilsonSymanzikRestoration}).
  \item \textbf{Boundary recombination retains factor one.} The $17$
    coordinates define a rank-$17$ degree-zero boundary-cochain quotient;
    shared-boundary currents cancel exactly. Under the three named analytic
    bounds, the resulting budget is $5544/5$ and the least closing depth is
    $15$ (\texttt{HypercubicDimension16BoundarySymanzik}).
  \item \textbf{The frontier is explicit.} The raw character theorem imposes
    none of the physical relation rows.  The derivative-label alpha quotient
    removes one purely syntactic redundancy, but field-label alpha equivalence
    and the antisymmetry, Bianchi, EOM, integration-by-parts,
    covariant-commutator, trace, and Cayley--Hamilton maps remain.  The
    quantitative restoration theorem is restricted to bounded constant
    Cartan curvature and is not a uniform interacting Symanzik theorem.
    Constructive Yang--Mills additionally requires a continuum measure, OS
    reconstruction, and a positive spectral gap.
\end{itemize}

\subsection*{The remaining inputs}

With the arithmetic and structural skeleton closed, the route now rests on the
following inputs --- listed with their exact status in v14, since these are
three different situations.

\begin{enumerate}
  \item \textbf{Derive the extraction/recombination constant on the actual map.}
    \emph{Status: not derived.} Appendix~F.5's displayed factors equal $33152$
    at $b=2$; Appendix~O's different factors with
    $C_{\mathrm{extract}}=2$ equal $11088/5$. The fluctuation big-$O$ constant,
    weighted cumulant-generation estimate, rooted tree-graph factor, and
    basis/dual-jet conditioning are not proved on the actual map. Regrouping
    connected families by union has norm one; the factor $14$ is the local
    rooted branching count, not a total-contact bound. The third round
    sharpened what a derivation must overcome: representative-wise truncation
    is refuted intrinsically, exact norm-below-two extractors exist on the
    corrected charts, and the transfer of any such extractor to the canonical
    $(F,D)$ space is refuted by the derivative-blindness and
    integration-by-parts/block obstructions. Our derivative-aware boundary
    complex and unpadded raw carrier now repair those two representational
    defects. The complete raw character census determines the invariant-space
    dimensions, and the Cartan octic restriction supplies exact duals and
    factor-one conditioning. Neither result imposes the full noncommutative
    relation quotient. \emph{What settles it:} construct equivariant linear
    maps for antisymmetry, Bianchi, EOM, integration by parts, trace, and
    Cayley--Hamilton on the actual unpadded invariant space; certify the rank
    and dual basis of their quotient without replacing the relations by a
    desired answer; and extend the classical constant-Cartan $O(a^4)$ estimate
    to uniform interacting Wilson observables. Then prove the weighted Wilson
    cumulant/tree estimate and Wilson-RG intertwining law on that same object.
    The resulting actual constant can then be checked against
    $C\,b^{\,3-\dmax}\leq1/3$.
  \item \textbf{Which support recurrence the glue satisfies.}
    \emph{Status: v14 asserts both branches of a now-proven dichotomy in
    different places.} \emph{What settles it:} one paragraph identifying the
    recurrence. If coarsen-then-thicken, the uniform bound is already a
    theorem; if thicken-only, the $O(J)$ growth breaks uniform tree decay and
    the step needs a new argument.
  \item \textbf{The two-marked correlation identity.}
    \emph{Status: missing.} The glue / back-propagation step requires a
    \emph{two}-marked transport identity of the shape
    $\langle A;\tau B\rangle_{\mu_0} = \langle QA;\tau' QB\rangle_{\mu_J}$;
    v14 states the one-marked pushforward duality, and the two-marked version
    does not follow from it (conditional expectations do not factor).
    \emph{What settles it:} state it precisely and prove it, or carry it as an
    explicit named assumption; once stated, its formalization is immediate.
  \item \textbf{KP convergence at the stopping scale and Wilson-measure
    reflection positivity.} \emph{Status: abstract results are classical; the
    route-specific instantiation is open.} One must construct the actual
    stopping-scale Wilson activities in the same norm, prove the KP criterion
    uniformly, and verify reflection and boundary-limit compatibility for the
    same Wilson family and RG kernels.
  \item \textbf{The real RG map satisfies the recursion.}
    \emph{Status: the central claimed content of v14's RG analysis; not
    independently verified here.} Everything above shows the surrounding
    machine is consistent and sharp; whether the actual Yang--Mills RG map, with
    its actual constants, satisfies the two-source recursion inside the
    $1/3$-threshold is the mathematical core of the route --- the one input
    that is neither bookkeeping, nor a clarification, nor classical.
\end{enumerate}

Items (1), (2), (3), and (5) contain route-specific mathematics. The classical
theorem statements in item (4) do not discharge their Wilson instantiation.
The actual RG recursion and constructive-QFT promotion remain open, and the
Yang--Mills mass gap remains open.

\paragraph{Lean modules.}
The results reported here are in
\texttt{Mettapedia.QuantumTheory.YangMills.RGBootstrap} (the contraction
predicate and knife-edge arithmetic),
\texttt{Mettapedia.QuantumTheory.YangMills.RGCrux} (the even lower-extraction
route obstruction),
\texttt{Mettapedia.QuantumTheory.YangMills.FiniteOSReconstruction},
\texttt{Mettapedia.QuantumTheory.YangMills.Z2StrongCouplingGap}, and
\texttt{Mettapedia.QuantumTheory.YangMills.Z3StrongCouplingGap} (the finite OS
reconstruction and strong-coupling gaps), and
\texttt{Mettapedia.QuantumTheory.YangMills.ProofState} (the continuum-open
gating); and, from the second round,
\texttt{RGBootstrapSlack} (two-source bootstrap and depth trichotomy),
\texttt{ExtractionMajorant} (displayed-sum audit and generic majorant model),
\texttt{WilsonBlockMajorant} (the concrete finite Wilson-polynomial realization),
\texttt{ExtendedExtractionTransfer} (the range-only obstruction and explicit
basis/dual-jet transfer theorem),
\texttt{Dimension16WilsonExtractionCertificate} (the F.4/O.9 relation-policy
mismatch, checked source transfer table, and obstructed as-written coordinate
certificate),
\texttt{WilsonPolymerRecombination} (norm-one union regrouping, the total-contact
counterexample, and the rooted interpretation of $14$),
\texttt{WilsonExtractionRecombinationConstant} (the two ledger calculations,
analytic-factor obstructions, and conditional depth arithmetic),
\texttt{SupportGrowth} (the recurrence dichotomy),
\texttt{TransferGapClustering} and \texttt{Z2TransferClustering}
(gap $\Leftrightarrow$ clustering and the discharged finite continuum gate),
\texttt{ToyRGMap} (the dynamical realization and depth-15 escape), and
\texttt{Q8StrongCouplingGap} / \texttt{Q8TransferClustering} (the non-abelian
instance); and, from the third round,
\texttt{SU2WilsonBlockPilot} (the exact $\mathrm{SU}(2)$ block, tree gauge,
co-tree coordinates, and fixed-boundary Haar reference integral),
\texttt{SU2CayleyHamiltonTruncationObstruction} (the intrinsic non-descent
witness), \texttt{SU2MajorantRepairDecision} (the sealed truncation-repair
decision), \texttt{SU2AssociatedGradedExtraction} /
\texttt{SU2AssociatedGradedExtractionDecision} (the graded jet basis, its
exact extraction constant, and the dimension separation from the schematic
count), \texttt{SU2IndependentTraceBasis} (the one-plaquette normal form and
its extraction constant), and \texttt{V14FDQuotientTransferNoGo} (the
derivative-blindness and integration-by-parts/block obstructions and the
uninhabited transfer sockets); and, from the fourth round,
\texttt{V14BoundaryCochainComplex}, \texttt{V14BoundaryCochainExtraction}, and
\texttt{V14BoundaryCochainBootstrap} (the derivative-aware boundary-cochain
scaffold and its conditional arithmetic), together with
\texttt{SU2LatticeFDCensusNoGo} (the exact hypercubic quartic witness and the
off-shell/on-shell Lorentz-census no-go); and, from the fifth round,
\texttt{V14HypercubicFDCensus} (the signed $H(4)$ action and finite raw
surface), \texttt{V14HypercubicQuarticCensusCertificate} and
\texttt{V14HypercubicQuarticBasis} (the complete unpadded Cartan quartic
census, duals, and identity conditioning),
\texttt{V14HypercubicQuarticWilsonBridge} (the exact Wilson coordinate vector
and nonzero $O(4)$-artifact quotient class), and
\texttt{V14HypercubicFDCensusPaddingNoGo} (the uninhabited faithful padded
dimension-$16$ exact census); and, from our unpadded dimension-$16$
construction, \texttt{HypercubicUnpaddedFDSyntax} (active dependent syntax),
\texttt{HypercubicDimension16CartanCensus},
\texttt{HypercubicDimension16CartanCertificate}, and
\texttt{HypercubicDimension16CartanBasis} (the $1287$-monomial Cartan octic
census, $17$ orbit coordinates, duals, and identity conditioning),
\texttt{HypercubicWilsonSymanzikRestoration} and
\texttt{HypercubicDimension16BoundarySymanzik} (the actual Wilson coordinate,
classical $O(a^4)$ restoration bound, boundary lift, factor-one extraction,
and conditional depth arithmetic), and
\texttt{HypercubicRawFDCharacterCensus},
\texttt{HypercubicRawFDCharacterCertificate}, and
\texttt{HypercubicRawFDDimension16Census} (the complete raw $H(4)$ character
certificate and exact active-carrier counts) --- all in the same namespace,
all axiom-guarded
to $\{\texttt{propext}, \texttt{Classical.choice}, \texttt{Quot.sound}\}$ with
no \texttt{sorry}. The manuscript analyzed here is Ben Goertzel's
\emph{Yang--Mills Mass Gap in 4D: RG Bootstrap, Polymer Expansion, OS
Reconstruction} (v14); constructions explicitly labeled ours are independent
formal repairs or tests, not claims about content already present in that
manuscript.

\end{document}
