\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{listings}
\geometry{margin=1in}

\lstdefinestyle{lean}{
  basicstyle=\ttfamily\small,
  breaklines=true,
  columns=fullflexible,
  keepspaces=true,
  showstringspaces=false,
  frame=single,
  framesep=4pt,
  xleftmargin=2pt,
  aboveskip=8pt,
  belowskip=8pt,
  literate=
    {⟨}{{$\langle$}}1
    {⟩}{{$\rangle$}}1
    {→}{{$\to$}}1
    {←}{{$\leftarrow$}}1
    {↔}{{$\leftrightarrow$}}1
    {¬}{{$\neg$}}1
    {∧}{{$\wedge$}}1
    {∨}{{$\vee$}}1
    {∀}{{$\forall$}}1
    {∃}{{$\exists$}}1
    {∈}{{$\in$}}1
    {∉}{{$\notin$}}1
    {⊆}{{$\subseteq$}}1
    {⊂}{{$\subset$}}1
    {⊕}{{$\oplus$}}1
    {⊥}{{$\perp$}}1
    {∘}{{$\circ$}}1
    {∪}{{$\cup$}}1
    {∩}{{$\cap$}}1
    {≤}{{$\leq$}}1
    {≥}{{$\geq$}}1
    {≠}{{$\neq$}}1
    {×}{{$\times$}}1
    {·}{{$\cdot$}}1
    {∅}{{$\emptyset$}}1
    {∂}{{$\partial$}}1
    {Γ}{{$\Gamma$}}1
    {Δ}{{$\Delta$}}1
    {Ω}{{$\Omega$}}1
    {σ}{{$\sigma$}}1
    {τ}{{$\tau$}}1
    {φ}{{$\varphi$}}1
    {ψ}{{$\psi$}}1
    {α}{{$\alpha$}}1
    {β}{{$\beta$}}1
    {₀}{{$_0$}}1
    {₁}{{$_1$}}1
    {₂}{{$_2$}}1
    {₃}{{$_3$}}1
    {₄}{{$_4$}}1
    {₅}{{$_5$}}1,
}
\lstset{style=lean}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}
\theoremstyle{definition}
\newtheorem{definition}{Definition}

\newcommand{\GG}{\mathbb{G}}
\newcommand{\FF}{\mathbb{F}_2}
\newcommand{\Wz}{W_0}
\newcommand{\Cl}{\mathrm{Cl}}
\newcommand{\KC}{\mathrm{KC}}
\newcommand{\LKR}{\mathrm{LKR}_{\mathrm{in}}}
\newcommand{\colorset}{\{r,b,p\}}

\title{A Machine-Checked Companion to Goertzel's\\
Spencer--Brown/Kauffman Route to the Four-Color Theorem:\\
\large Keystone, Pillars, and the Composition Ladder}
\author{The MeTTapedia formalization effort}
\date{July 2026}

\begin{document}
\maketitle
\sloppy

\begin{abstract}
This is a living formalization companion to Ben Goertzel's manuscript \emph{A
Human-Readable, Spencer--Brown/Kauffman-Style Proof of the Four-Color Theorem}
(v23), which organizes a candidate human-readable proof of the Four-Color Theorem
(4CT) around three interacting pillars: (A) an annular difference-\emph{spanning}
statement for a zero-boundary space $\Wz(H)$ (Theorem~4.9); (B) a CAP5-free
normal form with radius-1 collar locality; and (C) an \emph{executability} layer
that, refusing a false additivity of Kempe switches, reduces between-region Kempe
connectivity to a single \emph{Local Kempe Reachability with fixed input}
($\LKR$) property for one canonical three-cell collar gadget $\tau$ (Lemma~8.14),
composes it along the collar chain (Lemmas~8.15, 8.18, Cor.~8.19), and assembles
the wide annulus collar-by-collar (\S9.2). We record what the MeTTapedia
formalization has machine-checked of this route, with an honest ledger separating
what holds outright, what holds modulo one named remainder, and what is open, and
we foreground the places where the formalization \emph{refutes} a step rather than
discharging it.

Machine-checked outright (no \texttt{sorry}; axioms $\subseteq
\{\texttt{propext},\texttt{Classical.choice},\texttt{Quot.sound}\}$): finite
encoded-model audits of the keystone $\LKR$ property (Lemma~8.14) and two-color
\emph{transparency} (Lemma~8.15), together with completeness of the 192-state
incidence enumeration --- graph-level Kempe-step soundness remains open; a
proper-subspace strictness theorem against a larger unrestricted
boundary-zero chain space, with four uniform peel oracles refuted and
conditional need-based span infrastructure --- v23's actual cycle-space
inclusion (Theorem~4.9) remains open; and a length-2/3
radial-closing-edge fiber census for \S9.2 Step~3 --- the manuscript's
all-outer-stub, arbitrary-length statement remains open. The Gate-2 composition
(Lemmas~8.18/8.19) is \emph{reduced} --- the manuscript's own pointwise Step-1
preparation is refuted and replaced by a frontier-automaton / fibration
architecture --- to one live pin combining representative real-fiber
connectivity audits with DFA-mode sufficiency.

The formalization also produced a decisive negative in the encoded model.
\S9.2 Step~4 --- the manuscript's reinterpretation of collar Kempe words as
words of the ambient annulus --- fails in the encoded two-layer tau-chain
model: a certified, collar-input-avoiding switch whose ambient component
escapes the inner boundary, re-enters, and changes the collar restriction. Its
realization as a simple planar, cyclically-five-edge-connected actual collar is
a named open obligation, so this is a regression countermodel against the
composition \emph{seam} as written, not a graph-level refutation --- and not a
refutation of 4CT; its salvage (a normal-form confinement argument, or a
face-collar redesign) is open. We make no claim about the Four-Color Theorem
--- which is of course a theorem, via the Appel--Haken and
Robertson--Sanders--Seymour--Thomas computer-assisted proofs. The
human-readable v23 route remains \emph{open}, with its foundational layer
audited in an encoded model, and its most dangerous assembly seam pinned down
as broken in that model.

A third development round turned to the v24 working material (\emph{Deserts,
Pivots, and the Necklace}), which replaces v23's \S6--7. The v24 validation
toolchain and its numerical claims were reproduced independently: the $5412$
and $31704$ annular censuses with their Kempe fibers, the fullerene bases,
the pentagon seals, the desert and strand specimens --- including the
$688$-edge strand refuting the package's own Short Strand Conjecture --- and
the GWCO exact base through twelve. On the structural side the development
now carries a rotation-system Tait-coloring layer with exact facial linear
algebra; the all-face discrete Gauss--Bonnet identity
(\texttt{totalFaceCurvature\_eq\_twelve}); a proved \emph{weighted} pentagon
budget correcting the package's at-most-twelve pentagon count; the
locked-pentagon necklace assembly with singleton-strand forcing; a hexagonal
corridor theory (rung classification, clean width-four slabs, oriented
interfaces, Tait transfer, a sharp chirality barrier); congruence-correct
corridor and tube-ring pumping; and a framed-trail layer with
square/digon/rotor fiber calculi. The route's endgame --- fusion chains,
chiral monodromy, Trail Completability with its L1--L10 dependency package,
and a proved Short-Strand replacement --- remains open; the corridor and
pumping infrastructure is the active replacement search.
\end{abstract}

\tableofcontents

\section{The problem and Ben Goertzel's three-pillar route}
\label{sec:problem}

\subsection{Tait's reduction and the minimal-counterexample target}

The Four-Color Theorem asserts that every plane triangulation $G$ admits a
proper vertex 4-coloring. Passing to the cubic dual $K=G^{*}$, Tait's classical
equivalence (v23, Thm.~2.3) restates 4CT as: every bridgeless planar cubic
graph admits a \emph{proper 3-edge-coloring}, i.e.\ a map
$\chi:E(K)\to\colorset$ assigning distinct colors to the three edges at each
vertex. The manuscript encodes the three colors as the three nonzero elements
of $\GG=\FF^{2}$, with $r=(1,0)$, $b=(0,1)$, $p=(1,1)$, so that ``properness at
a vertex'' is exactly $\chi(e_1)+\chi(e_2)+\chi(e_3)=r+b+p=0$ in $\GG$, and
``integrating'' an edge-coloring across the planar dual becomes a path-sum in
$\FF^{2}$.

Following Spencer--Brown and Kauffman, the manuscript reformulates colorings as
plane \emph{formations} (red/blue Jordan curves with purple overlaps), defines
Kempe switches as the standard two-color interchange, and proves the
\emph{Parity Lemma} (planar invariance of the mod-2 count of two-color
circuits). The role of \S3 is to reduce 4CT, via Kauffman's parity/primality
argument (Theorem~3.1), to the nonexistence of a minimal counterexample
containing a \emph{between-region annulus} $H$ whose boundary-compatible
colorings are \emph{not} connected by Kempe moves supported inside the annulus.
Thus the entire analytic burden is shifted to a \emph{between-region Kempe
connectivity} statement for an annulus $H\subseteq K$ with outer and inner
boundary cycles $\Gamma_\infty,\Gamma_0$.

\subsection{The three pillars}

The manuscript's conceptual overview (v23, \S1.1) states the argument as three
interacting pillars.

\paragraph{Pillar~A: annular difference spanning (the linear ``accounting''
layer).} Working in a between-region annulus $H$, one encodes boundary
colorings and their differences as vectors in an $\FF$-space. Let $W(H)$ be the
coordinatewise cycle space of $\GG$-chains on $E(H)$ satisfying the Kirchhoff/\allowbreak
even-degree constraints at interior vertices, and let
\[
  \Wz(H) \;:=\; \{\,x\in W(H) : x(e)=0 \text{ for all boundary edges } e\in
  B_1\cup B_2\,\}
\]
be the \emph{zero-boundary} subspace. For a fixed proper coloring $C_0$ of $H$
with Kempe closure $\Cl(C_0)$, the manuscript defines a family $\KC(C_0)$ of
\emph{Kempe-closure (polarized face) generators} $X_f^{ab}(C)$ supported in
depth-1 collars (v23, Def.~4.8), and proves:
\begin{theorem}[Spanning theorem for $\Wz(H)$, v23 Theorem~4.9]
\label{thm:49}
Let $H$ be an annular subgraph of a bridgeless planar cubic graph, with
boundary cycles $\Gamma_0,\Gamma_\infty$. Fix any proper 3-edge-coloring $C_0$
of $H$ and let $\mathcal{G}:=\KC(C_0)$. Then
$\Wz(H)\subseteq\mathrm{span}_{\FF}(\mathcal{G})$; equivalently, if
$z\in\Wz(H)$ satisfies $z\cdot g=0$ for every $g\in\mathcal{G}$, then $z=0$.
\end{theorem}
The manuscript proves Theorem~\ref{thm:49} in strong-dual annihilator form: it
shows $U^{\perp}\cap\Wz(H)=\{0\}$ for $U=\mathrm{span}_{\FF}(\mathcal{G})$, by a
planar orthogonality peeling along a dual spanning forest, after a
``purification'' step (Lemma~4.4) that removes the polarization of the face
generators.

\paragraph{Pillar~B: CAP5-free geometry and radius-1 locality (the geometric
locality layer).} Assuming a minimal counterexample, the manuscript eliminates
the CAP5 separating obstruction and works in a CAP5-free normal form
(Corollary~6.9). A tube-forcing argument then reduces every ``escape'' of an
anchored Kempe chain to a finite three-cell gate enumeration, yielding radius-1
confinement of anchored Kempe cycles together with a cap-aware
disjointness/commutativity package (Lemmas~7.8, 7.9, 7.10). This is what
licenses peeling the wide annulus into radius-1 collars.

\paragraph{Pillar~C: executability without false additivity (the
algebra-to-geometry bridge).} The decomposition $\Delta=\sum v_{f,g}$ provided
by Pillar~A is a statement in $\Wz(H)$; it does \emph{not} by itself imply that
one may \emph{execute} the corresponding mixed color-pair Kempe switches as if
they formed an abelian sum. The manuscript is explicit that cross-pair
interference is real: an $(a,b)$-switch can destroy the $(b,c)$-structure a
later switch needs (v23, \S8.1), and Kempe switches using different color pairs
on shared support need not commute (v23, \S8.3). To execute the decomposition
honestly, the manuscript moves to an operator model: proper colorings form an
orthonormal basis of a Penrose--Kauffman state space, and each Kempe switch is
an involutive linear operator (generally noncommuting with switches of other
color pairs). Using radius-1 locality, between-region Kempe connectivity is
reduced to a single local property:
\begin{definition}[Local Kempe reachability with fixed input, v23 Def.~8.12]
\label{def:lkr}
Let $X$ be a planar cubic tangle with ordered input stubs $S_{\mathrm{in}}$ and
output stubs $S_{\mathrm{out}}$, and fix an input coloring $c$. Let
$\Omega_X(c)$ be the set of proper 3-edge-colorings of $X$ extending $c$ on the
input stubs. The \emph{Kempe graph} $\mathsf{K}_X(c)$ has vertex set
$\Omega_X(c)$, with an edge whenever two colorings differ by a single Kempe
switch supported on a two-color component touching no input-stub edge. We say
$X$ satisfies $\LKR$ if $\mathsf{K}_X(c)$ is connected for every $c$ for which
$\Omega_X(c)\neq\emptyset$.
\end{definition}

The chain of Pillar~C is then:
\begin{itemize}
  \item \textbf{Lemma~8.14}: the canonical three-cell collar gadget $\tau$
        satisfies $\LKR$ (and so does its mirror);
  \item \textbf{Lemma~8.15}: two-color \emph{transparency} of $\tau$ --- every
        two-color component is a boundary-to-boundary path with no internal
        cycle;
  \item \textbf{Lemma~8.18 / Corollary~8.19}: $\LKR$ \emph{composes} across a
        transparent interface, so an entire cut-open radius-1 collar tangle
        $\widehat{A}=G_m\circ\cdots\circ G_1$ satisfies $\LKR$;
  \item \textbf{\S9.2 assembly}: peel the wide annulus $H$ into nested radius-1
        collars and use the collar $\LKR$ property to rewrite the current
        coloring to the target collar-by-collar from outside to inside, the
        cap-aware locality lemma (7.9) ensuring no switched component reaches
        back to change a fixed boundary.
\end{itemize}

\subsection{Why Lemma~8.14 is the keystone}

The manuscript states that its proof is human-readable and ``the only finite
verification required is a small by-hand audit of a single three-cell gadget''
(v23, Abstract and \S1). In the three-pillar architecture, every other step is
either an explicit local lemma or a structural reduction; the one place where a
finite, exhaustive check is genuinely unavoidable is the $\LKR$ property of the
canonical gadget $\tau$. Formalizing Lemma~8.14 therefore certifies exactly the
finite core that the manuscript isolates as load-bearing. The remainder of this
companion describes that formalization (\S\ref{sec:lkr}), the resolution of the
Pillar~A spanning question into a need-based repair (\S\ref{sec:pillarA}), the
Pillar~C composition ladder --- what is proved, what is reduced to one pin, and
where a decisive counterexample was found (\S\ref{sec:pillarC}) --- and a precise
status ledger (\S\ref{sec:status}). Superseded routes are recorded in
appendices.

\section{The Pillar-C keystone, machine-checked: Lemma~8.14 and transparency 8.15}
\label{sec:lkr}

We restate the manuscript's keystone in its own notation and then describe the
Lean encoding.

\begin{lemma}[$\LKR$ for the canonical three-cell gadget, v23 Lemma~8.14]
\label{lem:814}
Let $\tau$ be the canonical three-cell collar gadget. It is a planar cubic
tangle with internal vertices $F_0,\dots,F_5$ and boundary stubs
$B_0,\dots,B_7$, whose internal edges form the tree
\[
  F_1 - F_0 - F_2 - F_4 - F_5, \qquad \text{with a leaf } F_3 \text{ attached to } F_2,
\]
and whose boundary stubs are attached by
$F_0B_0,\,F_1B_1,\,F_1B_2,\,F_3B_3,\,F_3B_4,\,F_5B_5,\,F_5B_6,\,F_4B_7$. Take
input stubs $\{B_0,B_1,B_2,B_3\}$ and output stubs $\{B_4,B_5,B_6,B_7\}$. Then
$\tau$ satisfies $\LKR$. The same holds for the mirror gadget.
\end{lemma}

The manuscript proves Lemma~\ref{lem:814} by cutting $\tau$ along the internal
interface edge $I=F_2F_4$ into $\tau=\sigma_{\mathrm{R}}\circ\sigma_{\mathrm{L}}$
and doing a small case analysis on the two pieces. Our formalization instead
audits the \emph{full} gadget directly, by exhibiting the proper-coloring state
space and an explicit Kempe-path certificate connecting every fixed-input
fiber; this is a strictly more direct realization of the same $\LKR$ claim, and
it does not rely on the $\sigma_{\mathrm{L}},\sigma_{\mathrm{R}}$ split or on
the composition Lemma~8.18.

\subsection{The canonical gadget and its 192-state coloring space}

The Lean module fixes the colors and the gadget incidence exactly as in
Lemma~\ref{lem:814}: the three nonzero colors are an inductive type, and the
gadget's edges (five internal edges plus the eight boundary stubs) and internal
vertices are inductive types with an explicit incidence map.

\begin{lstlisting}[language={}]
inductive LColor | r | b | p
  deriving DecidableEq, BEq, Repr, Inhabited

inductive TauEdge
  | F1F0 | F0F2 | F2F3 | F2F4 | F4F5
  | B0 | B1 | B2 | B3 | B4 | B5 | B6 | B7
  deriving DecidableEq, BEq, Repr, Inhabited

def tauInputEdges : List TauEdge := [TauEdge.B0, TauEdge.B1, TauEdge.B2, TauEdge.B3]
\end{lstlisting}

A proper 3-edge-coloring of $\tau$ is represented by the finite choices left
after properness is imposed at every cubic vertex: an ordered color triple at
the central vertex $F_2$, one binary choice for the forced edge $F_1F_0$, and one
ordered-pair (swap) bit at each remaining boundary fork --- $6\times2^{5}=192$
states. That this enumeration is exactly the proper-coloring state space is a
checked fact ($192$ entries, no duplicates, proper at every vertex).

\subsection{The Kempe audit and the machine-checked theorems}

A Kempe step switches a two-color component \emph{disjoint from the input stubs}
(Definition~\ref{def:lkr}). The $\LKR$ property is witnessed by an explicit
indexed-path certificate: for each of the 192 states it records the
representative of that state's fixed-input fiber and a path of at most two
input-disjoint Kempe switches reaching it, plus a coherence audit that any two
states with the same input edges share a representative (so fibers are well
defined). The three finite audits each reduce to \texttt{true} by the kernel's
decision procedure; the only axiom dependency is \texttt{propext}.

\begin{lstlisting}[language={}]
theorem tauStateSpaceAudit_ok : tauStateSpaceAudit = true := by decide
theorem lemma814PathCertificate_rows_ok :
    validIndexedRowsFrom 0 lemma814PathCertificate = true := by decide
theorem representativeCoherenceAudit_ok : representativeCoherenceAudit = true := by decide

/-- Lemma 8.14, closed by the finite state-space and indexed path certificate. -/
theorem lemma814_tau_lkrIn_audit : lemma814_tau_lkrIn_finiteCheck = true := by
  simp [lemma814_tau_lkrIn_finiteCheck, tauStateSpaceAudit_ok, tauLKRInAudit,
    lemma814PathCertificateAudit_ok]
\end{lstlisting}

The mirror clause holds definitionally (reflection changes only the planar order
of an isomorphic incidence tree). The incidence enumeration is complete for the
encoded tau graph: every proper incidence coloring is one of the 192 enumerated
colorings. The finite certificate audit is proved, but graph-level soundness of
every encoded step remains the named obligation
\texttt{Lemma814EncodedMovesAreGraphKempeSwitchesTarget}. Thus the current
Lemma~8.14 result is a finite encoded-model audit, not yet the manuscript graph
theorem.

\begin{remark}[Transparency~8.15, finite encoded-model audit]
\label{rem:815}
The same module formalizes Lemma~8.15 (two-color transparency): for each of the
192 colorings, every nonempty two-color component is a boundary-to-boundary tree
path (\texttt{transparentComponent}), aggregated as
\texttt{tauTreeTransparencyAudit}. That audit is now \emph{proved} ---
\texttt{lemma815\_tau\_tree\_transparency\_audit} reduces to \texttt{true} by a
range decomposition of the finite check, axiom-clean. The encoded transparency audit is proved. Its use as graph-level composition
(\S\ref{sec:pillarC}) shares Lemma~8.14's named graph-fidelity obligation, so
the local graph-theoretic core is not yet sealed.
\end{remark}

\section{Pillar~A: a proper-subspace obstruction, and its need-based repair}
\label{sec:pillarA}

Pillar~A (the spanning Theorem~\ref{thm:49}) is where the formalization first
found --- and then routed around --- a real gap. We give both halves, because
together they are a clean example of what a companion of this kind is for.

\subsection{The obstruction: the spanning \emph{equality} over-reaches}

On every \emph{closed-walk exact shell} --- a concrete annular configuration
carrying the boundary-source and interior-endpoint witness data that
Theorem~\ref{thm:49} is meant to cover --- the boundary-zero target that the
Kempe-closure detector actually pins down is a \emph{strict} subspace of the full
boundary-zero chain space.

\begin{lstlisting}[language={}]
/-- On every closed-walk exact shell, the Theorem-4.9 boundary-zero target is a
proper subspace of the full selected-boundary-zero chain space. -/
theorem theorem49BoundaryZeroKirchhoffSubspace_lt_planarBoundaryZeroSubmodule_of_closedWalkExactShell
    [Fintype G.edgeSet] {emb : PlaneEmbeddingWithBoundary G}
    (shell : ClosedWalkExactShell emb) :
    theorem49BoundaryZeroKirchhoffSubspace emb
        (selectedBoundaryInteriorEdgeEndpointVertices emb) <
      planarBoundaryZeroSubmodule emb
\end{lstlisting}

The strict inequality \texttt{<} is the load-bearing content: a proved
\emph{proper}-subspace inclusion, not a heuristic. The structural reason (every
closed-walk shell forces two distinct interior-support edges onto one face
boundary) refutes the natural one-collar repairs, and a companion audit shows the
four proposed \emph{uniform geometric oracles} that would each close
Theorem~\ref{thm:49}'s synthesis are all false:
\begin{lstlisting}[language={}]
theorem not_interiorDualPeelOracle         : ¬ InteriorDualPeelOracle
theorem not_wellFoundedPeelOracle          : ¬ WellFoundedPeelOracle
theorem not_previousBoundaryGeometryOracle : ¬ PreviousBoundaryGeometryOracle
theorem not_residualBoundaryGeometryOracle : ¬ ResidualBoundaryGeometryOracle
\end{lstlisting}
Lean proves that the formal detector is strictly smaller than a larger
unrestricted selected-boundary-zero chain space. This does not refute v23's
actual cycle-space/Kirchhoff-constrained claim
$\Wz(H)\subseteq\mathrm{span}_{\FF}(\mathcal{G})$. That inclusion is now named
\texttt{V23Theorem49W0ContainedInKempeClosureGeneratorSpanTarget} and remains
open; the four uniform oracle routes that would have closed it uniformly are
refuted.

\subsection{The repair: the route never needs the full space}

The resolution is that the synthesis does not \emph{use} the full boundary-zero
space; it uses only the discrepancy classes of boundary-compatible coloring
pairs, and those lie in the detector subspace the manuscript's own peeling
witnesses span. Formally, the requirement actually consumed downstream is
\emph{need-based}: it suffices that (1) the detector subspace is contained in the
projected Kempe-closure generator span, (2) each execution step preserves that
subspace, and (3) every route-used discrepancy class lies in it. All three are
machine-checked in the route's natural cubic setting (module
\texttt{PillarASmallerSpace}):
\begin{lstlisting}[language={}]
-- (3) discrepancy classes lie in the detector subspace (cubic setting):
theorem routeUsedDiscrepancyClassesLieInDetectorSubspace_of_hasCubicIncidentEdgeTriples ...
-- (2) a Kempe-switch execution step preserves detector membership:
theorem routeKempeSwitchExecutionStep_preserves_detectorSubspace ...
-- assembled sufficiency (inclusion form), discharging the requirement:
theorem needBasedPillarARequirement_of_detector_le_span_of_stepPreserves_of_routeDiscrepancies ...
\end{lstlisting}
Proposition~(3) has a two-idea proof one can state aloud: a Tait coloring is a
Klein-four flow at each cubic vertex, so two colorings agreeing on the selected
boundary differ by a \emph{boundary-zero flow}, which is exactly what the
Kirchhoff detector certifies. The manuscript's Theorem~4.9 states an \emph{inclusion}, not an equality. The
existing need-based theorems are conditional on detector containment, step
preservation, discrepancy membership, and embedding-specific peel data. They
are conditional algebraic-span infrastructure, not a proof of Theorem~4.9. What remains a genuine per-embedding obligation is
the \emph{supply} of a peeling witness for the synthesis's actual embedding
class; that is a composition-stage task, not a spanning gap.

\section{Pillar~C: the composition ladder}
\label{sec:pillarC}

Between the local keystone (\S\ref{sec:lkr}) and 4CT, v23's own argument climbs a
ladder: single-gadget $\LKR$ $\to$ transparent composition to a whole collar
chain (Gate-2) $\to$ closed re-glued collars (\S9.2 Step~3) $\to$ execution in the
ambient annulus (\S9.2 Step~4) $\to$ the wide-annulus peel. This companion has
now walked a substantial part of that ladder, with one step proved-modulo-a-pin
and one step \emph{refuted}.

\subsection{Gate-2: transparent composition, reduced to one pin}

Corollary~8.19 lifts $\LKR$ from the single gadget to a whole cut-open radius-1
collar chain across a transparent interface. The manuscript's own Step-1 proof of
Lemma~8.18 (a pointwise preparation via Lemma~8.16) does \emph{not} go through ---
the formalization refutes it directly:
\begin{lstlisting}[language={}]
theorem lemma818_pointwise_lift_preparation_obstruction : ...   -- axiom-clean
\end{lstlisting}
In its place the development builds a frontier-automaton / fibration architecture:
a finite frontier state over the chain transcript, generated parent-row
certificates, and a fibered-connectivity decomposition (base connected + fibers
connected + lifts). The executable chain test \texttt{chainLKRInAudit} passes on
all words up to length seven (real-fiber labs, all input fibers connected, zero
failures). The former metadata-only classification audit has been replaced: the
actual per-target test is
\texttt{representativeTargetFiberKempeOrbitConnectivityAudit}, and Gate-2's
single live pin is
\begin{lstlisting}[language={}]
Gate2RepresentativeFiberKempeOrbitConnectivityPin
\end{lstlisting}
combining fourteen representative real-fiber audits with DFA-mode sufficiency;
the all-chain implication is proved conditional on this pin. (A separate refuted route,
\texttt{not\_concreteChainFiberAppendPrefixFibrationClosed}, records a shortcut
that provably fails and is kept dead.)

\subsection{S2: length-2/3 radial-closing-edge fiber census}

Gate-2 certifies $\LKR$ with the \emph{first} gadget's input stubs fixed;
\S9.2 Step~3 needs the \emph{cyclically re-glued} collar with all outer-side stubs
fixed --- different fibers, no bridging lemma in the manuscript. What is proved
is a finite census: it ranges over twelve tau/mirror words of length 2 or 3 and
fixes the four radial-closing edges (a lab found all 972 such fibers
connected-or-empty --- 216 nonempty, 756 empty, zero disconnected --- and the
census target was discharged with zero pins). It does \emph{not} fix every
outer stub and does not range over arbitrary collar length. The actual
manuscript claim is named
\texttt{ManuscriptSection92S2AllOuterStubsFixedArbitraryCollarTarget} and
remains open.
\begin{lstlisting}[language={}]
def closedCollarLength23RadialClosingEdgeFiberCensus : Prop := ...   -- proved
def ManuscriptSection92S2AllOuterStubsFixedArbitraryCollarTarget : Prop  -- open
\end{lstlisting}
The route survey had rated S2 the sharpest mismatch in the manuscript --- a
statement never written down in v23 and not implied by Gate-2 --- so proving it on
the finite class is a real advance.

\subsection{S4: abstract-chain ambient-escape regression}

\S9.2 Step~4 reinterprets a collar Kempe word as a word of the \emph{ambient}
annulus, and confines the switched components with a face-only locality lemma
(7.9). The formalization proves an ambient-escape regression in the encoded
tau-chain model --- a collar plus one deeper radial ring sharing the interface.
No theorem currently realizes that witness as a simple planar,
cyclically-five-edge-connected actual collar; graph-facing salvage is
conditional on
\texttt{ClosedWalkActualCollarRotationFaceIncidenceCutLiftObligation}, which
remains open.
\begin{lstlisting}[language={}]
/-- A collar-certified, collar-input-avoiding Kempe switch whose ambient
two-layer component leaves through the inner side, hits the fixed outer input,
and does NOT restrict to the certified collar move. -/
theorem section92Step4TwoLayerCounterexampleClass :
    Section92Step4TwoLayerCounterexampleClass         -- axioms [propext]
\end{lstlisting}
Concretely (outer word $\tau\tau$, inner word $\tau$, input key $r,r,b,r$): a
switch that is input-avoiding \emph{in the collar alone} balloons, in the
two-layer object, into a component that crosses the shared inner boundary into the
deeper ring, returns, meets the fixed outer input edge, and lands the collar on a
\emph{different} coloring than the certified move. This refutes the reinterpretation
as a regime-free, purely-local principle: the ambient switch is a \emph{different}
move on the collar than the one Gate-2/S2 certified.

We are precise about what this does and does not say. It is a defect in the
manuscript's assembly \emph{seam} as argued (Step~4 invokes 7.9, a lemma proved
for single-face collars, as if it were a global confinement), not a refutation of
4CT.

The cheapest repair has also been tested, and \emph{refuted}. Strengthening the
certification so that switches avoid the entire outer interface --- both input
\emph{and} output stubs, not only the inputs --- does eliminate the escape (a
two-layer companion run finds zero escapes under full-interface avoidance), but at
a fatal cost: on the same finite class, two colorings with the same fixed input
are connected \emph{only} by a switch whose component touches the output stubs, so
forbidding output touches disconnects the fibers (module
\texttt{GoertzelLemma818TwoSidedAvoidance}: $432$ open and $216$ closed nonempty
fibers disconnect). The escape channel is therefore \emph{load-bearing for
connectivity}: the very moves that let a component escape the collar are the moves
the fibers need to remain connected. Confinement and connectivity are in direct
tension, so any repair must confine the escaping components \emph{without}
severing collar connectivity --- a needle the simplest fix cannot thread.

What remains is a genuinely regime-level salvage: a proof that the
minimal-counterexample \emph{regime} (CAP5-free normal form) excludes the
disconnecting/escaping configurations, or a \S9 redesign that only ever peels
\emph{face} collars where 7.9 applies as stated. Neither is established; both need
planar-normal-form infrastructure the development does not yet have; and the
abstract gadget lab cannot decide them, since the tension may or may not dissolve
in the actual normal form. As of this writing the seam is open, with both the
escape and the failure of the cheapest repair pinned down as checked theorems.

\subsection{Sharpening the open salvage: a winding invariant and a cyclic 2-cut reduction}

Since the escape was pinned down, the formalization has \emph{sharpened} --- though
not closed --- the open salvage, by asking a Spencer--Brown/Kauffman-native
question: which two-color components can escape? On the closed annular collar a
two-color component carries a well-defined mod-2 \emph{winding class} around the
annulus generator --- the parity of its crossing count with a fixed radial cut ---
a Parity-Lemma-style invariant, well defined per component and tracked across Kempe
switches. In this language the escape is exactly a \emph{winding} move: the
components that leave through the inner side and return are those of nonzero winding
class. The precise form of the S4 freedom is then a homological statement,
machine-checked on the witness class: \emph{winding is not boundary-determined} --- a
fixed-boundary fiber can carry components of different total winding class, so the
escaping (winding-1) moves are not forced by the boundary data alone.

This localizes the difficulty to one geometric question: can a winding-freedom
escape be \emph{realized on a genuinely simple planar collar}? The formalization
reduces it to a classical connectivity fact. Any simple planar realization that
preserves the winding profile must replace the escape's parallel endpoint bundle by
a simple two-pole side; a tree-rank (handshaking) count ---
$2\,|\text{side edges}| = 3\,|\text{internal}| + 4$ forces
$|\text{internal}|+1 < |\text{side edges}|$, hence a cycle --- turns that side into
a \emph{cyclic 2-cut} of the collar. A collar admitting no realized cyclic 2-cut
therefore admits no escape realization:
\begin{lstlisting}[language={}]
-- every simple planar winding-escape realization forces a cyclic two-cut:
theorem ...Escape_forces_cyclicTwoCut_allSizes : ...
-- so a collar forbidding cyclic two-cuts (e.g. cyclically 5-edge-connected)
-- admits no escape realization:
theorem ...Escape_not_simplyRealizable_allSizes
    (h : ...ForbidsCyclicTwoCut G) : ¬ ...SimplePlanarEscapeRealization G
\end{lstlisting}

We are precise about what this buys. It is a \emph{reduction of the open salvage to
one named residual}, not a repair: the theorem is conditional on the collar
forbidding cyclic 2-cuts, and the current realization datum carries the
separating-pair structure as an obligation rather than deriving it from the collar's
embedding. What it does is convert the vague ``the minimal-counterexample regime
should exclude the escape'' into a concrete checkable target --- \emph{the escape
collar carries no cyclic 2-cut}, i.e.\ it is cyclically sufficiently edge-connected,
which is exactly the kind of property the minimal-counterexample normal form is
expected to supply. And this residual is not an un-formalizable abstraction: the
development already proves cyclic-five-edge-connectivity for concrete graphs (and
refutes it for others), so discharging or refuting it \emph{for the escape collar}
is a reachable next question --- the honest current frontier of the S4 salvage.

\section{The v24 route: deserts, pivots, and the necklace}
\label{sec:v24}

Goertzel's v24 working package (July 2026) replaces v23's \S6--7 with a new
architecture: pentagonal \emph{pivots}, hexagonal \emph{deserts}, a
\emph{necklace} decomposition of the sphere relative to the twelve pentagons,
winding and monodromy invariants along corridors, and a final \emph{Trail
Completability} target from which the minimal-counterexample contradiction is
to follow, conditional on a dependency chain L1--L10. The package proposes a
universal Short Strand Conjecture and then refutes it itself with a
$688$-edge, reach-$40$ strand, so the route requires a replacement bound.
This section records what the formalization has established of this route so
far; the formalization targets combinatorial rotation systems throughout, not
topological planarity.

\paragraph{Independent reproduction of the validation toolchain.} Every
numerical claim consumed from the package was recomputed independently before
use: the annular censuses ($5412$ and $31704$) with their Kempe fibers, the
fullerene finite bases, the pentagon finite seals, tube seed growth, the
desert and strand specimens (including the Short-Strand refuter), Goldberg
normal-form specimens, and the GWCO exact base through twelve. A recurrent
tube-ring transfer theorem replaces the package's Pascal-triangle
extrapolation (\texttt{GoertzelV24TubeRingTransfer}).

\paragraph{Rotation systems and facial linear algebra.} A Tait-coloring
layer is built over rotation systems, with each edge's two faces identified,
face simplicity reduced to two-sidedness, facial dual connectedness, and the
exact facial linear algebra: facial boundary rank, primal cycle-space rank,
the equality of the facial span with the cycle space, and the face winding
classification (\texttt{GoertzelV24FaceBoundaryLinearAlgebra},
\texttt{GoertzelV24OrbitFaceCycleSpaceEquality},
\texttt{GoertzelV24WindingClassification}).

\paragraph{Curvature.} The all-face discrete Gauss--Bonnet identity is
proved from rotation-system data alone: the total face curvature
$\sum_f\,(6-\ell(f))$ equals $12$ (\texttt{totalFaceCurvature\_eq\_twelve} in
\texttt{GoertzelV24CurvatureScope}). The package's \emph{at-most-twelve
pentagon} step, which is false as stated under minimum face size five, is
corrected by a proved \emph{weighted} pentagon budget charging faces by
$6-\ell(f)$; the fullerene hexagonal bulk is derived on orbit faces, and
curvature-to-bulk corridor bounds connect the budget to corridor extraction
(\texttt{GoertzelV24OrbitFaceCurvatureBulk}, \texttt{GoertzelV24BulkCorridor}).

\paragraph{Necklace and corridors.} The locked-pentagon necklace is
assembled and the singleton necklace strand forced
(\texttt{GoertzelV24Necklace}). A hexagonal corridor theory is developed:
defect-free corridor neighborhoods extracted from geodesic face paths; an
internal rung classification with induced rung chains and the exclusion of
adjacent induced rungs; clean width-four slabs with oriented interfaces and
the matching of consecutive interfaces; Tait transfer across slabs with
finite color-transition alphabets and color-state words; and a sharp
chirality barrier under which transfer across a chiral reversal forces the
melted state (\texttt{GoertzelV24CleanHexCorridor},
\texttt{GoertzelV24HexFaceRungType}, \texttt{GoertzelV24OrientedHexSlab},
\texttt{GoertzelV24HexCorridorColorTransfer},
\texttt{GoertzelV24HexCorridorChiralityBarrier}).

\paragraph{Pumping.} The corridor acceptance language is proved periodic and
corridor pumping congruence-correct; with the recurrent tube-ring transfer
these are the working tools of the Short-Strand replacement search
(\texttt{GoertzelV24CorridorPumping}).

\paragraph{Framed trails and local fiber calculi.} The framed-trail layer
proves completion semantics and defect freedom --- the unique admissible
missing color and the characterization of proper trail extensions
(\texttt{missingColorAt\_is\_unique\_admissible},
\texttt{hasMatchingDefectColors\_iff\_exists\_properTrailExtensionColor} in
\texttt{GoertzelV24FramedTrail}) --- supported by exact local calculi: the
square fiber table with its realized Kempe switch and local and
compositional profile identities, the digon Kempe rung, rotor local color
routes, and the two-edge-cut color parity (\texttt{GoertzelV24Square}\,%
/\texttt{SquareKempe}/\texttt{SquareComposition}, \texttt{GoertzelV24Digon},
\texttt{GoertzelV24Rotor}, \texttt{GoertzelV24TwoEdgeCut}).

\paragraph{The minimality normal form (proved).} The full minimality
connectivity ladder is now machine-checked on rotation systems, with no
\texttt{sorry} and axioms in
$\{\texttt{propext},\texttt{Classical.choice},\texttt{Quot.sound}\}$. The
two-edge, cyclic three-edge, and cyclic four-edge cut reductions are each
proved by capping both sides into strictly smaller cubic rotation systems and
gluing their Tait colorings across the cut; a vertex-minimal Tait
counterexample admits none of them, so it is cyclically five-edge-connected
(\texttt{cyclicallyFiveEdgeConnected\_of\_vertexMinimalTaitCounterexample}).
The four-edge rung is the classically hard one: at a four-edge cut the four
boundary colors sum to zero in the Klein four-group, giving three boundary
classes (all-equal and the two non-crossing adjacent pairings), and the two
capped sides always share a reducible class. The load-bearing step --- that a
side admitting an all-equal boundary escapes, by a Kempe swap, into a
non-crossing adjacent class (never the crossing Birkhoff pairing) --- is
\emph{proved}, not assumed, from the planarity of the interior Kempe chains
(\texttt{GoertzelV24FourEdgeCutKempeEscape}), and a minimal counterexample is
correspondingly forced to have minimum face size five. The corridor-existence
side is lifted off the fullerene premise entirely: on any spherical cubic map
of minimum face size five, the pentagon count equals $12$ plus the total
negative curvature weight, and either the face count lies below a
weight-dependent threshold or a clean hexagonal corridor exists
(\texttt{GoertzelV24WeightedOrbitFaceCorridor}) --- no restriction to
pentagonal and hexagonal faces is used anywhere.

\paragraph{In progress and open.} On this normal form the endgame reduction is
under active construction: a fusion-chain / rebase-pumping dynamics that, from
any adjacent pair of the counterexample, produces either a fusion terminal or
a strictly descending rebase pumping
(\texttt{exists\_rotationOrderedFusionTerminalOrRebasePumping\_of\_}%
\texttt{vertexMinimalTaitCounterexample}), together with an exhaustive scope
classification of the remote facial-dual cycles it generates (length $\geq5$
exact cut, length-three single-vertex cut, length-four adjacent-pair cut with
an internal dual chord). What remains \emph{open} is the coloring transport
that turns each classified case into a contradiction with minimality --- the
large-cut splice/interface law and the explicit consumption of the
singleton-star and adjacent-pair-collar cases --- and hence Trail
Completability, the L1--L10 chain, and a proved Short-Strand replacement. The
v23-era collar obligations are taken up only where this route consumes them.
Nothing in this section claims the Four-Color Theorem or the completion of the
v24 route.

\section{Status and scope: machine-checked, reduced, and open}
\label{sec:status}

We state the scope exactly. The full route is a ladder $S0,\dots,S9$ (Gate-2, then
v23 \S9 and \S3); the table records each step's manuscript reference and current
Lean status.

\begin{center}\small
\begin{tabular}{@{}llll@{}}
\toprule
Step & Content & v23 ref & Lean status \\
\midrule
--- & single-gadget $\LKR$                & Lem.~8.14        & finite encoded-model audit; graph move-soundness open \\
--- & two-color transparency              & Lem.~8.15        & finite encoded-model audit; shares graph-fidelity boundary \\
--- & Pillar~A                            & Thm.~4.9         & actual $\Wz$ inclusion open; unrestricted-oracle strictness proved \\
S0  & Gate-2 chain $\LKR$                  & Lem.~8.18/8.19   & one actual fiber/orbit plus mode-sufficiency pin \\
S2  & radial-closing-edge fiber census     & \S9.2 Step~3     & proved only at length 2/3; manuscript target open \\
S4  & ambient escape regression            & \S9.2 Step~4     & abstract-chain countermodel; graph realization open \\
S1  & collar $\Rightarrow\tau$/mirror chain & Lem.~8.5--8.6   & open (structural) \\
S3  & annulus peeling well-definedness     & \S9.2 Step~2     & open (structural) \\
S5  & interface to Kauffman Thm.~3.1       & \S9.2 / \S3      & open (statement-level) \\
S6  & Kauffman parity/primality internals  & \S3.2--3.3       & open (structural) \\
S7  & minimal-counterexample normal form   & Lem.~5.2--5.3    & open (structural) \\
S8  & CAP5 reducibility                    & \S6              & partial \\
S9  & minimality wrap ($+$ Tait)           & Def.~5.1 / Thm.~2.3 & open (structural) \\
\bottomrule
\end{tabular}
\end{center}

\paragraph{Machine-checked outright.} The finite encoded-model audits for
Lemmas~8.14 and 8.15, together with completeness of the 192-state incidence
enumeration; unrestricted-oracle strictness and conditional need-based Pillar~A
infrastructure (with four uniform peel oracles refuted); and the length-2/3
radial-closing-edge S2 census. The corresponding graph move-soundness, actual
v23 $\Wz(H)$ inclusion, and manuscript S2 statement remain open. All with no \texttt{sorry} and axioms
$\subseteq\{\texttt{propext},\texttt{Classical.choice},\texttt{Quot.sound}\}$.

\paragraph{Reduced to one pin.} Gate-2 (Lemmas~8.18/8.19): the manuscript's
pointwise Step-1 preparation is refuted and replaced by the frontier-automaton /
fibration architecture, whose real-fiber labs pass to length seven; the whole
composition rests on a single named structural remainder.

\paragraph{Regression countermodel.} \S9.2 Step~4's collar-word-to-ambient-word
reinterpretation fails in the encoded two-layer tau-chain model. A simple planar
cyclically-five-connected graph realization has not been proved; the
actual-collar cut-lift obligation remains open. In the encoded model this
lowers the odds that the v23 route completes \emph{as written}; its salvage is
open.

\paragraph{v24 scope.} See \S\ref{sec:v24}. The validation toolchain and
censuses are independently reproduced; the all-face curvature identity and
the corrected \emph{weighted} pentagon budget are proved; the
necklace/corridor, pumping, and framed-trail layers are in the tree; the
endgame (fusion chains, chiral monodromy, Trail Completability, L1--L10, and
a proved Short-Strand replacement) is open.

\paragraph{Open (the non-finite heart).} Steps S1, S3, S5--S9: the realization of
abstract chains as actual collars, the wide-annulus peeling, the interface to
Kauffman's reduction, and the Kauffman/normal-form/CAP5 internals. Their common
cost is one shared planar-embedding/duality/Jordan infrastructure the development
does not yet have; most carry a known proof shape, so their risk is
formalization cost rather than mathematical doubt --- with the exception of the S4
salvage, which is genuinely open.

\paragraph{What is not claimed.} We do \emph{not} claim the Four-Color Theorem,
and we do not claim that v23 proves it. The 4CT is a theorem via the
computer-assisted proofs; what is at issue is solely the viability of the v23
human-readable route, which remains \emph{open} --- its foundational layer now
machine-checked, its most dangerous assembly seam pinned down as broken.

\section*{Provenance}
\addcontentsline{toc}{section}{Provenance}
The manuscript discussed is Ben Goertzel, \emph{A Human-Readable,
Spencer--Brown/Kauffman-Style Proof of the Four-Color Theorem}, version~v23. The
formalization is work of the MeTTapedia formalization effort. The keystone and
transparency are module \texttt{GoertzelLemma814}; the Pillar-A obstruction and
its need-based repair are \texttt{FrontierGeometric}, \texttt{GoalAudit}, and
\texttt{PillarASmallerSpace}; the Gate-2 architecture is
\texttt{GoertzelLemma818SemanticBridge} and the frontier-automaton modules; the
S2 bridge is \texttt{GoertzelLemma818ClosedCollarS2Bridge}; the S4 counterexample
and the refuted two-sided-avoidance repair are
\texttt{GoertzelLemma818TwoLayerEscape} and
\texttt{GoertzelLemma818TwoSidedAvoidance}. The v24 route of \S\ref{sec:v24}
is the \texttt{GoertzelV24*} module family (roughly sixty modules; the primary
mathematical source is the v24 working package \emph{Deserts, Pivots, and the
Necklace}, July 2026). Lean listings are ASCII
transliterations of the source declarations (the sources are normative); every
headline was checked with \texttt{\#print axioms}. Per-declaration source links
are omitted pending publication of the development tree.

\appendix

\section{A graveyard of superseded sub-routes}
\label{app:graveyard}

Each entry is a route or reading that was tried and set aside; several are
themselves machine-checked theorems that a stated step \emph{fails}.

\begin{description}
  \item[The spanning \emph{equality} $\Wz(H)=\mathrm{span}(\mathcal{G})$.] Refuted
        on every closed-walk exact shell (\S\ref{sec:pillarA}); superseded by the
        need-based inclusion, which is what the synthesis actually consumes.
  \item[The four uniform geometric peel oracles.] Each would have closed
        Theorem~4.9's synthesis uniformly; all four are machine-checked false.
        The route uses the manuscript's own per-embedding peeling witnesses
        instead.
  \item[The pointwise Step-1 preparation of Lemma~8.18.] The manuscript's own
        pointwise lift (via Lemma~8.16) is refuted
        (\texttt{lemma818\_pointwise\_lift\_preparation\_obstruction}); replaced by
        the frontier-automaton / fibration composition.
  \item[The prefix-fibration shortcut for Gate-2.] A tempting closed-form
        shortcut, machine-checked to fail
        (\texttt{not\_concreteChainFiberAppendPrefixFibrationClosed}); kept dead.
  \item[The false ``additivity'' of Kempe switches.] An $\FF$-additive execution
        of the Pillar-A decomposition $\Delta=\sum v_{f,g}$. This is \emph{not}
        the manuscript's route --- Pillar~C is titled ``executability without
        false additivity,'' and v23 \S8.1--8.3 show mixed color-pair switches on
        shared support do not commute. Recorded only to set aside; the faithful
        route is the operator/$\LKR$ execution of \S\ref{sec:lkr}.
  \item[An $\FF$-additivity / evader reconstruction (disavowed).] An early
        exploratory reconstruction outside the manuscript's route, which v23
        explicitly disavows (additivity invalid for mixed color-pairs; Rmk.~8.10).
        Not part of this companion's formalized content.
\end{description}

\end{document}
