\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{enumitem}
\geometry{margin=1in}

\title{4CP v24: Endpoint Experiments on the Current Shell-Bearing Benchmarks}
\author{Oruzi / Codex / Claude}
\date{June 11, 2026}

\begin{document}
\maketitle
\sloppy

\begin{abstract}
This document is an honest v24 status draft for the current Goertzel-style
four-color route.  Lean already proves that the present exact one-collar/v23
shells do not uniformly force any of the four currently formalized geometric
oracle inputs.  The live route surface now also formalizes the remaining
non-geometric candidate as an exact-shell algebraic cancellation oracle,
expressed by a projected-generator detector certificate on the shell's Tait
coloring, and now also in a weaker explicit-family form that only asks for
some detecting coloring family inside the relevant edge-Kempe closure.  The
natural cheap follow-up question is therefore whether the same
explicit shell-bearing benchmarks already falsify the endpoint itself,
\verb|Theorem49BoundaryRootSynthesis|.  The new finite lab in
\verb|scripts/4cp_lab/| computes that endpoint exactly on the current small
benchmarks.  On the shell-bearing wheel and shared-interior-pair embeddings,
the endpoint is true for the explicit benchmark colorings, and in the same lab
it is true for every Tait coloring enumerated there.  So the present benchmark
pathologies refute the geometric ladders, but do not presently refute the
endpoint.  Lean now proves the full endpoint on all 36 wheel Tait colorings
and on all 72 shared-interior-pair Tait colorings, and a new Lean theorem
proves that the full theorem-4.9 synthesis package depends only on the
underlying edge-Kempe closure class.  A companion Lean theorem now proves the
same closure invariance for the selected-boundary projected-generator detector
property exposed by the finite lab, so the current benchmark burden is no
longer inside these finite Tait sweeps even at the detector layer; it has
moved to wider shell-bearing searches or to a scalable computable F$_2$ layer
beyond them.  The exact shared radius-$1$ detector certificate from the finite
lab is now kernel-checked directly as well, and Lean sharpens it: instead of
needing the whole seven-color radius-$1$ neighborhood, the shared benchmark's
detector already follows from the explicit coloring plus one inner red/blue
Kempe neighbor.  The companion wheel radius-$0$ singleton certificate is now
kernel-checked directly too, so the finite lab's two minimal explicit
detector certificates both now live in Lean rather than only in Python output.
\end{abstract}

\section{Current formal status}

The Lean tree now has a sharp separation:
\begin{itemize}[leftmargin=2em]
\item \verb|Goal.lean| packages the manuscript-shaped target
  \verb|Theorem49ShellClaim|, proves all four currently formalized geometric
  uniform oracle routes false, and states the remaining non-geometric
  algebraic cancellation oracles in detector form, both closure-wide and
  explicit-family.
\item \verb|Shells.lean| and \verb|Frontier.lean| expose the live bundled
  exact one-collar/v23 shells, the new cancellation-shell bundles, and the
  maximal positive/negative wrappers over them.
\item \verb|ROADMAP.md| now records the live dichotomy: either strengthen the
  same-embedding geometry, uniformly derive the new detector/cancellation
  certificate from the exact shell, or refute the endpoint itself on a
  shell-bearing benchmark.
\end{itemize}

Before the new endpoint regressions, the cheapest direct refutation experiment
was still open.  The tree proved the endpoint on a degenerate all-boundary
wheel embedding, but not on the shell-bearing wheel/shared benchmarks
themselves.  It now proves the endpoint on all 36 Tait colorings of the
shell-bearing wheel benchmark and all 72 Tait colorings of the shell-bearing
shared benchmark.  For the shared benchmark, the Lean route first proves two
explicit Kempe-closure representatives, then proves abstract
`Theorem49BoundaryRootSynthesis` invariance under equality of the underlying
edge-Kempe closure, and finally classifies every Tait coloring into one of the
two parametric closure families that reduce back to those representatives.
The same pattern now closes one layer earlier as well: a dedicated Lean file
shows that the selected-boundary projected-generator detector property is
closure-class invariant, and the wheel/shared full-sweep regression files lift
the explicit detector certificates to all 36 wheel and all 72 shared Tait
colorings.  The live `Goal`/`Shells`/`Frontier` surface now exposes that same
detector property as the remaining exact-shell non-geometric repair candidate,
rather than leaving it only as experiment prose.  Another new Lean file,
\verb|Theorem49ColoringGeneratorFamilyRoute.lean|, now proves that any
explicit detecting coloring family inside the base edge-Kempe closure already
upgrades to the full theorem-4.9 synthesis endpoint.  So the live
non-geometric lane no longer has to be stated on the whole closure at all; it
can match the finite lab's smaller witness neighborhoods directly.  A new Lean
file,
\verb|Legacy/Theorem49SharedInteriorPairRadiusOneDetectorRegression.lean|,
now kernel-checks the exact shared radius-$1$ lab certificate itself, and
improves it: the seven-color radius-$1$ neighborhood is sufficient, but the
proof only needs a two-color witness subfamily consisting of the explicit
coloring and one inner red/blue Kempe swap.  Another new Lean file,
\verb|Legacy/Theorem49WheelRadiusZeroDetectorRegression.lean|, now
kernel-checks the exact wheel radius-$0$ lab certificate itself: the explicit
wheel benchmark coloring alone already detects every nonzero
selected-boundary-zero chain.  Another new Lean file,
\verb|Theorem49DetectorStrength.lean|, now proves that on every embedding with
an unblocked interior endpoint the theorem-4.9 target subspace
\verb|theorem49BoundaryZeroKirchhoffSubspace emb (selectedBoundaryInteriorEdgeEndpointVertices emb)|
is a proper subspace of the full selected-boundary-zero chain space
\verb|planarBoundaryZeroSubmodule emb|.  So the detector/cancellation oracle is
strictly stronger than the manuscript target on every shell-bearing embedding;
it is not simply theorem 4.9 rewritten in a more computational idiom.

\section{Stage-0 lab}

The new lab under \verb|scripts/4cp_lab/| mirrors the finite objects actually
used by the endpoint:
\begin{itemize}[leftmargin=2em]
\item selected-boundary support and interior-edge support,
\item selected-boundary interior-edge endpoint vertices,
\item the endpoint target
  \verb|theorem49BoundaryZeroKirchhoffSubspace|,
\item the raw Definition 4.8 generator span over the finite edge-Kempe
  closure of a base coloring,
\item the selected-boundary projection of that span, and
\item the thirteen endpoint fields collapsed to finite subspace equalities,
  inclusions, and orthogonality checks.
\end{itemize}

The cross-check gate is deliberately modest but exact:
\begin{itemize}[leftmargin=2em]
\item the support-set facts for the wheel, shared-interior-pair, and
  diamond-with-triangle embeddings agree with the Lean benchmark definitions;
\item the lab returns \verb|true| on the degenerate wheel embedding, matching
  the existing Lean-positive trivial case; and
\item the lab returns \verb|true| on the nondegenerate positive
  \verb|diamondWithTriangleEmbedding| case.
\end{itemize}

\section{Experiment 01}

Table~\ref{tab:exp01} summarizes the current direct endpoint computations.

\begin{table}[h]
\centering
\resizebox{\textwidth}{!}{\input{generated/exp01_status_table.tex}}
\caption{Stage-0 endpoint verdicts on the current small benchmark family.}
\label{tab:exp01}
\end{table}

The decisive point is the first two rows.  The shell-bearing wheel benchmark is
not an endpoint counterexample.  The shell-bearing shared-interior-pair
benchmark is not an endpoint counterexample either.  In fact, on both
embeddings every Tait coloring enumerated by the lab still satisfies the full
endpoint.

So the current explicit pathologies support the following status line:
\begin{quote}
The present benchmarks refute the currently formalized uniform geometry-to-oracle
ladders, but do not presently refute
\verb|Theorem49BoundaryRootSynthesis| itself.
\end{quote}

\section{Consequence for v24}

This rules out one tempting but too-fast narrative: it is not enough to say
``the wheel and shared-interior-pair pathologies already kill Theorem 4.9''.
At present they kill the known geometric globalization shells, not the
endpoint.  That matters for the paper architecture.

The live choices are therefore narrower:
\begin{enumerate}[leftmargin=2em]
\item search for a different shell-bearing embedding where the endpoint itself
  fails;
\item mine stronger same-embedding hypotheses that the current pathologies do
  not satisfy but genuine induction configurations do; or
\item build the planned Lean-computable F$_2$ elimination/search layer so the
  present benchmark discharge can be widened safely beyond the wheel/shared
  family.
\end{enumerate}

What this draft does \emph{not} claim is just as important.  It does not claim
the full Stage 1 genuine-configuration sweep.  It does not claim a Lean proof
of any wider shell-bearing sweep beyond the wheel/shared benchmarks.  And it
does not claim a new proof of the Four Color Theorem.

\section{Next steps}

The next technically responsible steps are:
\begin{itemize}[leftmargin=2em]
\item extend the present benchmark discharge to new shell-bearing families via
  a computable Lean F$_2$ layer or similarly scalable finite search interface;
\item extend the computational sweep beyond the current pathologies before
  writing any stronger negative or positive story; and
\item exploit the new explicit-family detector route rather than demanding
  whole-closure certificates up front, so finite Lean certificates can scale
  by neighborhood enlargement rather than closure enumeration alone; and
\item keep the paper honest by separating proved Lean facts, finite lab facts,
  and still-unproved geometric bridge claims.
\end{itemize}

\end{document}
