% fourcolor_proofstate.tex — Proof-state ledger for the Four-Color route corpus.
% Clean section content for \input; relies on amsmath/amssymb. No \documentclass.
%
% Verified directly against the Lean source under
%   lean/mettapedia/Mettapedia/GraphTheory/FourColor (read-only).
% Goal/GoalAlgebraic/GoalAudit were read and quoted from source.

\section{Four-Color via the Algebraic Route: Proof-State Ledger}
\label{sec:fourcolor-proofstate}

This is the honest accounting of the Four-Color corpus along Goertzel's specific
algebraic route ($\mathbb{F}_2$ color-algebra / boundary-word / Definition~4.8 /
Theorem~4.9 machinery). The headline finding: the Four Color Theorem is
\textbf{not} proven, is \textbf{not even stated as the top-level goal}, and the
single manuscript step under attack (Theorem~4.9) is proven \emph{only
conditionally} on an unproven \texttt{AlgebraicCancellationOracle}---while every
concrete \emph{geometric} route to discharge it is proven \emph{false}, and the
topological cyclic-separator (``Sublemma~6.8'') is an undischarged hypothesis
whose naive graph realization is also refuted. The corpus is, accurately, a
rigorous audit that localizes and partially walls off the open crux, with genuine
positive content in the small-case classifications and a few unconditional
algebra lemmas.

\subsection{What is machine-checked}
\label{sec:fc-checked}

\paragraph{Axiom and \texttt{sorry} hygiene.}
\textbf{Zero} real \texttt{sorry} (the only standalone token is in a Markdown
roadmap note), \textbf{zero} \texttt{admit} tactic (matches are the substring
inside identifiers like \texttt{admitsPlanarBoundary}$\dots$), \textbf{zero}
\texttt{axiom} declarations, \textbf{zero} \texttt{native\_decide} (small cases
use ordinary kernel \texttt{decide}). Consistent with the seal
$\text{axioms}\subseteq\{\texttt{propext},\texttt{Classical.choice},
\texttt{Quot.sound}\}$; no \texttt{\#print axioms} self-seal (reported, not
independently sealed).

\paragraph{Top-level goal status} \;[\textsc{Conditional / Open}].
\texttt{TaitColorable} is a \texttt{def}, not a theorem
(\texttt{Goal.lean}); the comment notes the Four Color Theorem is equivalent to
it ``by Tait's reduction (\emph{not formalized here}).'' The actual target is
\texttt{Theorem49ShellClaim}, also a \texttt{def : Prop}. \emph{Every} proof of
it is conditional---the named forms are
\texttt{theorem49ShellClaim\_of\_<X>Oracle}
(\texttt{Goal.lean}, \texttt{GoalAlgebraic.lean}); there is no bare
\texttt{theorem $\_$ : Theorem49ShellClaim}. The synthesis endpoint is reached
only from an assumed oracle.

\paragraph{Genuine unconditional content (the plumbing).}
\begin{itemize}
  \item \textbf{Lemma~44} (\texttt{GoertzelLemma44.lean},
  \texttt{v23\_single\_component\_purification}) \;[\textsc{Unconditional}]: the
  exact Step-2 Kempe-switch XOR identity
  $\texttt{gen}(C)+\texttt{gen}(\texttt{swap})=\texttt{componentBoundarySlice}$.
  Real algebraic content, fully proven.
  \item \textbf{Lemma~47} (\texttt{GoertzelLemma47.lean})
  \;[\textsc{Unconditional}]: cut-parity / incidence-count lemmas.
  \item \textbf{Definition~4.8} (\texttt{GoertzelDefinition48.lean}):
  definitional (polarized face generators, Kempe-closure family) with proven
  \texttt{simp}-lemmas.
  \item \texttt{ColorAlgebra.lean} ($\mathbb{F}_2=\texttt{ZMod }2$, $\text{Color}
  =\mathbb{F}_2\times\mathbb{F}_2$): elementary algebra fully proven by
  \texttt{decide}/\texttt{ring}/\texttt{fin\_cases}.
  \item \textbf{Detector-strength strictness}
  (\texttt{Theorem49DetectorStrength.lean},
  \texttt{theorem49BoundaryZeroKirchhoffSubspace\_lt\_planarBoundaryZeroSubmodule\_of\_hasUnblockedInteriorEndpoint})
  \;[\textsc{Unconditional}]: the manuscript target $W_0(H)$ is a \emph{proper}
  subspace of the full boundary-zero space---an honest result confirming the
  surviving oracle is strictly \emph{stronger} than Theorem~4.9 (closing it is
  harder, not a restatement).
\end{itemize}

\paragraph{Small-case finite classifications (independent positive content).}
The \texttt{Curriculum/Actual/} tree (5-, 6-, 7-vertex) is $\sim 68$ files of
genuine, fully-proven finite combinatorics, \texttt{sorry}/\texttt{axiom}-free
and importing \emph{none} of the Theorem49/Goertzel/oracle machinery. Verbatim
headline results: \texttt{top\_not\_colorable\_four\_of\_card\_eq\_five} ($K_5$
is not $4$-colorable) and the unique $5$-vertex critical graph is $K_5$
(\texttt{FiveVertexClassification.lean}); the $7$-vertex $K_5$-free incidence-
critical non-$4$-colorable graphs are exactly $K_2\bowtie C_5$ ($16$ edges) up to
isomorphism (\texttt{SevenVertexSixteenCharacterization.lean}, with witness
\texttt{$\dots$\_not\_colorable\_four}). These are real machine-checked
finite four-coloring facts, entirely distinct from and independent of the open
algebraic crux.

\subsection{What it scopes out}
\label{sec:fc-scopes}

\begin{itemize}
  \item \textbf{Tait's reduction is not formalized at all}---the bridge from the
  Four Color Theorem to the edge-coloring statement actually studied is absent.
  \item \textbf{The Theorem~49 family ($\sim 120$ files) is detector / evader /
  boundary-projection / peeling scaffolding}, and \emph{every} route to the
  endpoint is conditional. Representative signatures: \;[all
  \textsc{Conditional}]
  \begin{itemize}
    \item \texttt{$\dots$\_of\_boundaryZeroProjectedColoringGeneratorDetector}
    (requires a detector hypothesis \texttt{hdet});
    \item \texttt{$\dots$\_of\_familyPairingKerEqBot}
    (requires $\ker(\dots)=\bot$);
    \item \texttt{Theorem49PositiveGeometricSourceImpossibility}:
    \texttt{selectedBoundary$\dots$\_eq\_empty\_of\_closedWalkAnnulusBoundarySource$\dots$}
    --- an \emph{impossibility} result: the positive-geometry package forces an
    \emph{empty} carrier, killing that route.
  \end{itemize}
  \item \textbf{The CAP5 algebra bridge does not close.} In
  \texttt{CAP5AlgebraBridge.lean}, the three top theorems conclude
  \texttt{Theorem49BoundaryRootSynthesis} \emph{only} from open inputs (an
  algebraic control/non-vanishing hypothesis, single-coordinate witness families,
  and the \texttt{HasCycleOnSide} topological hypotheses). The bridge bottoms out
  in assumed inputs; it produces no unconditional coloring/reducibility result.
  Detectors and boundary-words (\texttt{CAP5PathXorDetector.lean},
  \texttt{CAP5BoundaryWord.lean}) are fully \emph{defined} but are objects to be
  \emph{supplied}, not proven to exist.
\end{itemize}

\subsection{Blocks and obstructions}
\label{sec:fc-blocks}

\paragraph{The open crux (confirmed).}
\begin{itemize}
  \item \textbf{Algebraic-cancellation oracle = assumed, never proven.}
  \texttt{GoalAlgebraic.lean} defines \texttt{AlgebraicCancellationOracle :
  Prop} (and two weaker lab-faithful variants), only ever \emph{consumed as a
  hypothesis} (\texttt{theorem49ShellClaim\_of\_algebraicCancellationOracle}).
  No theorem proves one as a conclusion; unlike the geometric oracles it is
  \emph{not} refuted---it is genuinely open.
  \item \textbf{The four geometric oracles are proven false.}
  \texttt{GoalAudit.lean}: \texttt{not\_interiorDualPeelOracle},
  \texttt{not\_wellFoundedPeelOracle},
  \texttt{not\_previousBoundaryGeometryOracle},
  \texttt{not\_residualBoundaryGeometryOracle}. The manuscript's intended
  geometric route to the synthesis is formally dead; only the unproven algebraic
  oracle survives.
  \item \textbf{Sublemma~6.8 / Jordan cyclic-separator = undischarged
  hypothesis, naive realization refuted.} In \texttt{CAP5Reducibility.lean} the
  planar/Jordan ``supply a side'' requirement is an explicit obligation; its
  graph-facing target is shown unsatisfiable as stated under cyclic
  $5$-edge-connectivity:
  \texttt{false\_of\_cyclicallyFiveEdgeConnected\_of\_portal\_no\_counterexample\_walk}
  and
  \texttt{false\_of\_cyclicallyFiveEdgeConnected\_of\_cyclicSeparatorCandidate}.
  The Jordan input (\texttt{HasCycleOnSide} on both sides) is a defined predicate
  taken as a hypothesis, \emph{not} derived from planarity---a clean, explicit,
  undischarged topological hypothesis whose naive graph realization is refuted.
\end{itemize}

\paragraph{Refutations / counterexamples.}
\texttt{Counterexamples.lean} (naive bridge/walk approaches fail),
\texttt{NoDigonsCounterexample.lean} (rotation-system data alone does not force
no-interior-digons; theta-graph refutation), and
\texttt{FrontierRefutations.lean} / \texttt{GoalAudit.lean} (the
wheel-with-inner-triangle and shared-interior-pair benchmarks inhabit the full
exact shell while refuting all four geometric oracles)---i.e.\ no uniform
derivation from the manuscript's stated hypotheses to the geometry its argument
consumes can exist.

\begin{center}
\begin{tabular}{lll}
\hline
Block & Status & Proven-intrinsic? \\
\hline
Small-case finite classifications & \textsc{Proven} & yes (genuine, independent) \\
Lemma 44 / 47, color algebra & \textsc{Proven} & yes (plumbing) \\
Detector-strength strictness $W_0(H)\subsetneq$ full & \textsc{Proven} & yes; makes oracle \emph{harder} \\
Four geometric peel oracles & \textsc{Refuted (proven false)} & yes (route killed) \\
Cyclic-separator graph realization & \textsc{Refuted under cyc-5-conn} & yes (naive realization dead) \\
Algebraic-cancellation oracle & \textsc{Assumed, open} & no; the live crux \\
Theorem 4.9 synthesis endpoint & \textsc{Conditional on the oracle} & open \\
Tait reduction (FCT $\Leftrightarrow$ edge-coloring) & \textsc{Not formalized} & absent \\
\hline
\end{tabular}
\end{center}

\subsection{PLN ledger}
\label{sec:fc-pln}

$\mathrm{ITV}=[L,U]=[\,s\cdot c,\ s\cdot c+(1-c)\,]$.

\begin{center}
\begin{tabular}{lcccc}
\hline
Node & $\langle s,c\rangle$ & $\mathrm{ITV}=[L,U]$ & PROGRESS & reading \\
\hline
Small-case classifications (5/6/7-vertex) & $\langle 1.00,0.95\rangle$ & $[0.95,1.00]$ & $100\%$ & genuine, scoped \\
Lemma 44/47, algebra plumbing & $\langle 1.00,0.90\rangle$ & $[0.90,1.00]$ & --- & unconditional \\
Theorem 4.9 via algebraic route (outcome) & $\langle 0.25,0.66\rangle$ & $[0.165,0.505]$ & $\sim 55\%$ & headline step \\
\hline
\end{tabular}
\end{center}

\noindent\textbf{Outcome vs progress.} The outcome node carries \emph{higher}
PROGRESS ($\sim 55\%$) than the other three problems precisely because the route
boundaries are sharp: four candidate geometric oracles are proven false, the
cyclic-separator's naive realization is refuted, the surviving algebraic oracle is
isolated, and the detector-strength result proves it is strictly stronger than
Theorem~4.9 (so the difficulty is correctly located, not understated). Outcome
confidence ($0.66$) is moderate---more than the analysis problems because the
crux is a single, sharply-stated algebraic obligation rather than an open ocean,
but well short of a proof because that obligation is genuinely unproven and the
Tait reduction is entirely absent. Strength ($0.25$) stays low and honest: the
central reduction is open.

\paragraph{Single honesty correction.}
Summarizing this as ``a Lean proof (or near-proof) of the Four Color Theorem''
is wrong on two compounding levels: (1) Tait's reduction---the bridge from the
Four Color Theorem to the edge-coloring statement actually studied---is not
formalized at all; and (2) even the single manuscript step being attacked
(Theorem~4.9) is proven only conditionally on an unproven
\texttt{AlgebraicCancellationOracle}, while every concrete geometric route to
discharge it is proven false and the topological cyclic-separator is an
undischarged hypothesis whose naive graph realization is also refuted. The
codebase's own \texttt{Goal.lean} states this correctly; what it does not yet do
is seal the axiom set with a checked \texttt{\#print axioms}.
