% ns_proofstate.tex — Proof-state ledger for the Navier-Stokes route corpus.
% Clean section content for \input; relies on amsmath/amssymb. No \documentclass.
%
% Verified directly against the Lean source under
%   lean/mettapedia/Mettapedia/FluidDynamics/NavierStokes (read-only).
% Theorems cited were opened and read; commit/summary language is not trusted.

\section{Navier--Stokes: Proof-State Ledger}
\label{sec:ns-proofstate}

This is the honest accounting of the Navier--Stokes (Clay / Fefferman global
regularity) corpus. The PDE is genuinely formalised---\texttt{NSSpace} $:=
\texttt{EuclideanSpace }\mathbb{R}\,(\texttt{Fin }3)$, with real Mathlib
\texttt{fderiv}/$\Delta$/\texttt{gradient} operators and a Bochner-integral
kinetic energy in \texttt{NavierStokesEquationCore.lean}. The headline finding:
\textbf{there is no unconditional global-regularity theorem, and the corpus does
not claim one.} The real Millennium target is a \texttt{def : Prop} that is
never proven as a theorem; the only \emph{resolved} truth value about it
\emph{refutes} an over-broad surrogate. Everything load-bearing is either a
conditional transfer lemma (target as a hypothesis), a finite-energy no-go
refutation of a specific candidate family, or honestly self-labelled
``scaling-uncleared'' bookkeeping.

\subsection{What is machine-checked}
\label{sec:ns-checked}

\paragraph{Axiom and \texttt{sorry} hygiene.}
\textbf{Zero} real \texttt{sorry}/\texttt{admit} (all matches are the prose word
``admits''), \textbf{zero} custom \texttt{axiom}, \textbf{zero}
\texttt{native\_decide}. The seal
$\text{axioms}\subseteq\{\texttt{propext},\texttt{Classical.choice},\texttt{Quot.sound}\}$
is consistent with static inspection; there is no \texttt{\#print axioms}
self-seal (reported, not independently sealed).

\paragraph{Conditional transfer lemmas (target as a hypothesis)}
\;[\textsc{Conditional}]. Every theorem naming the real target carries it on the
\emph{left}: form
$(h:\texttt{ExplicitFiniteEnergyAdmissibleNavierStokesMillenniumTarget})
\to \text{consequence}$. Examples:
\texttt{NavierStokesBKMTargetTransfersMillennium.lean},
\texttt{NavierStokesUniformVorticityTargetSurfaceTransfers.lean},
\texttt{NavierStokesSchwartzData.lean}. These prove ``\emph{if} you assume global
regularity, \emph{then} BKM / vorticity-continuation / Schwartz consequences
follow''---i.e.\ they assume the hard thing. The target itself
(\texttt{ExplicitFiniteEnergyAdmissible$\dots$}, and
\texttt{FiniteEnergyConcrete$\dots$}) is a \texttt{def : Prop}; \emph{no theorem
has either as its bare conclusion}.

\paragraph{The only resolved truth value is a refutation of a strawman}
\;[\textsc{Unconditional, negative}]. In
\texttt{NavierStokesUniformVorticityConcreteWitnesses.lean}:
\[
\texttt{not\_ExplicitConcreteNavierStokesMillenniumTarget}
:\ \lnot\,\texttt{ExplicitConcreteNavierStokesMillenniumTarget}.
\]
The \emph{naive} ``$\forall\,\nu\,u_0$ (no finite-energy hypothesis)'' target is
\emph{false}, because nonzero linear-shear data is admitted as smooth and
divergence-free input but has infinite energy and cannot meet the bounded-energy
output. The in-file comment keeps it as ``a regression guard against
reintroducing that theorem-shape bug.'' This refutes a strawman, not the real
problem.

\paragraph{Finite-energy no-go refutations}
\;[\textsc{Unconditional, negative, narrow}]. In
\texttt{NavierStokesEnergyBKMBridge.lean},
\[
\texttt{not\_exists\_energyBKMBridge\_kineticIntegrabilityOnSlab\_constantInitialVelocity}
\]
(and a heat-shear analogue): for $c\neq 0$, $0\le T$, there is \emph{no}
velocity field matching constant initial data with kinetic energy integrable on
the slab---because a nonzero constant / heat-shear field on $\mathbb{R}^3$ has
infinite initial kinetic energy. Genuine, sound, but narrow: it excludes
specific non-finite-energy candidates.

\subsection{What it scopes out}
\label{sec:ns-scopes}

\begin{itemize}
  \item \textbf{No global regularity.} The corpus's own headers say so:
  \texttt{ProofState.lean} ``an audit surface $\dots$ not a solution of the
  Millennium problem''; \texttt{Live.lean} ``It is not a proof of the Millennium
  Navier-Stokes problem.''
  \item \textbf{The Fefferman ``global regularity clause'' is a tautology over
  abstract predicates.} In \texttt{FeffermanTargetBack.lean},
  \texttt{FeffermanGlobalRegularityClause }$K := \texttt{Nonempty
  (FeffermanGlobalRegularityOutput }K)$, where $K$'s physical content
  (\texttt{SmoothVelocity}, \texttt{MomentumEquation}, \texttt{Incompressible},
  \texttt{BoundedEnergy}, $\dots$) is an \emph{arbitrary abstract
  \texttt{Prop}-valued field} \emph{not wired to the formalised
  $\mathbb{R}^3$ NS PDE}. Every ``realizes\_clause'' theorem takes obligations
  that \emph{already bundle proofs of all output properties as hypotheses} and
  returns the bundle---an $A\to A$ shape, not a reduction.
  \item \textbf{Cole--Hopf is scalar, not vector NS.}
  \texttt{ColeHopfInterface.lean} states explicitly it ``does \emph{not} attempt
  to formalize the actual SG diffusion or semigroup laws''; it records
  hypotheses (uniform positivity of $\Phi$, an identity-energy bound, a
  frame-curl bound) and derives a pointwise $|\text{vorticity}|\le$ envelope
  bound. \texttt{ColeHopfPositiveLowerBound.lean} works with the scalar
  $W=-2\nu\log\Phi$ on a scalar heat field---Burgers/heat algebra used as a
  uniform-vorticity-envelope generator, \emph{not} a solution of vector NS. The
  corpus is candid that reaching the Fefferman target from the resulting
  ``vorticity tendril'' still requires a separate lift supplying velocity,
  pressure, the PDE, incompressibility, initial condition, bounded energy, and
  the relation tying vorticity to velocity.
\end{itemize}

\subsection{Blocks and obstructions}
\label{sec:ns-blocks}

\paragraph{The averaged-equation / supercritical-scaling route is recorded
``scaling-uncleared'' with missing obligations (confirmed).}
\texttt{ProofState.lean} node \texttt{navier.supercritical-scaling} has
\texttt{status := .scalingUncleared}, $\langle s,c\rangle=\langle
0,98\rangle$, with explicit blocker text: ``Do not promote this route to global
regularity unless the critical-norm and supercritical-upgrade blocks are
replaced by checked clearance theorems, the averaged-equation obligation packet
is represented, and the required challenge-world interfaces are supplied.''
Supporting (verbatim) records in \texttt{Scaling/Basic.lean} and
\texttt{Scaling/AveragedEquationObstruction.lean}:
\begin{itemize}
  \item \texttt{currentNavierEnergyBKMRoute\_regularityPromotionGate\_refuted}:
  a conjunction asserting $\lnot$ClearsAll on the scaling status, the world
  interfaces, the averaged-equation compatibility, and the promotion gate, plus
  \texttt{velocityLpScalingRegime finiteEnergyVelocityLpIndex = .supercritical};
  \item \texttt{currentNavierEnergyBKMRoute\_averagedMomentumEquation\_obstruction}:
  records that \texttt{averagedMomentumEquation} is in the status's
  \texttt{missingObligations} and not represented;
  \item \texttt{currentNavierEnergyBKMRoute\_allAveragedEquationObstructions}.
\end{itemize}

\paragraph{Caveat: these are bookkeeping over hand-set data, not analysis.} The
``status'' being tested is a manually authored record whose fields are literally
typed in (\texttt{criticalNorm := .blocked}, \texttt{represented := []},
\texttt{supplied := [.finiteEnergyL2Diagnostic]}). The theorems prove, by
\texttt{rfl}/\texttt{simp}/\texttt{decide} over finite enumerations, that a
record whose \texttt{represented} field is \texttt{[]} fails a list-membership
predicate. This is a sound \emph{guardrail} asserting the route has not been
done, not a proof it cannot be. The one genuine scaling fact is
\texttt{velocityLpScalingRegime}\;$2=\texttt{.supercritical}$,
$3=\texttt{.critical}$: the $L^2$ (finite-energy) diagnostic is supercritical
against the $L^3$ critical index---the real supercriticality barrier encoded as
a fact about index $2$ vs $3$, not a proof of a no-go.

\paragraph{Gates are two-sided (non-vacuous), but contentless.} Positive
canaries exist---\texttt{exampleNavierAveragedEquationCompatibilityClearedStatus.Clears}
and \texttt{navierAveragedEquationFullInterface\_lab\_positive\_canary} prove
that an all-obligations-supplied record \emph{does} clear the gate---so the
obstructions are not vacuous. But the canaries are
\texttt{structure $\dots$ \{ $\dots$ : Bool \}} records with \texttt{rfl}-provable
predicates, carrying zero PDE content.

\begin{center}
\begin{tabular}{lll}
\hline
Block & Status & Proven-intrinsic? \\
\hline
Supercriticality ($L^2$ vs $L^3$ index) & \textsc{Encoded as arithmetic fact} & encodes, does not prove a no-go \\
Critical-norm gate & \textsc{Blocked} (hand-set) & no; route bookkeeping \\
Supercritical-upgrade gate & \textsc{Blocked} (hand-set) & no; route bookkeeping \\
Averaged-equation barrier (4 obligations) & \textsc{Not represented} & no; route bookkeeping \\
\hline
\end{tabular}
\end{center}

\noindent None of these blocks is proven-intrinsic in Lean. There is no theorem
``any finite-energy route necessarily fails'' and no formalised averaging-method
no-go; they mark that the current naive finite-energy/BKM route fails its own
bookkeeping floors.

\subsection{PLN ledger}
\label{sec:ns-pln}

$\mathrm{ITV}=[L,U]=[\,s\cdot c,\ s\cdot c+(1-c)\,]$.

\begin{center}
\begin{tabular}{lcccc}
\hline
Node & $\langle s,c\rangle$ & $\mathrm{ITV}=[L,U]$ & PROGRESS & reading \\
\hline
Conditional transfer lemmas checked & $\langle 1.00,0.95\rangle$ & $[0.95,1.00]$ & --- & lemma-level only \\
Supercritical-scaling node (route) & $\langle 0.00,0.98\rangle$ & $[0.00,0.02]$ & --- & honest ``not done'' \\
Global regularity (outcome) & $\langle 0.04,0.21\rangle$ & $[0.008,0.798]$ & $\sim 30\%$ & headline goal \\
\hline
\end{tabular}
\end{center}

\noindent\textbf{Outcome vs progress.} Outcome confidence is low and flat: the
supercriticality crux is untouched (the only ``scaling math'' is the index-2-is-
supercritical arithmetic fact). PROGRESS ($\sim 30\%$) reflects that the PDE is
genuinely formalised, a clean set of conditional consequences of regularity is
proven, a strawman target was caught and refuted, and the averaged-equation
route's missing obligations are explicitly enumerated. The supercritical-scaling
node's $\langle 0,0.98\rangle$ is the right way to record ``a step we have
\emph{confidently determined is not done},'' distinct from the outcome's
$\langle 0.04,0.21\rangle$ ``we do not know.''

\paragraph{Single honesty correction.}
A summary saying the corpus ``reaches the Fefferman target conditionally on a
clean compatibility hypothesis'' overstates by hiding that the Fefferman $K$
predicates are abstract, unconstrained \texttt{Prop} fields disconnected from the
formalised $\mathbb{R}^3$ NS PDE: the ``global regularity clause'' is
\texttt{Nonempty} of a structure whose entire physical content is opaque
parameters, realised only after every such predicate is assumed proven as
input---an $A\to A$ shape, not a reduction of NS to something easier. The
genuinely load-bearing analytic theorems are all \emph{negative} (finite-energy
no-go refutations) or \emph{conditional transfers}; the scaling/averaged-equation
layer is sound \texttt{Bool}/enumeration bookkeeping. To its credit, the corpus's
own headers and the $0\%$-support scaling nodes state all of this plainly.
